### 2020-12-19 old/test/ladybug_adhesion.tex
version 2
Signed-off-by: Pranav Sudersan <pranavsudersan@gmail.com>

%% LyX 2.3.5.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{achemso}
%\usepackage{biblatex}
%\usepackage[backend=biber]{biblatex}
%\usepackage[backend=biber,bibstyle=ACM-Reference-Format,citestyle=chem-rsc,url = false, isbn = false]{biblatex}
%\addbibresource{\string"E:/Work/Documents/PhD Literature.bib\string"}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage{graphicx}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}
\setkeys{acs}{doi = true}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

\title{Shape of adhesive fluid controls insect adhesion in air and underwater}

\author{Pranav Sudersan}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Thomas Endlein}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Michael Kappl}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Hans-Jürgen Butt}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\email{butt@mpip-mainz.mpg.de}

\phone{+49 6131 379 111}

\fax{+49 6131 379 310}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\SectionNumbersOn

\makeatother

%\usepackage[bibstyle=ACM-Reference-Format,citestyle=chem-rsc,url = false, isbn = false]{biblatex}
%\addbibresource{\string"E:/Work/Documents/PhD Literature.bib\string"}
\begin{document}
\begin{abstract}
Insects like beetles and flies can stick to various surfaces using
hairy pads mediated by adhesive fluid. The pads can even attach underwater,
presumably due to an air bubble trapped around the pad. There is however
a lack of understanding on the exact role of the bubble for underwater
adhesion. Here, we develop a simple theoretical model to estimate
the net adhesion of a hairy pad due to capillary forces. We perform\emph{
in-vivo} adhesion measurements of a constrained ladybug pad as well
as image its contact against smooth hydrophilic and hydrophobic substrates
in air and underwater conditions. Our experiments reveal that on hydrophobic
substrates, even without a bubble, the pad can show adhesion underwater
comparable to that in air. Only on hydrophilic substrates, a trapped
bubble is essential to generate adhesion underwater. Based on the
model, this observation is explained qualitatively. The shape of the
adhesive fluid has a negative curvature when on contact with a hydrophobic
substrate underwater, resulting in capillary forces due to the negative
Laplace pressure. Our results demonstrate that capillary forces governed
by the shape of the adhesive fluid well explains insect adhesion under
different conditions. 
\end{abstract}

\section{Introduction}

Many\textsuperscript{\cite{RN87,RN93}}

\section{Theoretical}

\subsection{Capillary Bridge Model}

This is a cool model

\begin{figure}

\includegraphics[scale=0.5]{\string"model_schematic\string".png}\caption{Model}

\end{figure}

\subsection{Results}

Wow! Nice results!

\begin{figure}

\includegraphics[scale=0.5]{\string"model_result-hydrophilic\string".png}

\includegraphics[scale=0.5]{\string"model_result-hydrophobic\string".png}\caption{Effect of substrate}

\end{figure}

\section{Experimental}

\subsection{Material and Methods}

I bought XYZ from PQR.

\subsubsection{Substrate preparation}

I made glass and fluorinate surface

\subsubsection{Contact angle measurement}

Settings for dynamic contact angle measurement

\subsubsection{Adhesion measurement}

Describe setup and protocol. I measure forces.

\subsubsection{Data analysis}

Describe image processing, statistical techniques.

\begin{figure}
\includegraphics[scale=0.5]{\string"setup_schematic\string".pdf}\caption{Setup}
\end{figure}

\subsection{Results}

Super results!

\begin{figure}
\includegraphics[scale=0.5]{\string"effect_of_contact-glass\string".jpg}

\includegraphics[scale=0.5]{\string"effect_of_contact-pfots\string".jpg}\caption{Effect of contact}
\end{figure}

\section{Discussion}

talk talk

\begin{figure}
\caption{Comparison with model}

\end{figure}

\begin{figure}

\caption{Oil contact images}

\end{figure}

\section{Conclusion}

that's all folks!

\mciteErrorOnUnknownfalse

\bibliography{references} %no file format, is in same dir.

%\printbibliography

\end{document}

### 2020-12-19 old/plot codes/effect_of_fluid_volume.py

@@ -1,0 +1,206 @@
+import seaborn as sns
+import pandas as pd
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks",
+              palette = sns.color_palette("hls", 4))
+fig_size = (6,6) #figure size
+plot_name = "Figure11-Effect of fluid volume"
+save = False #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201123 constant total fluid volume/'
+dataPath = folderPath + 'fluid_data_all.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+modelData.rename(columns={'Force': 'Force Deriv'}, inplace = True) #force from energy derivative
+modelData.rename(columns={'Force_Calc': 'Total'}, inplace = True) #force from energy derivative
+#include degree sign to contact angle
+##modelData['Contact Angle'] = modelData['Bottom_Angle'].astype(str) + '°'
+
+modelData['Contact Angle'] = (180-modelData['Bottom_Angle']).astype(str) + '°'
+#non dimensionalize volume, length scale relative to pinned DIAMETER (factor of 2)
+modelData['Fluid Volume'] = (4*np.pi/3)*((modelData['Pin_Radius']*2)**(-3))
+
+#forces scale
+modelData['Force Deriv'] *= 2*np.pi*modelData['Pin_Radius']*2
+modelData['Total'] *= 2*np.pi*modelData['Pin_Radius']*2
+modelData['Laplace'] = (modelData['Pressure'] - modelData['Ambient_Pressure']) * modelData['Bottom_Area']*modelData['Pin_Radius']*2
+modelData['Surface Tension'] = -1 * modelData['Bottom_Length'] * np.sin(modelData['Bottom_Angle']*np.pi/180)*modelData['Pin_Radius']*2
+##modelData['Force_Total'] = modelData['Force_Laplace'] + modelData['Force_Surface_Tension']
+
+column_list = list(modelData.columns)
[…]

### 2020-12-19 old/plot codes/exp_data.py

@@ -1,0 +1,80 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib.pyplot as plt
+from datetime import datetime
+
+sns.set(rc={'figure.figsize':(14,10)})
+sns.set_theme(context = 'paper', style="ticks",
+              palette="pastel", font_scale = 2)
+
+
+# Load the example tips dataset
+summaryData = pd.read_excel('E:/Work/Documents/paper-underwater_adhesion/Data/summary_20200911.xlsx', index_col=0)
+summaryData.rename(columns = {'Label': 'Contact_type'}, inplace = True)
+##summaryData = summaryData[summaryData["Label"] != "Ambiguous"]
+summaryData.replace({'Contact_type': {'Dry': 'Air',
+                                      'Bubble': 'Underwater: Bubble',
+                                      'Wet': 'Underwater: Wet'}},
+                    inplace = True)
+
+# Draw a nested boxplot to show bills by day and time
+ax = sns.boxplot(x="Contact_type", y="Adhesion_Force",
+                hue="Substrate",
+                data=summaryData)
+ax.set(xlabel=None, ylabel='Adhesion Force $[μN]$')
+
+sns.despine(offset=10, trim=True)
+plt.xticks(rotation=0)
+plt.tight_layout()
+##plt.show()
+
+import statsmodels.api as sm
+from statsmodels.formula.api import ols
+# Ordinary Least Squares (OLS) model
+# C(Label):C(Substrate) represent interaction term
+model = ols('Adhesion_Force ~ C(Contact_type) + C(Substrate) + C(Contact_type):C(Substrate)',
+            data=summaryData).fit()
+anova_table = sm.stats.anova_lm(model, typ=2)
+print(anova_table)
+
+# Shapiro-Wilk test used to check the normal distribution of residuals
+import scipy.stats as stats
+w, pvalue = stats.shapiro(model.resid)
+print(w, pvalue)
+
+#Bartlett’s test to check the Homogeneity of variances
+##import scipy.stats as stats
+##w, pvalue = stats.bartlett(d['A'], d['B'], d['C'], d['D'])
+##print(w, pvalue)
+
+# load packages
+from pingouin import pairwise_tukey
+# perform multiple pairwise comparison (Tukey HSD)
+# for unbalanced (unequal sample size) data, pairwise_tukey uses Tukey-Kramer test
+
+statDf = pd.DataFrame()
+
+fixed_params = ["Substrate", "Contact_type"]
[…]

### 2020-12-19 old/plot codes/expt_plot.py

@@ -1,0 +1,213 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib.pyplot as plt
+from datetime import datetime
+import numpy as np
+
+
+get_stats = False #calculate statistics
+save = False #save plot and statistics
+plot_name = 'Figure5-Expt_Effect_of_contact'
+contact_order = ['Air', 'Underwater: Bubble', 'Underwater: Wet', 'Bad Contact']
+
+sns.set(rc={'figure.figsize':(14,10)})
+sns.set_theme(context = 'paper',style="ticks",
+              palette="pastel", font_scale = 2)
+
+# Load experiment data
+exptData = pd.read_excel('E:/Work/Documents/paper-underwater_adhesion/Data/summary_data_Effect of contact-201112145030.xlsx', index_col=0)
+exptData.rename(columns = {'Pulloff Force': 'Adhesion_Force'}, inplace = True)
+exptData.rename(columns = {'Contact Type': 'Contact_type'}, inplace = True)
+##exptData = exptData[exptData["Contact type"] != "Ambiguous"] #filter out ambiguous data
+exptData.replace({'Contact_type': {'Dry': 'Air',
+                                   'Bubble': 'Underwater: Bubble',
+                                   'Wet': 'Underwater: Wet',
+                                   'Ambiguous': 'Bad Contact'}},
+                 inplace = True)
+exptData['Data'] = 'Experiment'
+exptData_relevant = exptData[['Contact_type',
+                              'Adhesion_Force',
+                              'Substrate',
+                              'Data']].copy()
+
+# Model data
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201020 ladybug data final/'
+dataPath = folderPath + 'summary_data_final.xlsx'
+modelData = pd.read_excel(dataPath)
+modelData.rename(columns = {'Model': 'Contact_type'}, inplace = True)
+column_list = list(modelData.columns)
+modelData = modelData[modelData['Hair dia'] == 4e-6] #filter hair diameter (4um)
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+force_order = ['Air','Underwater: Wet','Underwater: Bubble']
+group_param = ['Contact_type', 'Contact Angle', 'θ-fa', 'θ-fw',
[…]

### 2020-12-19 old/plot codes/fluid_contribution_plot.py

@@ -1,0 +1,202 @@
+import seaborn as sns
+import pandas as pd
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks",
+              palette = sns.color_palette("hls", 7))
+fig_size = (6,6) #figure size
+plot_name = "Figure1-Single bridge"
+save = False #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201006 model data final (af=2, l_d=10)/'
+dataPath = folderPath + 'fluid_bridge_data.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+modelData.rename(columns={'Force': 'Force Deriv'}, inplace = True) #force from energy derivative
+modelData.rename(columns={'Force_Calc': 'Total'}, inplace = True) #force from energy derivative
+#include degree sign to contact angle
+##modelData['Contact Angle'] = modelData['Bottom_Angle'].astype(str) + '°'
+
+#forces scale
+modelData['Force Deriv'] *= 2*np.pi
+modelData['Total'] *= 2*np.pi
+modelData['Laplace'] = (modelData['Pressure'] - modelData['Ambient_Pressure']) * modelData['Bottom_Area']
+modelData['Surface Tension'] = -1 * modelData['Bottom_Length'] * np.sin(modelData['Bottom_Angle']*np.pi/180)
+##modelData['Force_Total'] = modelData['Force_Laplace'] + modelData['Force_Surface_Tension']
+
+column_list = list(modelData.columns)
+##['Bottom_Angle', 'Pin_Radius', 'Elastic_Modulus', 'Aspect_Ratio',
+## 'Ambient_Pressure', 'Height', 'Base_Height', 'Height_Final',
+## 'Strain', 'Force', 'Force_Calc', 'Energy', 'Area', 'Scale',
+## 'Volume', 'Pressure', 'Bottom_Length', 'Top_Length', 'Bottom_Area',
+## 'Top_Area', 'Mean_Curvature', 'Min_Radius', 'Max_Radius',
[…]

### 2020-12-19 old/plot codes/fluid_plot.py

@@ -1,0 +1,168 @@
+import seaborn as sns
+import pandas as pd
+import numpy as np
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks",
+              palette = sns.color_palette("hls", 7))
+fig_size = (6,6) #figure size
+plot_name = "Figure1-Single bridge"
+save = False #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201006 model data final (af=2, l_d=10)/'
+dataPath = folderPath + 'fluid_bridge_data.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+modelData.rename(columns={'Bottom_Angle': 'Contact Angle'}, inplace = True)
+#forces scale
+modelData['Force'] *= 2*np.pi
+modelData['Force_Calc'] *= 2*np.pi
+
+column_list = list(modelData.columns)
+##['Distance', 'Force_hair_air', 'Force_hair_water', 'Force (hair)',
+##       'Bubble', 'Underwater: Bubble', 'Air', 'Underwater: Wet',
+##       'Bubble Contact Area', 'Pad  area', 'Hair Area', 'Contact Angle',
+##       'θ-fa', 'θ-fw', 'D_p/D_h', 'a_b', 'a_f', 'Packing fraction',
+##       'Aspect Ratio', 'Hair dia', 'Pad dia', 'Number of hairs', 'Hair length',
+##       'γ-fa', 'γ-wa', 'γ-fw', 's-f', 's-b', 'Vf', 'Vb', 'Fluid data file',
+##       'Bubble data file']
+
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+##force_order = ['Air','Underwater: Wet','Underwater: Bubble', 'Bubble only']#['Air','Underwater: Wet','Underwater: Bubble','Bubble only']
+color_list = None#['g', 'b', 'r', 'c'] #corresponding colors
[…]

### 2020-12-19 old/plot codes/gecko_comparison.py

@@ -1,0 +1,54 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib.pyplot as plt
+from datetime import datetime
+import numpy as np
+
+plot_name = 'Figure-9-Gecko_comparison'
+save = False
+
+##sns.set(rc={'figure.figsize':(30,25)})
+sns.set_theme(context = 'paper',style="ticks",
+              palette="pastel", font_scale = 2)
+
+#only 2 colors chosen
+color_list = sns.color_palette('pastel')[:2] #['lightgreen', 'b']
+color_list.reverse() #reversed so blue is for Wet
+
+# Load experiment data
+geckoData = pd.read_excel('E:/Work/Documents/paper-underwater_adhesion/Data/gecko_comparison.xlsx')
+
+#filter based on substrates
+geckoData = geckoData[(geckoData['Substrate'] == 'Glass') | True]#(geckoData['Substrate'] == 'PTFE')]
+
+
+# Draw a nested boxplot to show bills by day and time
+ax = sns.catplot(x='Substrate', y='Force',
+                hue='Contact type', col = 'Source',
+                kind = 'bar', data=geckoData,
+                 palette = color_list)
+
+ax.set(xlabel=None, ylabel='Force $[N]$')
+
+#replace 'Source = ' from titles
+axes = ax.axes.flatten()
+for ax in axes:
+    ax.set_title(ax.get_title().replace('Source = ', ''))
+
+##ax.set_xticklabels(rotation=45,
+##                   horizontalalignment='right')
+##ax.tight_layout(w_pad=0)
+##sns.despine(offset=10, trim=True)
+##plt.tight_layout()
+##plt.show()
+
+
+#save data and plot
+if save == True:
+    fig = ax.figure
+    timestamp = datetime.today().strftime('%Y%m%d%H%M%S')
+    fig.savefig(plot_name + "-" + timestamp + ".svg",
+                bbox_inches = 'tight', transparent = True)
+
+plt.show()
+

### 2020-12-19 old/plot codes/model_bubble_volume.py

@@ -1,0 +1,201 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks")
+fig_size = (6,6) #figure size
+plot_name = "Figure4-Effect_of_bubble_volume"
+save = False #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201006 model data final (af=2, l_d=10)/'
+dataPath = folderPath + 'summary_data_final.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+column_list = list(modelData.columns)
+##['Distance', 'Force_hair_air', 'Force_hair_water', 'Force (hair)',
+##       'Bubble', 'Underwater: Bubble', 'Air', 'Underwater: Wet',
+##       'Bubble Contact Area', 'Pad  area', 'Hair Area', 'Contact Angle',
+##       'θ-fa', 'θ-fw', 'D_p/D_h', 'a_b', 'a_f', 'Packing fraction',
+##       'Aspect Ratio', 'Hair dia', 'Pad dia', 'Number of hairs', 'Hair length',
+##       'γ-fa', 'γ-wa', 'γ-fw', 's-f', 's-b', 'Vf', 'Vb', 'Fluid data file',
+##       'Bubble data file']
+
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+force_order = ['Underwater: Bubble', 'Bubble only']#['Air','Underwater: Wet','Underwater: Bubble','Bubble only']
+color_list = ['r', 'c']#['g', 'b', 'r', 'c'] #corresponding colors
+fix_marker = None #set to 'o' if style_param is None else set as None
[…]

### 2020-12-19 old/plot codes/model_hair_size.py

@@ -1,0 +1,201 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks")
+fig_size = (12,6) #figure size
+plot_name = "Figure3-Effect_of_hair_size"
+save = False #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201006 model data final (af=2, l_d=10)/'
+dataPath = folderPath + 'summary_data_final.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+column_list = list(modelData.columns)
+##['Distance', 'Force_hair_air', 'Force_hair_water', 'Force (hair)',
+##       'Bubble', 'Underwater: Bubble', 'Air', 'Underwater: Wet',
+##       'Bubble Contact Area', 'Pad  area', 'Hair Area', 'Contact Angle',
+##       'θ-fa', 'θ-fw', 'D_p/D_h', 'a_b', 'a_f', 'Packing fraction',
+##       'Aspect Ratio', 'Hair dia', 'Pad dia', 'Number of hairs', 'Hair length',
+##       'γ-fa', 'γ-wa', 'γ-fw', 's-f', 's-b', 'Vf', 'Vb', 'Fluid data file',
+##       'Bubble data file']
+
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+force_order = ['Air','Underwater: Wet','Underwater: Bubble', 'Bubble only']#['Air','Underwater: Wet','Underwater: Bubble','Bubble only']
+color_list = ['g', 'b', 'r', 'r']#['g', 'b', 'r', 'c'] #corresponding colors
+fix_marker = None #set to 'o' if style_param is None else set as None
[…]

### 2020-12-19 old/plot codes/model_hair_size_constant_vol.py

@@ -1,0 +1,206 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks")
+fig_size = (11,6) #figure size
+plot_name = "Figure10-Effect_of_hair_size_constant_volume"
+save = False #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201123 constant total fluid volume/'
+dataPath = folderPath + 'summary_data_constant_vol.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+column_list = list(modelData.columns)
+##['Distance', 'Force_hair_air', 'Force_hair_water', 'Force (hair)',
+##       'Bubble', 'Underwater: Bubble', 'Air', 'Underwater: Wet',
+##       'Bubble Contact Area', 'Pad  area', 'Hair Area', 'Contact Angle',
+##       'θ-fa', 'θ-fw', 'D_p/D_h', 'a_b', 'a_f', 'Packing fraction',
+##       'Aspect Ratio', 'Hair dia', 'Pad dia', 'Number of hairs', 'Hair length',
+##       'γ-fa', 'γ-wa', 'γ-fw', 's-f', 's-b', 'Vf', 'Vb', 'Fluid data file',
+##       'Bubble data file']
+
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+force_order = ['Air','Underwater: Wet','Underwater: Bubble', 'Bubble only']#['Air','Underwater: Wet','Underwater: Bubble','Bubble only']
+color_list = ['g', 'b', 'r', 'r']#['g', 'b', 'r', 'c'] #corresponding colors
+fix_marker = None #set to 'o' if style_param is None else set as None
[…]

### 2020-12-19 old/plot codes/model_hair_size_v2.py

@@ -1,0 +1,206 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks")
+fig_size = (11,6) #figure size
+plot_name = "Figure3-Effect_of_hair_size"
+save = False #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201006 model data final (af=2, l_d=10)/'
+dataPath = folderPath + 'summar_data-effect of hair size_v2.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+column_list = list(modelData.columns)
+##['Distance', 'Force_hair_air', 'Force_hair_water', 'Force (hair)',
+##       'Bubble', 'Underwater: Bubble', 'Air', 'Underwater: Wet',
+##       'Bubble Contact Area', 'Pad  area', 'Hair Area', 'Contact Angle',
+##       'θ-fa', 'θ-fw', 'D_p/D_h', 'a_b', 'a_f', 'Packing fraction',
+##       'Aspect Ratio', 'Hair dia', 'Pad dia', 'Number of hairs', 'Hair length',
+##       'γ-fa', 'γ-wa', 'γ-fw', 's-f', 's-b', 'Vf', 'Vb', 'Fluid data file',
+##       'Bubble data file']
+
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+force_order = ['Air','Underwater: Wet','Underwater: Bubble', 'Bubble only']#['Air','Underwater: Wet','Underwater: Bubble','Bubble only']
+color_list = ['g', 'b', 'r', 'r']#['g', 'b', 'r', 'c'] #corresponding colors
+fix_marker = None #set to 'o' if style_param is None else set as None
[…]

### 2020-12-19 old/plot codes/model_plot.py

@@ -1,0 +1,158 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks")
+fig_size = (12,6) #figure size
+plot_name = "Figure4-Effect of hair size"
+save = True #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201006 model data final (af=2, l_d=10)/'
+dataPath = folderPath + 'summary_data_final.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+column_list = list(modelData.columns)
+##['Distance', 'Force_hair_air', 'Force_hair_water', 'Force (hair)',
+##       'Bubble', 'Underwater: Bubble', 'Air', 'Underwater: Wet',
+##       'Bubble Contact Area', 'Pad  area', 'Hair Area', 'Contact Angle',
+##       'θ-fa', 'θ-fw', 'D_p/D_h', 'a_b', 'a_f', 'Packing fraction',
+##       'Aspect Ratio', 'Hair dia', 'Pad dia', 'Number of hairs', 'Hair length',
+##       'γ-fa', 'γ-wa', 'γ-fw', 's-f', 's-b', 'Vf', 'Vb', 'Fluid data file',
+##       'Bubble data file']
+
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+force_order = ['Air','Underwater: Wet','Underwater: Bubble', 'Bubble only']#['Air','Underwater: Wet','Underwater: Bubble','Bubble only']
+color_list = ['g', 'b', 'r', 'r']#['g', 'b', 'r', 'c'] #corresponding colors
+fix_marker = None #set to 'o' if style_param is None else set as None
[…]

### 2020-12-19 old/plot codes/model_substrate.py

@@ -1,0 +1,202 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib.offsetbox import AnchoredText
+from matplotlib import rc
+from datetime import datetime
+
+matplotlib.use('Qt5Agg')
+
+##sns.set(rc={'figure.figsize':(15,7)})
+sns.set_theme(context = 'talk',
+              style="ticks")
+fig_size = (12,6) #figure size
+plot_name = "Figure2-Effect_of_substrate"
+save = False #change to False if dont want to save
+zero_line = True #set True for dashed zero line in plot
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201006 model data final (af=2, l_d=10)/'
+dataPath = folderPath + 'summary_data_final.xlsx'
+
+modelData = pd.read_excel(dataPath) # Load dataset
+
+column_list = list(modelData.columns)
+##['Distance', 'Force_hair_air', 'Force_hair_water', 'Force (hair)',
+##       'Bubble', 'Underwater: Bubble', 'Air', 'Underwater: Wet',
+##       'Bubble Contact Area', 'Pad  area', 'Hair Area', 'Contact Angle',
+##       'θ-fa', 'θ-fw', 'D_p/D_h', 'a_b', 'a_f', 'Packing fraction',
+##       'Aspect Ratio', 'Hair dia', 'Pad dia', 'Number of hairs', 'Hair length',
+##       'γ-fa', 'γ-wa', 'γ-fw', 's-f', 's-b', 'Vf', 'Vb', 'Fluid data file',
+##       'Bubble data file']
+
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+force_order = ['Air','Underwater: Wet','Underwater: Bubble', 'Bubble only']#['Air','Underwater: Wet','Underwater: Bubble','Bubble only']
+color_list = ['g', 'b', 'r', 'r']#['g', 'b', 'r', 'c'] #corresponding colors
+fix_marker = None #set to 'o' if style_param is None else set as None
[…]

### 2020-12-19 old/plot codes/model_vs_exp.py

@@ -1,0 +1,94 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib.pyplot as plt
+from datetime import datetime
+import numpy as np
+
+sns.set(rc={'figure.figsize':(30,25)})
+sns.set_theme(context = 'paper',style="ticks",
+              palette="pastel", font_scale = 2)
+
+
+# Load experiment data
+exptData = pd.read_excel('E:/Work/Documents/paper-underwater_adhesion/Data/summary_20200911.xlsx', index_col=0)
+exptData.rename(columns = {'Label': 'Contact type'}, inplace = True)
+exptData = exptData[exptData["Contact type"] != "Ambiguous"]
+exptData.replace({'Contact type': {'Dry': 'Air',
+                                   'Bubble': 'Underwater: Bubble',
+                                   'Wet': 'Underwater: Wet'}},
+                 inplace = True)
+exptData['Data'] = 'Experiment'
+exptData_relevant = exptData[['Contact type',
+                              'Adhesion_Force',
+                              'Substrate',
+                              'Data']].copy()
+
+# Model data
+folderPath = 'E:/Work/Surface Evolver/Data/Bubble_Bridge/20201020 ladybug data final/'
+dataPath = folderPath + 'summary_data_final.xlsx'
+modelData = pd.read_excel(dataPath)
+modelData.rename(columns = {'Model': 'Contact type'}, inplace = True)
+column_list = list(modelData.columns)
+#force variables in data (used to convert data to long form)
+force_vars = ['Force_hair_air', 'Force_hair_water', 'Force (hair)',
+              'Bubble only', 'Underwater: Bubble', 'Air', 'Underwater: Wet']
+#forces to include in plot
+force_order = ['Air','Underwater: Wet','Underwater: Bubble']
+group_param = ['Contact type', 'Contact Angle', 'θ-fa', 'θ-fw',
+               'D_p/D_h', 'a_b', 'a_f', 'Fluid data file',
+               'Bubble data file']
+
+#reshape force data into long form based on force_vars
+id_vars_list = [x for x in column_list if x not in force_vars]
+data_reshaped = pd.melt(modelData,
+                        id_vars = id_vars_list,
+                        var_name="Contact type",
+                        value_name="Adhesion_Force")
+
+#filter data
+data_filtered = data_reshaped[data_reshaped['Contact type'].
+                              isin(force_order)]
+#group data (find maxima)
[…]

### 2021-01-26 source/tex/ladybug_adhesion.tex
included tex files

%% LyX 2.3.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{achemso}
\usepackage[T2A,LGR,T1]{fontenc}
\usepackage{babel}
\usepackage{array}
\usepackage{textcomp}
\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subscript}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

\title{Wetting of adhesive fluid controls insect adhesion in air and underwater}

\author{Pranav Sudersan}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Michael Kappl}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Thomas Endlein}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Bat-El Pinchasik}

\affiliation{School of Mechanical Engineering, Tel Aviv University, Tel Aviv-Yafo,
Israel}

\author{Hans-J\"{u}rgen Butt}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\email{butt@mpip-mainz.mpg.de}

\phone{+49 6131 379 111}

\fax{+49 6131 379 310}

\DeclareRobustCommand{\greektext}{%
  \fontencoding{LGR}\selectfont\def\encodingdefault{LGR}}
\DeclareRobustCommand{\textgreek}[1]{\leavevmode{\greektext #1}}
\ProvideTextCommand{\~}{LGR}[1]{\char126#1}

\DeclareRobustCommand{\cyrtext}{%
  \fontencoding{T2A}\selectfont\def\encodingdefault{T2A}}
\DeclareRobustCommand{\textcyr}[1]{\leavevmode{\cyrtext #1}}

\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\SectionNumbersOn
%\setkeys{acs}{doi = true}
\setkeys{Gin}{width=\linewidth}
\usepackage{subcaption}

\makeatother

\begin{document}
\begin{abstract}
Insects like beetles can stick to various surfaces using hairy pads
mediated by an oily adhesive fluid. It was previously shown that the
pads can even attach underwater, presumably due to an air bubble trapped
around the pad. However, the bubble's relative contribution to adhesion
via capillary force remains unclear. To investigate the exact role
of bubble, in this study, we perform\emph{ in-vivo} underwater adhesion
measurements of a ladybug's pad, in the presence and absence of the
trapped bubble and compare it with its adhesion in air. Our experiments
reveal that on a hydrophobic substrate, even without a bubble, the
pad can show adhesion underwater comparable to that in air. On a hydrophilic
substrate, underwater adhesion is significantly reduced, with or without
a trapped bubble. To explain these results, we develop a simple theoretical
model to estimate the net adhesion of a hairy pad due to capillary
forces. Our results demonstrate that the wetting properties of the
adhesive fluid determines the insect's adhesion in both air and underwater
conditions.
\end{abstract}

\section{Introduction}

The question of how insects can walk on smooth surfaces against gravity
has fascinated scientists for at least the past three centuries \cite{RN198,RN59}.
We now know that such animals are able to adhere by using specialized
organs on their feet called adhesive pads. These adhesive pads exist
in a variety of types depending on the animal, but are generally categorized
into: 1) ``smooth pads'' found in ants\cite{RN201}, stick insects
\cite{RN182}, etc. and 2) ``hairy pads'' seen in flies \cite{RN155},
geckos \cite{RN202} and others. The hairy pads show: 1) compliance
to rough surfaces due to their lower effective modulus, 2) angle dependent
adhesion due to asymmetric hair geometry and 3) self-cleaning capability
\cite{RN20}, which makes them suitable to adhere to most surfaces
reversibly. Many of these insects pads also secrete an adhesive fluid,
as seen in flies and ants \cite{RN201} (``wet adhesion''), while
others such as spiders and geckos rely on their dry hairy pads for
attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid
secretion can enforce adhesion through surface tension and viscous
forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van
der Waals forces \cite{RN202}.

Terrestrial beetles such as the dock beetle or the ladybug have hairy
pads consisting of a dense array of hair-like structures called setae.
The setae tips can be discoidal, spatula or pointed shaped, which
are distributed throughout the pad depending on sex or species\cite{RN19}.
Single seta force measurements revealed that discoidal shaped seta
shows larger pull-off force than spatula and pointed setae\cite{RN79},
illustrating the role of hair geometry in adhesion. The tip of each
seta secretes approximately one femtoliter of oily adhesive fluid
\cite{RN108}. The fluid's chemical composition is identified as a
mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol\cite{RN221,RN222}.
A recent study by Gernay et. al.\cite{RN77}, based on an elastocapillary
model, has been able to reasonably predict single seta adhesion forces
theoretically, confirming the dominant role of surface tension in
the ``wet adhesion'' of beetles.

While most of the studies on insect adhesion are done under natural
conditions in air, insect attachment underwater has been relatively
unexplored. Typically, underwater adhesion is complicated to achieve
due to the difficulty in displacing the water layer and enable good
contact\cite{RN123}. Regardless, a study on leaf beetles\cite{RN87}
has revealed that they can in fact attach quite well to surfaces underwater.
Its hairy pad traps an air bubble underwater, which dewets the surface
on contact. It has been hypothesized that a combination of capillary
forces due the air bubble and hair contact within the dewetted area
results in its adhesion underwater. However, a detailed investigation
of the bubble's contribution and necessity to adhere to different
surfaces is lacking. Geckos are also known to adhere underwater, where
its shear adhesion force on hydrophobic substrates are similar in
both air and underwater conditions. Interestingly, its adhesion on
a fluorinated substrate is even larger underwater than in air\cite{RN15}.
This has been partially explained by a thermodynamic work of adhesion
model, assuming full displacement of water at the interface, leading
to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.

The goal of this paper is to provide a generalized picture of adhesion
in insects which use hairy pads secreting a fluid for attachment.
First, we perform adhesion measurements of a single constrained pad
of a live ladybug beetle in air and underwater conditions, both on
smooth hydrophilic and hydrophobic glass surfaces, with a microscopic
observation of the contact process. Second, we develop a simple theoretical
model considering capillary forces to predict the net adhesion force
of a hairy pad under different conditions. Finally, we discuss key
insights gained from our experiments and model, as well as possible
implications in understanding adhesion in other animals.

\section{Experimental}

Normal adhesion force measurements on a restrained leg of a live ladybug
beetle were performed. We characterize adhesion by the pull-off force
during detachment. Measurements were done against smooth glass and
fluorinated surfaces to represent hydrophilic and hydrophobic substrates
respectively. When no water was present, we labeled the contact type
as ``\emph{in air}''. For the underwater conditions, measurements
were done both in the presence and absence of a trapped bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the bubble's role in underwater adhesion. Adhesion force
for each of the labeled contact types were compared for both substrates.

\subsection{Material and Methods}

\subsubsection{Insect preparation}

Seven-spotted adult ladybug beetles (\emph{Coccinella septempuctata})
purchased from Katz Biotech (Baruth, Germany) were used for adhesion
tests. The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water\emph{ ad libitum}.

Experiments were done on male beetles. Each leg of the beetle has
a pair of hairy pads covered with mostly discoidal shaped setae, capable
of strong adhesion. For the test, we only allowed the distal-end pad
to make contact. The beetle's leg was constrained similar to the method
described by Bullock et al \cite{RN19}. A steel ball fixed with a
piece of thick solder wire served as a rotatable holder to fix the
beetle and align its leg (Figure \ref{fig:Setup}). The beetle was
first anesthetized using CO\textsubscript{2} sublimating from a piece
of dry ice and then glued to the steel ball on its back. Its front
left leg was carefully fixed to the solder wire of the holder using
Blue-Tac. Its claws were fixed using epoxy glue to prevent any wiggling.
A small piece of non-sticky Teflon tape helped to keep its other legs
tucked close to the body and avoid their interference during the adhesion
test.

After measurements, the beetle was freed by carefully removing the
epoxy glue and Blue-Tac without harming it and set free.

\subsubsection{Substrate preparation}

Standard 20 mm wide glass coverslips were used as the hydrophilic
substrate. Glass was wiped with isopropanol, rinsed in water and dried
under nitrogen flow. The surface was then plasma cleaned in a oxygen
plasma chamber (Diener Electronic Femto) for 10 min at 120 W. The
surface was further rinsed with water and dried under nitrogen flow.

For the hydrophobic substrate, the glass cover slip was coated with
a fluorosilane via chemical vapor deposition (CVD). First, the glass
was cleaned using IPA and plasma treated as before. Next, 0.2 ml of
Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
Sigma Aldrich, was put in a sealed chamber along with the the cleaned
glass. The chamber was placed under 100 mbar pressure for 10 min for
the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
for 3 hours.

The substrate wettability was characterized by dynamic contact angle
measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
De-ionized water and n-hexadecane were used as test liquids. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate. Static
contact angles were measured for a 5 \textgreek{m}l drop.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R} & \ensuremath{\theta}\textsubscript{S}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{} & 57\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{} & 110\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{} & 72\ensuremath{\pm}2\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Static and dynamic contact angles measurements \label{tab:Contact-Angles}}
\end{table}

\subsubsection{Field desorption mass spectroscopy}

Field Desorption Mass Spectrometry (FDMS) measurements of the adhesive
fluid secretions were performed using ZAB 2-SE-FPD spectrometer (VG
Instruments). A previous study on archanids \cite{RN223} reported
that the secreted fluid does not dissolve away in water. To confirm
this for the beetle, measurements before and after the immersion of
its legs in water were done. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was immersed in 100
\textmu L milli-Q water for 15 min, then in THF for 20 min and then
transferred to the measurement chamber of the spectrometer. Molecular
composition was extracted from the peak positions of the FDMS data.

\subsubsection{Adhesion test}

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fiber optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The sensor was mounted on a stage
consisting of a X-piezo, used for precise lateral movements, XYZ motors,
for coarse movements and a goniometer, for adjusting substrate alignment
with the optics. Additionally, a separate Z-piezo, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. A 3 axis manual micro-manipulator
together with the rotatable steel ball allowed good alignment of the
beetle's foot to the substrate. A coaxial illuminated tube microscope
(\emph{Navitar}) with 2x objective and a stereo-microscope with 1x
objective (\emph{Wild Heerbrugg}) fit with cameras were used to record
the sample contact with the substrate from ventral and side views
respectively. Pad contact area was visualized through the substrate
in total reflection mode by the ventral view camera. The data acquisition
from the force sensor and cameras, together with the appropriate piezo
motion steps were synchronized using a custom LABVIEW program. Force
data was acquired at a sample rate of 984 Hz, averaged to 512 points
per motion step. Videos were recorded at 20 frames per second.

The vertical and lateral piezos were together used to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, some additional motion steps were
included (Figure \ref{fig:Setup}). A 100 \textgreek{m}m lateral sliding
motion was done after the leg makes contact, to give it a proximal
pull which will orient its hairs with the substrate \cite{RN19}.
An additional 10 \textgreek{m}m compression step (approach) was done
to ensure all hairs were loaded in compression and made good contact
with the surface. A short pause (1 s) was introduced to minimize any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textgreek{m}m/s. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml MilliQ water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before experiment,
the pad was repeatedly brought into contact with the surface 10 times
to equilibriate the pad system. 5 force measurements were subsequently
performed on a fresh spot of the substrate and averaged for data analysis.
Experiments were repeated with 5 individual beetles for each type
of contact and substrate. In total, 30 beetles were tested.

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion test setup. Representative force data
and contact area of distal pad are shown in the plot, in which, the
shaded regions represent distinct piezo motion steps, negative force
values represent attraction and the minimum force peak during the
final retraction step is the adhesion force.}
\end{figure}

\subsubsection{Data analysis}

Extraction of pull-off force from force data, image processing, plotting
and statistical analysis were all performed in ``\emph{Buggee}'',
a tool written in Python using open-source libraries for synchronous
analysis of force data and video recordings (\url{https://github.com/PranavSudersan/Buggee}).

For measurements in air, pull-off force was defined as the minimum
negative force during the final retraction step. For underwater measurements,
an additional correction was necessary. When the beetle was submerged
underwater, its contact line at the water surface shifted, which influenced
the force readout due to surface tension effects. This effect needed
to be canceled. So, a ``background'' force data was recorded, where
the submerged beetle makes no contact with the substrate. This background
data was then subtracted from a typical force data with substrate
contact to correct for the external surface tension effects. The pull-off
force was subsequently calculated from the minima as before.

Data sets were compared for statistical differences using pairwise
Student t-test and their corresponding p-value and Common Language
Effect Size (CLES) are reported. Shapiro-Wilk test was done for each
data set to verify a normal distribution of its residuals and Levene's
test was done to check for variance homogeneity, to validate the t-test
assumptions. Bonferroni's correction was used to account for multiple
comparison between groups.

\subsection{Results}

\subsubsection{Field desorption mass spectroscopy}

Molecular weights of the secreted fluid mixtures extracted from an
Asian ladybird's leg, without and after immersion in water are compared
(Table \ref{tab:Molecular-distribution-of}). Except for two molecular
weights (406.8 g/mol and 331.6 g/mol), the chemical fingerprint remained
unchanged, indicating that the adhesion fluid was not washed away
underwater. Probable compounds in the fluid, corresponding to the
resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes.

\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|}
\hline 
Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
\hline 
\hline 
324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
\hline 
 & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
\hline 
350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
\hline 
352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
\hline 
378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
\hline 
404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
\hline 
406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
\hline 
432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
\hline 
\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
with and without rinsing the beetle's leg in water. Molecular weights
were extracted from the peaks in the FDMS spectra. \label{tab:Molecular-distribution-of}}
\end{table}

\subsubsection{Adhesion measurements}

Adhesion force for the distal pad of ladybug beetle against glass
and PFOTS in air and underwater conditions are compared (Figure \ref{fig:Effect-of-contact}
and Table \ref{tab:Statistical-analysis}). In air, there is no significant
difference in the adhesion force between glass and PFOTS substrate
(p = 0.959). Underwater however, when there is no trapped bubble,
adhesion on a PFOTS surface is significantly larger than on glass
(p < 0.001). On PFOTS, there is no significant difference in the adhesion
force in air or underwater conditions. But on glass, adhesion in air
is significantly larger than underwater, either in the presence (p
= 0.002) or absence (p < 0.011) of the bubble. At the same, we see
that the presence of the bubble results in a higher adhesion force
than with no bubble (CLES = 0.84) on glass, although the difference
is not statistically significant (p = 0.07).

\begin{table}[H]
\noindent \begin{centering}
\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|}
\hline 
Fixed & A & B & p-value & CLES\tabularnewline
\hline 
\hline 
In air & PFOTS & Glass & 0.959 & 0.48\tabularnewline
\hline 
Underwater: bubble & PFOTS & Glass & 0.011 & 0.96\tabularnewline
\hline 
Underwater: no bubble & PFOTS & Glass & \textbf{< 0.001} & 1.0\tabularnewline
\hline 
PFOTS & In air & Underwater: bubble & 0.897 & 0.48\tabularnewline
\hline 
PFOTS & In air & Underwater: no bubble & 0.828 & 0.48\tabularnewline
\hline 
PFOTS & Underwater: bubble & Underwater: no bubble & 0.721 & 0.44\tabularnewline
\hline 
Glass & In air & Underwater: bubble & \textbf{0.002} & 1.0\tabularnewline
\hline 
Glass & In air & Underwater: no bubble & \textbf{< 0.001} & 1.0\tabularnewline
\hline 
Glass & Underwater: bubble & Underwater: no bubble & 0.07 & 0.84\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\caption{Pairwise statistical comparison of single leg adhesion force of the
beetle for each contact type and substrate. The uncorrected p-values
and Common Language Effect Size (CLES) are obtained from post-hoc
pair-wise Student t-test between A and B while keeping the third parameter
fixed. p-values showing statistically significant difference between
A and B are in boldface. The condition for statistical significance
is based on the Bonferroni-corrected critical p-value of 0.008.\label{tab:Statistical-analysis}}
\end{table}
\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Single leg adhesion force measurements
of ladybug beetle (\emph{Coccinella septempuctata}) on glass and PFOTS
substrates in air and underwater conditions. Values represent peak
force of a distal pad pulled off from each substrate. Three types
of contact are seen in underwater experiments and are represented
separately: \textquotedblleft\emph{bubble}\textquotedblright , \textquotedblleft\emph{no
bubble}\textquotedblright{} and \textquotedblleft\emph{bad contact}\textquotedblright .
Stars represent theoretical predictions of adhesion force calculated
from the capillary bridge model, where hair diameter = 4 \textgreek{m}m,
pad diameter = 200 \textgreek{m}m, hair height = 40 \textgreek{m}m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the adhesive fluid in air and water are assumed to be 24
mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
\end{figure}

Apart from the three predicted contact types, we also observed an
additional fourth type of contact which sometimes occurs underwater,
labeled as ``\emph{bad contact}''. In this scenario, the ventral
view recordings show that the hairs don't appear to contact well with
the substrate, unlike the other three contact types. ``\emph{Bad
contact}'' shows no adhesion with either glass or PFOTS substrate.
While it's not completely clear why such a contact occurs, there can
be two possible reasons. First, the hairs could get bundled due to
a small air meniscus within the hairs, resulting in their disorientation.
Second, a thin water layer at the substrate interface might not be
drained out to allow the hairs to make contact with the substrate,
resulting in a loss of adhesion.

\section{Theory}

\subsection{Capillary Bridge Model}

We model the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$, as shown in figure \ref{fig:Model}. The hairs and the pad
are assumed to be perfectly rigid, for simplicity. The tip of each
hair has an adhesive fluid of volume, $V_{f}$, making contact with
the substrate. The fluid is pinned to the circumference of the hair
and forms a capillary bridge of height, $d$. Similar to our experiments,
we consider three types of contacts for the pad: 1) \emph{In air},
2) \emph{Underwater: no bubble} and 3) \emph{Underwater: bubble}.
In the third case, a bubble of volume, $V_{b}$, is trapped between
the hairs and pinned to the pad circumference.

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate in three ways: a) \emph{In air}, where the adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the adhesive fluid bridges are
inside the bubble while others are outside in water. The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}
Let $V_{f}=\frac{4}{3}\pi s_{f}^{3}$ and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$,
where $s_{f}$ and $s_{b}$ are the radii of spheres with equivalent
volumes. Fluid and bubble radii are assumed to scale proportional
to their corresponding pinned contact diameter. We thus defined the
size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$ and $\phi_{b}=D_{p}/\left(2s_{b}\right)$
for the fluid and bubble respectively, to conveniently scale their
volumes relative to the hair and pad diameters they were pinned to.

The net force for cases 1 and 2 can be calculated as:

\begin{equation}
F_{net}=Nf\label{eq:f_air/water}
\end{equation}

Here, $f$ is the capillary force of a single fluid bridge at a distance,
$d$, in air ($f_{air}$) or underwater ($f_{water}$).

For case 3, the net force is given by:

\begin{equation}
F_{net}=N_{in}f_{air}+N_{out}f_{water}+f_{bubble}\label{eq:f_bubble}
\end{equation}

Here, $N_{in}$ and $N_{out}$ are the number of hairs inside and
outside the bubble, respectively, $f_{air}$ and $f_{water}$ are
the capillary forces of the fluid bridge inside and outside the bubble,
respectively, and $f_{bubble}$ is the capillary force contribution
due to the bubble meniscus alone at distance $d+L$.

The capillary force, $f$, is the sum of two contributions: surface
tension and Laplace pressure. Force versus distance for a single capillary
bridge is calculated by Surface Evolver simulations\cite{RN206},
(described in \ref{subsec:Simulation-Method}) and used to obtain
$F_{net}$ as a function of $d$ for each type of contact. The adhesion
force of the complete hairy pad system is then obtained from the minima
of $F_{net}$, where negative force values represent attraction.

We have considered $f_{air}$ and $f_{water}$ to be distinct terms
because the capillary force by the adhesive fluid will be different
in air and underwater due to its different contact angle and interfacial
tension in each case. Using the Young-Dupr\textcyr{\`\cyre} equations,
one can derive the following relation for the contact angle of the
adhesive fluid underwater:

\begin{equation}
\cos\theta_{fw}=\frac{\gamma_{fa}\cos\theta_{fa}-\gamma_{wa}\cos\theta_{wa}}{\gamma_{fw}}\label{eq:theta_fw}
\end{equation}

Here, $\theta_{fw}$ and $\theta_{fa}$ are the contact angles of
the adhesive fluid with the substrate in water and air respectively,
$\theta_{wa}$ is the contact angle of water with the substrate in
air, $\gamma_{fa}$ is the surface tension of the adhesive fluid,
$\gamma_{wa}$ is the surface tension of water and $\gamma_{fw}$
is the interfacial tension of the adhesive fluid with water.

All lengths are normalized w.r.t. $s_{f}$ and forces are normalized
w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values are fixed relative
to $\gamma_{fa}$. Non dimensional bubble volume is expressed as,
$\hat{V}_{b}=V_{b}/s_{f}^{3}$

Geometric parameters and interfacial properties are kept fixed for
all model calculations (Table \ref{tab:Model-parameters}). Here,
we assume the adhesive fluid to be an oil-lke substance and thus the
interfacial tension ratios $\gamma_{wa}/\gamma_{fa}$ and $\gamma_{fw}/\gamma_{fa}$
are taken corresponding to typical values of oil and water. We consider
representative hydrophilic and hydrophobic substrates with $\theta_{fa}$
and $\theta_{wa}$ values corresponding to a typical glass and fluorinated
surface, respectively. Area fraction of the hairs relative to the
pad, $\alpha=ND_{h}^{2}/D_{p}^{2}$, hair aspect ratio, $L/D_{h}$,
and fluid size parameter, $\phi_{f}$, are fixed to values typical
for a ladybug's hairy pad.

First, we calculate force-distance curves for a single pinned liquid
capillary bridge. Second, the effect of substrate on the force-distance
curves of the hairy pad system is compared for each type of contact.
Third, the effect of varying hair diameter, $D_{h}$, on net adhesion
is studied. Finally, we look at the effect of changing the bubble
volume, $\hat{V}_{b}$, on the net underwater adhesion.

\begin{table}[H]
\centering{}%
\begin{tabular}{|l|c|}
\hline 
Property & Value\tabularnewline
\hline 
\hline 
Area fraction, $\alpha$ & 0.1\tabularnewline
\hline 
Hair aspect ratio, $L/D_{h}$ & 10\tabularnewline
\hline 
Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\tabularnewline
\hline 
Fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\tabularnewline
\hline 
Fluid size parameter, $\phi_{f}$ & 2\tabularnewline
\hline 
Hydrophilic substrate & $\theta_{fa}=6\lyxmathsym{\textdegree}$, $\theta_{wa}=24\lyxmathsym{\textdegree}$\tabularnewline
\hline 
Hydrophobic substrate & $\theta_{fa}=50\lyxmathsym{\textdegree}$, $\theta_{wa}=120\lyxmathsym{\textdegree}$\tabularnewline
\hline 
\end{tabular}\caption{\label{tab:Model-parameters}Fixed parameters of the capillary bridge
model}
\end{table}

\subsection{Results}

\subsubsection{Capillary force of a pinned liquid bridge\label{subsec:Capillary-force-of}}

Forces due to a single pinned capillary liquid bridge in contact with
a substrate are obtained via simulations (Figure \ref{fig:Single-bridge}).
Capillary forces are more attractive for smaller contact angles. The
Laplace pressure contribution to the net adhesion force dominates
for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
Interestingly, its contribution to the adhesion force is mostly non-repulsive
for contact angles greater than 90\textdegree . This is because, the
low volume of the liquid and its pinned contact line prevents the
meniscus from having a high positive curvature due to geometric constraints.
Only for a contact angle of 150\textdegree , the liquid's curvature
becomes positive, manifested in its slightly repulsive Laplace contribution.
Surface tension makes a significant contribution to the net force
only for a small range of contact angles close to 90\textdegree .
For contact angles greater than 150\textdegree , the net adhesion
force approaches zero. We see that, generally, the shape of the liquid
meniscus determines the strength of its adhesion force. High adhesion
is thus seen for contact angles less than $\sim$ 70\textdegree{}
due to a net negative curvature of the meniscus, while low adhesion
is seen for contact angles greater than $\sim$ 150\textdegree{} due
to its net curvature being close to zero.

\begin{figure}[H]
\begin{minipage}[t]{0.5\columnwidth}%
\includegraphics[scale=0.5]{Figure4a-Single_bridge_fd}

\subcaption{Force-distance curves}%
\end{minipage}\hfill{}%
\begin{minipage}[t]{0.5\columnwidth}%
\includegraphics[scale=0.5]{Figure4b-Single_bridge_force_contribution}

\subcaption{Force contributions}%
\end{minipage}\caption{\label{fig:Single-bridge}Normalized capillary force of a single liquid
bridge in contact with a substrate and pinned to a circular perimeter
on top. Fluid size parameter, $\phi_{f}=2$. Negative force values
represents attraction. a) Force-distance curves are shown for different
contact angles of the liquid with the substrate. b) Adhesion force,
calculated from the minima of the corresponding force-distance curve,
is plotted as a function of contact angle with the substrate, together
with its Laplace and surface tension components (equation \ref{eq:f_bridge}).
Simulation snapshots of the liquid meniscus corresponding to angles
6\textdegree{} and 150\textdegree{} are depicted.}
\end{figure}

The force-distance curves show a general trend of being repulsive
at small distances (Figure \ref{fig:Single-bridge}a). This is a result
of the pinned contact line on the top. A limited volume is available
for the liquid to occupy when the gap distance is small, causing the
meniscus shape to bulge outwards near the pinned contact line. This
creates a net positive curvature, resulting in a positive Laplace
pressure and thus repulsion.

\subsubsection{Capillary Bridge Model: Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}

The normalized force-distance curves of a hairy pad system on a hydrophilic
and hydrophobic substrate are predicted based on the capillary bridge
model and compared for the different contact types (Figure \ref{fig:Effect-of-substrate}).
The forces in each case are calculated from equations (\ref{eq:f_air/water})
and (\ref{eq:f_bubble}) for fixed geometric and interfacial properties
(Table \ref{tab:Model-parameters}).

On the hydrophilic substrate ($\theta_{wa}=24\lyxmathsym{\textdegree}$),
contact\emph{ in air} shows the highest adhesion. \emph{Underwater:
no bubble} shows close to no adhesion while \emph{underwater: bubble}
shows moderate adhesion. In contrast, for a hydrophobic substrate
($\theta_{wa}=120\lyxmathsym{\textdegree}$), the highest adhesion
is seen for \emph{underwater: no bubble}, much larger than \emph{in
air}. Even \emph{underwater: bubble} has slightly higher adhesion
than \emph{in air}. Note that the contact area is fixed by keeping
the area fraction and $D_{p}/D_{h}$ constant. All curves correspond
to the same total hair contact area. Thus, the above mentioned effects
are attributed solely to how the the capillary force changes in each
scenario.

On a hydrophilic substrate, the contact angle of the oily adhesive
fluid is 6\textdegree , when surrounded by air (Table \ref{tab:Model-parameters})
and 150\textdegree , when surrounded by water (equation (\ref{eq:theta_fw})).
This results in the meniscus shape to have a net negative and slightly
positive curvatures, respectively, resulting in strong adhesion in
air and poor adhesion underwater. On a hydrophobic substrate however,
the contact angles of the fluid in air and water are 50\textdegree{}
and 1\textdegree , respectively. In both cases, the contact angles
are low, resulting in strong adhesion in both media. Additionally,
the interfacial tension of the oily fluid underwater ($\gamma_{fw}$)
is twice that of in air ($\gamma_{fa}$). Thus, we see a higher capillary
adhesion for the \emph{underwater: no bubble} case when compared to
\emph{in air} (Figure \ref{fig:Oil-contact-images}).

\begin{figure}[H]
\centering{}\includegraphics{Figure5-Model_effect_of_substrate}\caption{\label{fig:Effect-of-substrate}Theoretical force-distance curves
of a hairy pad system on a hydrophilic and hydrophobic substrate in
air and underwater conditions. A negative force value represents attraction.
Normalized forces are calculated from the capillary bridge model,
with model parameters listed in Table \ref{tab:Model-parameters}.
The bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Insets represent the \emph{underwater:
bubble }contact for each substrate.}
\end{figure}

The net force in the \emph{underwater: bubble} case mainly depends
on the proportion of hairs inside and outside the bubble (equation
(\ref{eq:f_bubble})). For the given bubble volume, only part of the
hairs are inside the bubble for the hydrophilic substrate, while,
all the hairs are inside the bubble for the hydrophobic substrate.
Therefore, the force curve lies between \emph{in air} and \emph{underwater:
no bubble} cases for a hydrophilic substrate, and closely follows
the \emph{in air} case for a hydrophobic substrate.

The contribution of the capillary force due to the bubble itself is
negligible for both substrates (Figure \ref{fig:Effect-of-substrate}).
Its contribution even is slightly repulsive on the hydrophilic substrate
due to the positive curvature of the bubble, and slightly attractive
on the hydrophobic substrate due to its negative curvature. This small
contribution is manifested by the slightly higher adhesion for \emph{underwater:
bubble} relative to \emph{in air} for the hydrophobic substrate, since
all hairs are within the bubble in this case.

\subsubsection{Capillary Bridge Model: Effect of bubble volume}

The effect of varying bubble volume, $\hat{V}_{b}$, on the net adhesion
force of the \emph{underwater: bubble} case are compared for hydrophilic
and hydrophobic substrates (Figure \ref{fig:Effect-of-bubble}). From
previous section, we know that on the hydrophilic substrate, fluid
bridges outside the bubble show poor adhesion due to the positive
curvature of their meniscus. Thus, decreasing $\hat{V}_{b}$ decreases
the adhesion force due to a larger proportion of hairs being outside
the bubble. In contrast, on the hydrophobic substrate, fluid bridges
outside the bubble show higher capillary forces, due to its low contact
angle and high interfacial tension in water. Thus, adhesion force
increases for a hydrophobic substrate as the bubble size decreases.

\begin{figure}[H]
\includegraphics{Figure7-Model_effect_of_bubble_volume}\caption{\label{fig:Effect-of-bubble}Normalized adhesion force of a hairy
pad system as a function of bubble volume, $\hat{V}_{b}$, for the
\emph{underwater: bubble} contact type. Adhesion forces are calculated
from the minima of the respective force-distance curves. Negative
force value represents attraction. Pad to hair diameter ratio ($D_{p}/D_{h}$)
is kept fixed. Highlighted regions represent entrapment of all hairs
within the bubble.}
\end{figure}
The contribution of the bubble to the net adhesion force is small
regardless of its volume, when compared to the whole pad. We see that
a smaller $\hat{V}_{b}$ results in increased attraction by the bubble
on both types of substrates. For larger values of $\hat{V}_{b}$,
the force trend for the whole pad mostly follows that of the bubble,
because the bubble in this case is big enough to entrap all the hairs
inside it. Thus, the force contribution due to the fluid bridges remain
unchanged, and only the bubble's contribution drives the slight variation
in the pad's adhesion at high $\hat{V}_{b}$. Once the bubble is small
enough such that part of the fluid bridges start making contact in
water, the force trend changes, with a steep decrease (increase) in
adhesion force on hydrophilic (hydrophobic) substrate as the volume
decreases.

\subsubsection{Capillary Bridge Model: Effect of hair diameter }

The effect of changing hair diameter, $D_{h}$, to the net adhesion
force is compared for hydrophilic and hydrophobic substrates (Figure
\ref{fig:Effect-of-hair}). Here, the pad diameter, total hair contact
area and bubble volume are constant since $D_{p}$, $\alpha$ and
$\hat{V}_{b}$ are kept fixed. The radius corresponding to the fluid
volume is assumed to scale proportional to the hair diameter and is
fixed ($\phi_{f}=2$).

Adhesion force increases with decreasing $D_{h}$ for both hydrophilic
and hydrophobic substrates in all contact types. This is consistent
with the ``contact splitting'' theory, which predicts higher adhesion
when the contact is split into many small contact points\cite{RN24}.
Reducing the hair diameter results in two competing effects: 1) capillary
force due to a single fluid bridge decreases due to its smaller size
and ``self-similar'' scaling assumption ($f\sim D_{h}$), which
decreases the net force, and 2) total number of fluid bridges increases
since the total hair contact area is assumed to be fixed ($N\sim1/D_{h}^{2}$),
which increases the net force. The second effect dominates, resulting
in a higher adhesion force as $D_{h}$ decreases.

\begin{figure}[H]
\includegraphics[scale=0.5]{Figure6-Model_effect_of_hair_size}\caption{\label{fig:Effect-of-hair}Normalized adhesion force of a hairy pad
system on a hydrophilic and hydrophobic substrate as a function of
hair diameter, $D_{h}$. Volume of each fluid bridge, $V_{f}$, scales
relative to $D_{h}$ based on the parameter $\phi_{f}=2$. Adhesion
forces are calculated from the minima of the respective force-distance
curves, based on the capillary bridge model. A negative value represents
attraction. The bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Pad diameter and bubble
volume are kept fixed. All lengths are scaled relative to $D_{p}$.}
\end{figure}

Similar to the trend in Figure \ref{fig:Effect-of-substrate}, contact
\emph{in air} shows the highest adhesion force on a hydrophilic substrate
for the given range of hair diameters, while on a hydrophobic substrate,
\emph{underwater: no bubble} shows highest adhesion. \emph{Underwater:
bubble} contact shows intermediate adhesion between \emph{in air}
and \emph{underwater: no bubble} contact types.

The bubble's contribution gets repulsive as hair diameter decreases
for both substrates (Figure \ref{fig:Effect-of-hair}). Since the
aspect ratio $L/D_{h}$ is fixed (Table \ref{tab:Model-parameters}),
decreasing the hair diameter also decreases its length. Since the
bubble's volume is kept constant, it will then have a lesser space
available to occupy between the pad and the substrate, This results
in it bulging outwards near the pinned contact line on the top. Thus,
the bubble's contribution gets repulsive as hair diameter decreases.

\section{Discussion}

Our experiments demonstrate, for the first time, that the ladybug
beetle can attach underwater to a hydrophobic substrate even without
a bubble trapped around its hairs. A previous study\cite{RN87} had
hypothesized that a bubble is necessary for underwater attachment
in beetles. This is, however, only true for hydrophilic substrates,
where a trapped bubble can facilitate underwater adhesion due to the
hairs making contact in a dewetted environment. For a hydrophobic
substrate, the adhesion is similar regardless of whether the contact
occurs in air or underwater conditions, with or without a trapped
bubble. Our theoretical calculations further show that the bubble
by itself has a negligible capillary contribution to the net underwater
adhesion of the pad. Direct force measurement of a single similarly
sized bubble making contact with a hydrophobic substrate shows a maximum
adhesion less than 50 \textgreek{m}N, which further validates that
the bubble's contribution is insignificant (\ref{subsec:Capillary-force-due}).

Predictions of the ladybug's adhesion from the capillary bridge model
follow our experimental results (Figure \ref{fig:Effect-of-contact}).
In underwater conditions without a trapped bubble, adhesion on a hydrophobic
substrate is significantly larger than on a hydrophilic substrate.
This is explained by the different oil interfacial tension and contact
angles with the substrates in air and underwater, which determines
the capillary adhesive force in each case (Figure \ref{fig:Oil-contact-images}).
However, the experiments don't show the predicted $\sim$ 2.6 times
increase in underwater adhesion relative to that in air on the hydrophobic
PFOTS surface. This discrepancy could be due to our assumptions of
the oily fluid's interfacial properties. If we choose $\gamma_{fa}$=30
mN/m and $\gamma_{fw}$=40 mN/m, the corresponding increase in adhesion
will be $\sim$ 1.7, closer to our experimental value of $\sim$ 1.
The resulting change in $\theta_{fa}$ and $\theta_{fw}$ will further
decrease this number. Direct measurement of the fluid's interfacial
properties is thus essential to better predict the insect's adhesion,
and will be a subject of future study. Further, due to surface inhomogeneities,
not all the hairs might be able to completely drain the interfacial
water layer, in order for the adhesive fluid to make a direct contact
with the substrate. This can further reduce underwater adhesion, in
comparison to our theoretical predictions which assumes a perfect
contact.

\begin{figure}[H]
\includegraphics{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
meniscus in contact with glass and PFOTS in air and underwater conditions.
The corresponding interfacial tension, \textgreek{g}, and contact
angle, \ensuremath{\theta}, used to predict the ladybug's adhesion
are labeled for each case.}
\end{figure}

In the model, we assume that all the hairs detach simultaneously to
give a theoretical maximum achievable adhesion force. In our experiments,
however, the pad always makes contact with the substrate at a random
orientation, which is difficult to control precisely. During detachment,
the pad typically peels off from its proximal to distal end rather
than detach simultaneously. Our model also assumes the hairs to be
of similar geometry, unlike the beetle's pad which has a distribution
of flat or pointed tipped hairs. Thus, it's not surprising that the
model overestimates the adhesion forces. The predictions are however
in the same order of magnitude as experiments, and the qualitative
trend is consistent for both hydrophilic and hydrophobic substrates
in air and underwater.

Our study provides further validation that capillary forces by the
adhesive fluid control the insect's adhesion and van der Waals contribution,
if any, must be negligible. Further, the capillary forces can even
enable insect attachment underwater depending on the substrate chemistry.
When underwater, without a trapped bubble, the pad adheres strongly
to a hydrophobic substrate, but poorly to a hydrophilic substrate,
even though it shows similarly strong adhesion to both substrates
in air. This behavior can only be explained by capillary forces. Our
preliminary FDMS results further provides validation to our assumption
that the adhesive fluid can form capillary bridges with the substrate
in water, instead of getting washed away (Table \ref{tab:Molecular-distribution-of}).

The findings can also be extended to other animals relying on oily
secretions for adhesion. Ants, for example, show similar adhesion
on hydrophobic substrates under wet and dry conditions\cite{RN213},
similar to what we see in a ladybug. Recent adhesion experiments on
geckos reveal that they can attach well to fluoropolymer substrates
underwater while they show little adhesion to the same substrate in
air\cite{RN199,RN15}. Geckos are thought to rely on van der Waals
forces via dry contact with the substrate \cite{RN202}, although
recent observations of phospholipid footprints left behind walking
geckos \cite{RN205} could change that picture. Since geckos adhere
poorly to PTFE (surface energy \textasciitilde{} 20 mN/m) one can
speculate that the phospholipid material has a higher surface energy,
and consequently makes a higher contact angle with PTFE in air. Let
us assume the phosopholipid substance to be a fluid similar to oil
with $\gamma_{fa}$= 30 mN/m and $\gamma_{fw}$= 42 mN/m such that
its contact angle with PTFE is 80\textdegree . Equation \ref{eq:theta_fw}
then gives us an underwater contact angle of 70\textdegree{} for the
phospholipid fluid. Thus, on a PTFE surface, the capillary bridge
model can predict a higher adhesion underwater than in air due to
its lower contact angle and higher interfacial energy underwater.
Based on similar assumptions, we predict the net adhesion force for
the gecko on different substrates (Figure \ref{fig:Comparison-with-model}).
The adhesion force predictions are in good qualitative agreement with
the whole animal experimental shear force values reported for the
gecko, with the trend of higher adhesion in air than underwater for
glass, similar adhesion in air and underwater for PMMA/OTS-SAM and
lower adhesion in air than underwater for PTFE. We, thus, propose
that the underwater experiments performed on geckos \cite{RN199,RN15}
indicate a capillary contribution to gecko adhesion. We suggest performing
single seta adhesion force tests similar to Autumn et. al. \cite{RN202}
using a hydrophilic and fluorinated probe in air and underwater conditions
to validate the role of capillary contributions to gecko adhesion.

\begin{figure}[H]
\includegraphics{Figure-9-Gecko_comparison}\caption{\label{fig:Comparison-with-model}Whole animal adhesion force of geckos
on various substrates. Experimental shear adhesion values are reproduced
from Stark et. al. \cite{RN15}. Normal adhesion forces for each gecko
toe are theoretically estimated from the capillary bridge model, with
hair diameter = 400 nm, toe diameter = 4 mm, adhesive fluid volume
= 4.19x10\protect\textsuperscript{-3} fL and 10\% hair coverage.
\textquotedblleft\emph{Underwater: no bubble}\textquotedblright{}
type contact is assumed for the \textquotedblleft Wet\textquotedblright{}
case. Net adhesion force is calculated by assuming 5 toes on each
leg and 4 legs in total on a gecko. Interfacial tension of the phospholipid
layer (PL) in air and water are assumed to be 30 mN/m and 42 mN/m
respectively. PL contact angles with glass, PMMA, OTS-SAM and PTFE
are assumed to be 6\textdegree , 10\textdegree , 20\textdegree{} and
80\textdegree{} respectively. The corresponding water contact angles
are 50\textdegree , 85\textdegree , 94\textdegree{} and 97\textdegree{}
respectively, as reported in Stark et. al. \cite{RN15}.}
\end{figure}

We have so far limited our analysis to only smooth substrates. Insects
in the real world, however, interact with rough substrates very often.
Previous studies \cite{RN136} have shown that substrate roughness
is a more dominant parameter than substrate chemistry in controlling
insect adhesion. Future work will explore how roughness can impact
the net capillary force. Our study can have potential applications
in the design of bio-inspired materials to achieve underwater adhesion
via capillary bridges. Bubble can possibly be used to control underwater
adhesion by changing the relative proportion of the arrays inside
and outside the bubble. A suitable choice of adhesive fluid can be
made tailored to the substrate and environment of application to achieve
optimal adhesion performance.

\section{Conclusions}

Our study illustrates that the ladybug beetle relies primarily on
its oily fluid secretion to achieve adhesion in both air and underwater
conditions. The beetle can attach underwater on a hydrophobic substrate
even without a trapped air bubble within its hairy pad, although it
loses this ability on a hydrophilic substrate. This is explained theoretically
by the different contact angle and interfacial tension of the adhesive
fluid in air and underwater conditions. Further, the bubble itself
has a negligible capillary contribution to the total force. The trapped
bubble can promote adhesion only on a hydrophilic substrate by providing
an air medium to the adhesive fluid bridges inside it. Oil wettability,
thus, primarily controls the insect's adhesion in any given condition.
A similar argument also explains previously reported underwater measurements
in geckos \cite{RN15}, which highlights the possibility of capillary
contributions to gecko adhesion. Future studies should characterize
the fluid secretion's interfacial properties with a particular substrate
to better understand the nature of the animal's adhesion.

\section{Acknowledgement}

We are grateful to Eduard Arzt and Ren\textcyr{\`\cyre} Hensel for
fruitful discussions. This work was funded by \emph{Deutsche Forschungsgemeinschaft}
(Grant number: PI 1351/2-1).

\appendix

\section{Appendix}

\subsection{Simulation method: Single capillary bridge \label{subsec:Simulation-Method}}

\setcounter{figure}{0} \renewcommand{\thefigure}{A.\arabic{figure}} 
\setcounter{equation}{0} \renewcommand{\theequation}{A.\arabic{equation}} Capillary
force due to a single adhesive fluid or bubble meniscus (termed ``capillary
bridge'') is calculated by performing simulations in Surface Evolver
\cite{RN206}, similar to the method described by De Souza et. al.\cite{RN93}.
A simple cubic geometry, mimicking the capillary bridge, of constant
volume, $V$, is defined as the initial condition with an interfacial
tension, $\gamma$, with the surrounding medium. Interfacial tension
of the capillary bridge with the substrate is given by $\gamma\cos\theta$,
where $\theta$ is the corresponding contact angle inside the bridge.
For the case of a bubble meniscus, $\theta$ is defined w.r.t. the
surrounding water, since $\theta$ can also directly characterize
the substrate wettability. The capillary bridge spans a gap distance
$d$ between the top face and the substrate. The boundary conditions
are set corresponding to a pinned contact line of diameter $D$ on
the top face and constant interfacial tension with the substrate on
the bottom. All lengths are normalized relative to length $s=\left(3V/4\pi\right)^{1/3}$.
An appropriate geometry refinement routine is chosen to evolve the
capillary bridge shape to its minimum energy state. The normalized
total capillary force, $\hat{f}=f/\gamma s$, is the sum of the Laplace
pressure and surface tension contributions , where:

\begin{equation}
f=f_{laplace}+f_{surface\,tension}=\varDelta P_{laplace}A_{_{bottom}}+2\pi R_{bottom}\gamma\sin\theta\label{eq:f_bridge}
\end{equation}

Here, $\varDelta P_{laplace}$ is the Laplace pressure of the equilibrium
capillary bridge, $A_{bottom}$ is the contact area of the capillary
bridge with the substrate at bottom and $R_{bottom}$ is the corresponding
radius of contact, all obtained from the simulation output for the
equilibrium surface.

The gap distance $d$ is varied stepwise and the capillary force is
calculated each time to obtain force-distance curves for a particular
choice of $D$ and $\theta$.

\subsection{Single capillary bridge: Effect of volume}

Surface Evolver simulation results showing the effect of volume on
the maximum capillary force of a single fluid bridge. Since the fluid
is pinned at the top to the same diameter, D, a smaller volume would
result in high interfacial curvatures, which increases the capillary
force due to the negative Laplace pressure. In this case, small contact
angles lead to a greater increase in adhesion.

\begin{figure}[H]

\begin{centering}
\includegraphics{FigureS2-Effect_of_fluid_volume}\caption{Normalized maximum capillary force for a single bridge as a function
of fluid volume}
\par\end{centering}
\end{figure}

\subsection{Capillary Bridge Model: Effect of hair diameter at constant fluid
volume}

Here, instead of scaling the fluid volume relative to the hair diameter,
we now assume a fixed total fluid volume distributed equally among
the $N$ hairs. Total fluid volume, $V_{total}=NV_{f}=2000$. Hair
diameter is varied while keeping the total hair contact area constant.
Length is in arbitrary units. Forces increase at a much smaller rate
on decreasing diameter when compared to the case with self-similar
scaling of fluid volume (Figure \ref{fig:Effect-of-hair}).

\begin{figure}[H]
\includegraphics{FigureS3-Effect_of_hair_size(constant_vol)}

\caption{Normalized adhesion force of hairy pad system on a hydrophilic and
hydrophobic substrate as a function of hair diameter ($D_{h}$), calculated
from the capillary bridge model. The total adhesive fluid volume is
fixed to 2000. Adhesion forces are calculated from minima of the respective
force-distance curves. Negative force value represents attraction.
The bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Bubble volume and pad
diameter are kept fixed. All lengths are scaled relative to $D_{p}$.}
\end{figure}

\subsection{Capillary force due to a bubble\label{subsec:Capillary-force-due}}

Capillary force of a single bubble against a PFOTS surface are compared
for two different volumes. The volumes correspond to the expected
range in the case of the trapped bubble in a ladybug. Here, the bubble
is pinned to a micropatterned PDMS substrate on the top. The maximum
adhesion force of any of the bubble never exceeds 50 \textgreek{m}N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textgreek{m}N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible.

\begin{figure}[H]
\begin{centering}
\includegraphics{FigureS4-Expt_bubble_force}\caption{Capillary force of the bubble}
\par\end{centering}
\end{figure}

\bibliography{references}

\end{document}

### 2021-02-10 source/tex/ladybug_adhesion.tex

@@
 
-\author{Thomas Endlein}
+\author{Bat-El Pinchasik}
+
+\affiliation{School of Mechanical Engineering, Tel Aviv University, Tel Aviv-Yafo,
+Israel}
+
+\author{Hans-J\"{u}rgen Butt}
 
@@
 
-\author{Bat-El Pinchasik}
-
-\affiliation{School of Mechanical Engineering, Tel Aviv University, Tel Aviv-Yafo,
-Israel}
-
-\author{Hans-J\"{u}rgen Butt}
+\author{Thomas Endlein}
 
@@
 
-\email{butt@mpip-mainz.mpg.de}
+\email{endlein01@mpip-mainz.mpg.de}
 
@@
 Insects like beetles can stick to various surfaces using hairy pads
-mediated by an oily adhesive fluid. It was previously shown that the
-pads can even attach underwater, presumably due to an air bubble trapped
-around the pad. However, the bubble's relative contribution to adhesion
-via capillary force remains unclear. To investigate the exact role
-of bubble, in this study, we perform\emph{ in-vivo} underwater adhesion
-measurements of a ladybug's pad, in the presence and absence of the
-trapped bubble and compare it with its adhesion in air. Our experiments
-reveal that on a hydrophobic substrate, even without a bubble, the
-pad can show adhesion underwater comparable to that in air. On a hydrophilic
-substrate, underwater adhesion is significantly reduced, with or without
-a trapped bubble. To explain these results, we develop a simple theoretical
-model to estimate the net adhesion of a hairy pad due to capillary
-forces. Our results demonstrate that the wetting properties of the
-adhesive fluid determines the insect's adhesion in both air and underwater
-conditions.
+on their legs. It was previously shown that these pads can even attach
+underwater, presumably due to an air bubble trapped around the pad.
+However, the bubble's contribution to adhesion via capillary force
+remained unclear. To investigate the role of the bubble, we measured\emph{
+in-vivo} underwater adhesion of a ladybug's pad, in the presence and
+absence of the trapped bubble and compare it with its adhesion in
+air. Our experiments reveal that on a hydrophobic substrate, even
+without a bubble, the pad can show adhesion underwater comparable
+to that in air. On a hydrophilic substrate, underwater adhesion is
+significantly reduced, with or without a trapped bubble. To explain
+these results, we develop a simple theoretical model for the net adhesion
+of a hairy pad due to capillary forces. Our results demonstrate that
+the wetting properties of the adhesive fluid determines the insect's
+adhesion in both air and underwater conditions.
 \end{abstract}
@@
 
-The question of how insects can walk on smooth surfaces against gravity
-has fascinated scientists for at least the past three centuries \cite{RN198,RN59}.
-We now know that such animals are able to adhere by using specialized
-organs on their feet called adhesive pads. These adhesive pads exist
-in a variety of types depending on the animal, but are generally categorized
-into: 1) ``smooth pads'' found in ants\cite{RN201}, stick insects
-\cite{RN182}, etc. and 2) ``hairy pads'' seen in flies \cite{RN155},
-geckos \cite{RN202} and others. The hairy pads show: 1) compliance
-to rough surfaces due to their lower effective modulus, 2) angle dependent
-adhesion due to asymmetric hair geometry and 3) self-cleaning capability
-\cite{RN20}, which makes them suitable to adhere to most surfaces
-reversibly. Many of these insects pads also secrete an adhesive fluid,
-as seen in flies and ants \cite{RN201} (``wet adhesion''), while
-others such as spiders and geckos rely on their dry hairy pads for
-attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid
-secretion can enforce adhesion through surface tension and viscous
-forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van
-der Waals forces \cite{RN202}.
+The question of how insects and other small animals can walk on smooth
+surfaces against gravity has fascinated scientists for at least the
+past three centuries \cite{RN198,RN59}. We now know that such animals
+are able to adhere by using specialized organs on their feet called
+adhesive pads. These adhesive pads exist in a variety of types depending
+on the animal, but are generally categorized into: 1) ``smooth pads''
+found in ants\cite{RN201}, stick insects \cite{RN182}, etc. and
+2) ``hairy pads'' seen in flies \cite{RN155}, geckos \cite{RN202}
+and others. The hairy pads show: 1) compliance to rough surfaces due
+to their lower effective modulus, 2) angle dependent adhesion due
+to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20},
+which makes them suitable to adhere to most surfaces reversibly. Many
+of these insects pads also secrete an adhesive fluid, as seen in flies
+and ants \cite{RN201} (``wet adhesion''), while others such as
+spiders and geckos rely on their dry hairy pads for attachment (``dry
+adhesion''). In the ``wet adhesion'' case, fluid secretion can
+enforce adhesion through surface tension and viscous forces \cite{RN71},
+while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.
 
@@
 on contact. It has been hypothesized that a combination of capillary
-forces due the air bubble and hair contact within the dewetted area
-results in its adhesion underwater. However, a detailed investigation
+forces due the air bubble and hair secretions within the dewetted
+area results in its adhesion underwater. However, a detailed investigation
 of the bubble's contribution and necessity to adhere to different
@@
 The goal of this paper is to provide a generalized picture of adhesion
-in insects which use hairy pads secreting a fluid for attachment.
-First, we perform adhesion measurements of a single constrained pad
-of a live ladybug beetle in air and underwater conditions, both on
-smooth hydrophilic and hydrophobic glass surfaces, with a microscopic
-observation of the contact process. Second, we develop a simple theoretical
-model considering capillary forces to predict the net adhesion force
-of a hairy pad under different conditions. Finally, we discuss key
-insights gained from our experiments and model, as well as possible
-implications in understanding adhesion in other animals.
+for insects which use hairy pads and secrete a oily fluid for attachment.
+First, we measured adhesion of a single constrained pad of a live
+ladybug beetle in air and underwater conditions, both on smooth hydrophilic
+and hydrophobic glass surfaces, with a microscopic observation of
+the contact process. Second, we developed a simple theoretical model
+considering capillary forces to predict the net adhesion force of
+a hairy pad under different conditions. The case of underwater adhesion
+was studied both in the presence and absence of a trapped bubble,
+to decouple the bubble's role in the insect's adhesion. Finally, we
+discuss key insights gained from our experiments and model with regards
+to understanding adhesion in other animals.
 
@@
 
-Seven-spotted adult ladybug beetles (\emph{Coccinella septempuctata})
+Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
 purchased from Katz Biotech (Baruth, Germany) were used for adhesion
@@
 
-Experiments were done on male beetles. Each leg of the beetle has
-a pair of hairy pads covered with mostly discoidal shaped setae, capable
-of strong adhesion. For the test, we only allowed the distal-end pad
-to make contact. The beetle's leg was constrained similar to the method
-described by Bullock et al \cite{RN19}. A steel ball fixed with a
-piece of thick solder wire served as a rotatable holder to fix the
-beetle and align its leg (Figure \ref{fig:Setup}). The beetle was
-first anesthetized using CO\textsubscript{2} sublimating from a piece
-of dry ice and then glued to the steel ball on its back. Its front
-left leg was carefully fixed to the solder wire of the holder using
-Blue-Tac. Its claws were fixed using epoxy glue to prevent any wiggling.
-A small piece of non-sticky Teflon tape helped to keep its other legs
-tucked close to the body and avoid their interference during the adhesion
-test.
+Each leg of the beetle has a pair of hairy pads covered with mostly
+discoidal shaped setae, capable of strong adhesion. For the test,
+we only allowed the distal-end pad to make contact. The beetle's leg
+was constrained similar to the method described by Bullock et al \cite{RN19}.
+A steel ball fixed with a piece of thick solder wire served as a rotatable
+holder to fix the beetle and align its leg (Figure \ref{fig:Setup}).
+The beetle was first anesthetized using CO\textsubscript{2} sublimating
+from a piece of dry ice and then glued to the steel ball on its back.
+Its front left leg was carefully fixed to the solder wire of the holder
+using Blue-Tac. Its claws were fixed using epoxy glue to prevent any
+wiggling. A small piece of non-sticky Teflon tape helped to keep its
+other legs tucked close to the body and avoid their interference during
+the adhesion test.
 
@@
 measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
-De-ionized water and n-hexadecane were used as test liquids. Advancing
+Milli-Q water and n-hexadecane were used as test liquids. Advancing
 and receding contact angles were measured for a maximum drop volume
-of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate. Static
-contact angles were measured for a 5 \textgreek{m}l drop.
+of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate.
 
@@
 \centering{}%
-\begin{tabular}{|c|c|c|c|c|}
-\hline 
-Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R} & \ensuremath{\theta}\textsubscript{S}\tabularnewline
-\hline 
-\hline 
-\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{} & 57\ensuremath{\pm}2\textdegree{}\tabularnewline
-\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
- & n-Hexadecane & <10\textdegree{} & <10\textdegree{} & <10\textdegree{}\tabularnewline
-\hline 
-\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{} & 110\ensuremath{\pm}2\textdegree{}\tabularnewline
-\cline{2-5} \cline{3-5} \cline{4-5} \cline{5-5} 
- & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{} & 72\ensuremath{\pm}2\textdegree{}\tabularnewline
-\hline 
-\end{tabular}\caption{Static and dynamic contact angles measurements \label{tab:Contact-Angles}}
+\begin{tabular}{|c|c|c|c|}
+\hline 
+Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
+\hline 
+\hline 
+\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
+\cline{2-4} \cline{3-4} \cline{4-4} 
+ & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
+\hline 
+\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
+\cline{2-4} \cline{3-4} \cline{4-4} 
+ & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
+\hline 
+\end{tabular}\caption{Dynamic contact angles measurements \label{tab:Contact-Angles}}
 \end{table}
-
-\subsubsection{Field desorption mass spectroscopy}
-
-Field Desorption Mass Spectrometry (FDMS) measurements of the adhesive
-fluid secretions were performed using ZAB 2-SE-FPD spectrometer (VG
-Instruments). A previous study on archanids \cite{RN223} reported
-that the secreted fluid does not dissolve away in water. To confirm
-this for the beetle, measurements before and after the immersion of
-its legs in water were done. The middle leg of an Asian ladybird (\emph{Harmonia
-axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
-to the measurement chamber of the FDMS. As a reference, pure THF was
-used. The second middle leg of the same ladybird was immersed in 100
-\textmu L milli-Q water for 15 min, then in THF for 20 min and then
-transferred to the measurement chamber of the spectrometer. Molecular
-composition was extracted from the peak positions of the FDMS data.
 
@@
 beetle's foot to the substrate. A coaxial illuminated tube microscope
-(\emph{Navitar}) with 2x objective and a stereo-microscope with 1x
-objective (\emph{Wild Heerbrugg}) fit with cameras were used to record
-the sample contact with the substrate from ventral and side views
-respectively. Pad contact area was visualized through the substrate
-in total reflection mode by the ventral view camera. The data acquisition
-from the force sensor and cameras, together with the appropriate piezo
-motion steps were synchronized using a custom LABVIEW program. Force
-data was acquired at a sample rate of 984 Hz, averaged to 512 points
-per motion step. Videos were recorded at 20 frames per second.
+(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
+with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with cameras
+were used to record the sample contact with the substrate from ventral
+and side views respectively. Pad contact area was visualized through
+the substrate in total reflection mode by the ventral view camera.
+The data acquisition from the force sensor and cameras, together with
+the appropriate piezo motion steps were synchronized using a custom
+LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
+averaged to 512 points per motion step. Videos were recorded at 20
+frames per second.
 
@@
 
-For underwater experiments, 1 ml MilliQ water was pipetted into the
+For underwater experiments, 1 ml Milli-Q water was pipetted into the
 substrate holder. In order to achieve an underwater contact without
@@
 \par\end{centering}
-\caption{\label{fig:Setup} Adhesion test setup. Representative force data
-and contact area of distal pad are shown in the plot, in which, the
-shaded regions represent distinct piezo motion steps, negative force
-values represent attraction and the minimum force peak during the
-final retraction step is the adhesion force.}
-\end{figure}
+\caption{\label{fig:Setup} Adhesion test setup. The recorded force data and
+contact area of distal pad are shown in the plot, in which, the shaded
+regions represent distinct piezo motion steps, negative force values
+represent attraction and the minimum force peak during the final retraction
+step is the adhesion force.}
+\end{figure}
+
+\subsubsection{Field desorption mass spectroscopy}
+
+A previous study on archanids \cite{RN223} reported that its secreted
+fluid does not dissolve in water. To confirm if even the beetle retains
+its adhesive fluid underwater, we perform Field Desorption Mass Spectroscopy
+(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
+were done on the extracted secretions before and after rinsing its
+legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
+axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
+to the measurement chamber of the FDMS. As a reference, pure THF was
+used. The second middle leg of the same ladybird was subsequently
+immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
+20 min and then transferred to the measurement chamber of the spectrometer.
+Molecular composition was extracted from the peak positions of the
+FDMS spectra.
 
@@
 
-For measurements in air, pull-off force was defined as the minimum
-negative force during the final retraction step. For underwater measurements,
-an additional correction was necessary. When the beetle was submerged
-underwater, its contact line at the water surface shifted, which influenced
-the force readout due to surface tension effects. This effect needed
-to be canceled. So, a ``background'' force data was recorded, where
-the submerged beetle makes no contact with the substrate. This background
-data was then subtracted from a typical force data with substrate
-contact to correct for the external surface tension effects. The pull-off
-force was subsequently calculated from the minima as before.
+For measurements in air, the pull-off force was defined as the minimum
+negative force during the final retraction step (Figure \ref{fig:Setup}).
+For underwater measurements, an additional correction was necessary.
+When the beetle was submerged underwater, its contact line at the
+water surface shifted, which influenced the force readout due to surface
+tension effects. This effect needed to be canceled. So, a ``background''
+force data was recorded, where the submerged beetle makes no contact
+with the substrate. This background data was then subtracted from
+a typical force data with substrate contact to correct for the external
+surface tension effects. The pull-off force was subsequently calculated
+from the minima as before.
 
@@
 
+\subsubsection{Adhesion measurements}
+
+In air, adhesion forces of the distal pad of ladybug beetle against
+glass and PFOTS are rather similar; no significant differences are
+detected (Figure \ref{fig:Effect-of-contact} and Table \ref{tab:Statistical-analysis}).
+In contrast, underwater adhesion on PFOTS surface is significantly
+larger than on glass (p < 0.001). This stronger adhesion on PFOTS
+is observed both in the presence and absence of a trapped bubble.
+In both cases, adhesion force reach similar values as in air. In contrast,
+on glass, adhesion underwater is significantly reduced as compared
+to dry conditions, irrespective of the presence of a trapped bubble
+(p $\leq$ 0.002). Underwater adhesion on glass tends to be slightly
+higher in the presence of a bubble (CLES = 0.84). However, this difference
+is small and not statistically significant (p = 0.07).
+
+\begin{figure}[H]
+\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing single
+leg adhesion force measurements of ladybug beetle (\emph{Coccinella
+septempuctata}) on glass and PFOTS substrates in air and underwater
+conditions. The two types of contact during underwater experiments
+are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
+and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
+represent theoretical predictions of adhesion force, while, circles
+represent the contribution of the bubble itself, calculated from the
+capillary bridge model. In the model, hair diameter = 4 \textgreek{m}m,
+pad diameter = 200 \textgreek{m}m, hair height = 40 \textgreek{m}m,
+N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
+= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
+tension of the adhesive fluid in air and water were assumed to be
+24 mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
+\end{figure}
+
+Apart from the three depicted contact types, we observed an additional
+fourth type which occurred in roughly 25\% of our underwater experiments.
+In this scenario, the ventral view recordings show that the hairs
+did not appear to contact well with the substrate, unlike the other
+three contact types. This ``bad contact'' scenario shows no adhesion
+with either glass or PFOTS substrate. While it was not completely
+clear why such a contact occurs, there can be two possible reasons.
+First, the hairs could get bundled due to a small air meniscus within
+the hairs, resulting in their disorientation. Second, a thin water
+layer at the substrate interface might not be drained out to allow
+the hairs to make contact with the substrate, resulting in a loss
+of adhesion.
+
 \subsubsection{Field desorption mass spectroscopy}
 
-Molecular weights of the secreted fluid mixtures extracted from an
-Asian ladybird's leg, without and after immersion in water are compared
-(Table \ref{tab:Molecular-distribution-of}). Except for two molecular
-weights (406.8 g/mol and 331.6 g/mol), the chemical fingerprint remained
-unchanged, indicating that the adhesion fluid was not washed away
-underwater. Probable compounds in the fluid, corresponding to the
-resultant molecular weights, include mostly aliphatic hydrocarbons
+FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
+leg when underwater (Table \ref{tab:Molecular-distribution-of}).
+Molecular weights of the secreted fluid mixtures extracted from the
+beetle's leg, without and after immersion in water, show that, except
+for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
+fingerprint remained unchanged This indicates that the adhesion fluid
+was not washed away underwater. Probable compounds in the fluid, corresponding
+to the resultant molecular weights, include mostly aliphatic hydrocarbons
 with traces of aldehydes.
@@
 
-\subsubsection{Adhesion measurements}
-
-Adhesion force for the distal pad of ladybug beetle against glass
-and PFOTS in air and underwater conditions are compared (Figure \ref{fig:Effect-of-contact}
-and Table \ref{tab:Statistical-analysis}). In air, there is no significant
-difference in the adhesion force between glass and PFOTS substrate
-(p = 0.959). Underwater however, when there is no trapped bubble,
-adhesion on a PFOTS surface is significantly larger than on glass
-(p < 0.001). On PFOTS, there is no significant difference in the adhesion
-force in air or underwater conditions. But on glass, adhesion in air
-is significantly larger than underwater, either in the presence (p
-= 0.002) or absence (p < 0.011) of the bubble. At the same, we see
-that the presence of the bubble results in a higher adhesion force
-than with no bubble (CLES = 0.84) on glass, although the difference
-is not statistically significant (p = 0.07).
-
-\begin{table}[H]
-\noindent \begin{centering}
-\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|}
-\hline 
-Fixed & A & B & p-value & CLES\tabularnewline
-\hline 
-\hline 
-In air & PFOTS & Glass & 0.959 & 0.48\tabularnewline
-\hline 
-Underwater: bubble & PFOTS & Glass & 0.011 & 0.96\tabularnewline
-\hline 
-Underwater: no bubble & PFOTS & Glass & \textbf{< 0.001} & 1.0\tabularnewline
-\hline 
-PFOTS & In air & Underwater: bubble & 0.897 & 0.48\tabularnewline
-\hline 
-PFOTS & In air & Underwater: no bubble & 0.828 & 0.48\tabularnewline
-\hline 
-PFOTS & Underwater: bubble & Underwater: no bubble & 0.721 & 0.44\tabularnewline
-\hline 
-Glass & In air & Underwater: bubble & \textbf{0.002} & 1.0\tabularnewline
-\hline 
-Glass & In air & Underwater: no bubble & \textbf{< 0.001} & 1.0\tabularnewline
-\hline 
-Glass & Underwater: bubble & Underwater: no bubble & 0.07 & 0.84\tabularnewline
-\hline 
-\end{tabular}
-\par\end{centering}
-\caption{Pairwise statistical comparison of single leg adhesion force of the
-beetle for each contact type and substrate. The uncorrected p-values
-and Common Language Effect Size (CLES) are obtained from post-hoc
-pair-wise Student t-test between A and B while keeping the third parameter
-fixed. p-values showing statistically significant difference between
-A and B are in boldface. The condition for statistical significance
-is based on the Bonferroni-corrected critical p-value of 0.008.\label{tab:Statistical-analysis}}
-\end{table}
-\begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Single leg adhesion force measurements
-of ladybug beetle (\emph{Coccinella septempuctata}) on glass and PFOTS
-substrates in air and underwater conditions. Values represent peak
-force of a distal pad pulled off from each substrate. Three types
-of contact are seen in underwater experiments and are represented
-separately: \textquotedblleft\emph{bubble}\textquotedblright , \textquotedblleft\emph{no
-bubble}\textquotedblright{} and \textquotedblleft\emph{bad contact}\textquotedblright .
-Stars represent theoretical predictions of adhesion force calculated
-from the capillary bridge model, where hair diameter = 4 \textgreek{m}m,
-pad diameter = 200 \textgreek{m}m, hair height = 40 \textgreek{m}m,
-N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
-= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
-tension of the adhesive fluid in air and water are assumed to be 24
-mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
-\end{figure}
-
-Apart from the three predicted contact types, we also observed an
-additional fourth type of contact which sometimes occurs underwater,
-labeled as ``\emph{bad contact}''. In this scenario, the ventral
-view recordings show that the hairs don't appear to contact well with
-the substrate, unlike the other three contact types. ``\emph{Bad
-contact}'' shows no adhesion with either glass or PFOTS substrate.
-While it's not completely clear why such a contact occurs, there can
-be two possible reasons. First, the hairs could get bundled due to
-a small air meniscus within the hairs, resulting in their disorientation.
-Second, a thin water layer at the substrate interface might not be
-drained out to allow the hairs to make contact with the substrate,
-resulting in a loss of adhesion.
-
 \section{Theory}
@@
 \subsection{Capillary Bridge Model}
-
-We model the hairy pad as an array of $N$ cylindrical rods of length,
-$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
-$D_{p}$, as shown in figure \ref{fig:Model}. The hairs and the pad
-are assumed to be perfectly rigid, for simplicity. The tip of each
-hair has an adhesive fluid of volume, $V_{f}$, making contact with
-the substrate. The fluid is pinned to the circumference of the hair
-and forms a capillary bridge of height, $d$. Similar to our experiments,
-we consider three types of contacts for the pad: 1) \emph{In air},
-2) \emph{Underwater: no bubble} and 3) \emph{Underwater: bubble}.
-In the third case, a bubble of volume, $V_{b}$, is trapped between
-the hairs and pinned to the pad circumference.
 
@@
 \end{figure}
-Let $V_{f}=\frac{4}{3}\pi s_{f}^{3}$ and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$,
-where $s_{f}$ and $s_{b}$ are the radii of spheres with equivalent
-volumes. Fluid and bubble radii are assumed to scale proportional
-to their corresponding pinned contact diameter. We thus defined the
-size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$ and $\phi_{b}=D_{p}/\left(2s_{b}\right)$
-for the fluid and bubble respectively, to conveniently scale their
-volumes relative to the hair and pad diameters they were pinned to.
+We model the hairy pad as an array of $N$ cylindrical rods of length,
+$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
+$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad are assumed
+to be perfectly rigid, for simplicity. The tip of each hair has an
+adhesive fluid of volume, $V_{f}$, making contact with the substrate.
+The fluid is pinned to the circumference of the hair and forms a capillary
+bridge of height, $d$. Similar to our experiments, we consider three
+types of contacts for the pad: 1) \emph{In air}, 2) \emph{Underwater:
+no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
+bubble of volume, $V_{b}$, is trapped between the hairs and pinned
+to the pad circumference.
+
+To characterize the adhesive fluid and bubble volume we define two
+radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
+and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$. Here, $s_{f}$ and $s_{b}$
+are the radii of spheres with equivalent volumes. Fluid and bubble
+radii are assumed to scale proportional to their corresponding pinned
+contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$
+and $\phi_{b}=D_{p}/\left(2s_{b}\right)$ for the fluid and bubble
+respectively, to conveniently scale their volumes relative to the
+hair and pad diameters they were pinned to.
 
@@
 The capillary force, $f$, is the sum of two contributions: surface
-tension and Laplace pressure. Force versus distance for a single capillary
-bridge is calculated by Surface Evolver simulations\cite{RN206},
-(described in \ref{subsec:Simulation-Method}) and used to obtain
-$F_{net}$ as a function of $d$ for each type of contact. The adhesion
-force of the complete hairy pad system is then obtained from the minima
-of $F_{net}$, where negative force values represent attraction.
+tension and Laplace pressure (equation \ref{eq:f_bridge}). Force
+versus distance for a single capillary bridge is calculated by Surface
+Evolver simulations\cite{RN206}, (described in \ref{subsec:Simulation-Method})
+and used to obtain $F_{net}$ as a function of $d$ for each type
+of contact. The adhesion force of the complete hairy pad system is
+then obtained from the minima of $F_{net}$, where negative force
+values represent attraction.
 
@@
 in air and underwater due to its different contact angle and interfacial
-tension in each case. Using the Young-Dupr\textcyr{\`\cyre} equations,
-one can derive the following relation for the contact angle of the
-adhesive fluid underwater:
+tension in each case. Using the Young-Dupr\textcyr{\`\cyre} equations
+for each case of fluid-air, fluid-water and water-air interface, one
+can derive the following relation for the contact angle of the adhesive
+fluid underwater:
 
@@
 
-\subsection{Results}
-
-\subsubsection{Capillary force of a pinned liquid bridge\label{subsec:Capillary-force-of}}
+\subsection{Capillary force of a pinned liquid bridge\label{subsec:Capillary-force-of}}
 
 Forces due to a single pinned capillary liquid bridge in contact with
-a substrate are obtained via simulations (Figure \ref{fig:Single-bridge}).
-Capillary forces are more attractive for smaller contact angles. The
-Laplace pressure contribution to the net adhesion force dominates
-for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
+a substrate are obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
+We see that, generally, the shape of the liquid meniscus determines
+the strength of its adhesion force. High adhesion is seen for contact
+angles less than $\sim$ 70\textdegree{} due to a net negative curvature
+of the meniscus, while low adhesion is seen for contact angles greater
+than $\sim$ 150\textdegree{} due to its net curvature being close
+to zero. The Laplace pressure contribution to the net adhesion force
+dominates for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
 Interestingly, its contribution to the adhesion force is mostly non-repulsive
@@
 For contact angles greater than 150\textdegree , the net adhesion
-force approaches zero. We see that, generally, the shape of the liquid
-meniscus determines the strength of its adhesion force. High adhesion
-is thus seen for contact angles less than $\sim$ 70\textdegree{}
-due to a net negative curvature of the meniscus, while low adhesion
-is seen for contact angles greater than $\sim$ 150\textdegree{} due
-to its net curvature being close to zero.
+force approaches zero.
 
@@
 represents attraction. a) Force-distance curves are shown for different
-contact angles of the liquid with the substrate. b) Adhesion force,
-calculated from the minima of the corresponding force-distance curve,
-is plotted as a function of contact angle with the substrate, together
+contact angles of the liquid with the substrate. b) Adhesion forces,
+calculated from the minima of the corresponding force-distance curves,
+are plotted as a function of contact angle with the substrate, together
 with its Laplace and surface tension components (equation \ref{eq:f_bridge}).
@@
 creates a net positive curvature, resulting in a positive Laplace
-pressure and thus repulsion.
-
-\subsubsection{Capillary Bridge Model: Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}
+pressure and thus repulsion. Without pinning, the capillary forces
+would have shown high attractive forces on a hydrophilic substrate\cite{RN93}.
+
+\subsection{Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}
 
@@
 On the hydrophilic substrate ($\theta_{wa}=24\lyxmathsym{\textdegree}$),
-contact\emph{ in air} shows the highest adhesion. \emph{Underwater:
-no bubble} shows close to no adhesion while \emph{underwater: bubble}
-shows moderate adhesion. In contrast, for a hydrophobic substrate
-($\theta_{wa}=120\lyxmathsym{\textdegree}$), the highest adhesion
-is seen for \emph{underwater: no bubble}, much larger than \emph{in
-air}. Even \emph{underwater: bubble} has slightly higher adhesion
-than \emph{in air}. Note that the contact area is fixed by keeping
-the area fraction and $D_{p}/D_{h}$ constant. All curves correspond
-to the same total hair contact area. Thus, the above mentioned effects
-are attributed solely to how the the capillary force changes in each
-scenario.
-
-On a hydrophilic substrate, the contact angle of the oily adhesive
-fluid is 6\textdegree , when surrounded by air (Table \ref{tab:Model-parameters})
-and 150\textdegree , when surrounded by water (equation (\ref{eq:theta_fw})).
-This results in the meniscus shape to have a net negative and slightly
-positive curvatures, respectively, resulting in strong adhesion in
-air and poor adhesion underwater. On a hydrophobic substrate however,
-the contact angles of the fluid in air and water are 50\textdegree{}
-and 1\textdegree , respectively. In both cases, the contact angles
-are low, resulting in strong adhesion in both media. Additionally,
-the interfacial tension of the oily fluid underwater ($\gamma_{fw}$)
-is twice that of in air ($\gamma_{fa}$). Thus, we see a higher capillary
-adhesion for the \emph{underwater: no bubble} case when compared to
-\emph{in air} (Figure \ref{fig:Oil-contact-images}).
+highest adhesion is seen when the hairs contact in air, while lowest
+adhesion occurs underwater without a trapped bubble. The presence
+of a bubble leads to intermediate force values. In contrast, on a
+hydrophobic substrate ($\theta_{wa}=120\lyxmathsym{\textdegree}$),
+highest adhesion is seen for the underwater case without a trapped
+bubble, much larger than in air. When a bubble is present, the forces
+are only slightly larger than in air.
 
@@
 
+The observed trend in forces can be explained by how the adhesive
+fluid wets the surface in each case. On a hydrophilic substrate, the
+contact angle of the oily adhesive fluid is 6\textdegree , when surrounded
+by air (Table \ref{tab:Model-parameters}) and 150\textdegree , when
+surrounded by water (equation (\ref{eq:theta_fw})). This results
+in the meniscus shape to have a net negative and slightly positive
+curvatures, respectively, resulting in strong adhesion in air and
+poor adhesion underwater. On a hydrophobic substrate however, the
+contact angles of the fluid in air and water are 50\textdegree{} and
+1\textdegree , respectively. In both cases, the contact angles are
+low, resulting in strong adhesion in both media. Additionally, the
+interfacial tension of the oily fluid underwater ($\gamma_{fw}$)
+is twice that of in air ($\gamma_{fa}$). Thus, we see a higher capillary
+adhesion for the \emph{underwater: no bubble} case when compared to
+\emph{in air} (Figure \ref{fig:Oil-contact-images}). Note that the
+contact area is fixed in all cases by keeping the area fraction and
+$D_{p}/D_{h}$ constant. Thus the observed effects is not a result
+of changing contact area, but rather on the nature of capillary forces.
+
+\begin{figure}[H]
+\includegraphics{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
+meniscus in contact with glass and PFOTS in air and underwater conditions.
+The corresponding interfacial tension, \textgreek{g}, and contact
+angle, \ensuremath{\theta}, used to predict the ladybug's adhesion
+are labeled for each case.}
+\end{figure}
+
 The net force in the \emph{underwater: bubble} case mainly depends
@@
 
-The contribution of the capillary force due to the bubble itself is
-negligible for both substrates (Figure \ref{fig:Effect-of-substrate}).
-Its contribution even is slightly repulsive on the hydrophilic substrate
-due to the positive curvature of the bubble, and slightly attractive
-on the hydrophobic substrate due to its negative curvature. This small
-contribution is manifested by the slightly higher adhesion for \emph{underwater:
-bubble} relative to \emph{in air} for the hydrophobic substrate, since
-all hairs are within the bubble in this case.
-
-\subsubsection{Capillary Bridge Model: Effect of bubble volume}
-
-The effect of varying bubble volume, $\hat{V}_{b}$, on the net adhesion
-force of the \emph{underwater: bubble} case are compared for hydrophilic
-and hydrophobic substrates (Figure \ref{fig:Effect-of-bubble}). From
-previous section, we know that on the hydrophilic substrate, fluid
-bridges outside the bubble show poor adhesion due to the positive
-curvature of their meniscus. Thus, decreasing $\hat{V}_{b}$ decreases
-the adhesion force due to a larger proportion of hairs being outside
-the bubble. In contrast, on the hydrophobic substrate, fluid bridges
-outside the bubble show higher capillary forces, due to its low contact
-angle and high interfacial tension in water. Thus, adhesion force
-increases for a hydrophobic substrate as the bubble size decreases.
+We see that the bubble itself doesn't contribute much to the net force
+on either substrate (Figure \ref{fig:Effect-of-substrate}). Its contribution
+even is slightly repulsive on the hydrophilic substrate due to the
+positive curvature of the bubble, and slightly attractive on the hydrophobic
+substrate due to its negative curvature. This small contribution is
+manifested by the slightly higher adhesion for \emph{underwater: bubble}
+relative to \emph{in air} for the hydrophobic substrate, since all
+hairs are within the bubble in this case.
+
+\subsection{Effect of bubble volume}
 
@@
 \end{figure}
-The contribution of the bubble to the net adhesion force is small
-regardless of its volume, when compared to the whole pad. We see that
-a smaller $\hat{V}_{b}$ results in increased attraction by the bubble
-on both types of substrates. For larger values of $\hat{V}_{b}$,
-the force trend for the whole pad mostly follows that of the bubble,
-because the bubble in this case is big enough to entrap all the hairs
-inside it. Thus, the force contribution due to the fluid bridges remain
-unchanged, and only the bubble's contribution drives the slight variation
-in the pad's adhesion at high $\hat{V}_{b}$. Once the bubble is small
-enough such that part of the fluid bridges start making contact in
-water, the force trend changes, with a steep decrease (increase) in
-adhesion force on hydrophilic (hydrophobic) substrate as the volume
-decreases.
-
-\subsubsection{Capillary Bridge Model: Effect of hair diameter }
-
-The effect of changing hair diameter, $D_{h}$, to the net adhesion
-force is compared for hydrophilic and hydrophobic substrates (Figure
-\ref{fig:Effect-of-hair}). Here, the pad diameter, total hair contact
-area and bubble volume are constant since $D_{p}$, $\alpha$ and
-$\hat{V}_{b}$ are kept fixed. The radius corresponding to the fluid
-volume is assumed to scale proportional to the hair diameter and is
-fixed ($\phi_{f}=2$).
+The volume of the bubble can influence its capillary force contribution,
+as well as change the relative proportion of hairs inside and outside
+it. To investigate this, we varied the bubble volume, $\hat{V}_{b}$,
+and compared the maximum adhesion force on both hydrophilic and hydrophobic
+substrates (Figure \ref{fig:Effect-of-bubble}). The contribution
+of the bubble to the net adhesion force is small regardless of its
+volume, when compared to the whole pad. Further, opposite trends of
+adhesion is seen on the two substrates with changing $\hat{V}_{b}$.
+
+From previous section, we know that on the hydrophilic substrate,
+fluid bridges outside the bubble show poor adhesion due to the positive
+curvature of their meniscus. Thus, decreasing $\hat{V}_{b}$ decreases
+the adhesion force due to a larger proportion of hairs being outside
+the bubble. In contrast, on the hydrophobic substrate, fluid bridges
+outside the bubble show higher capillary forces, due to its low contact
+angle and high interfacial tension in water. Thus, adhesion force
+increases for a hydrophobic substrate as the bubble size decreases.
+
+A smaller $\hat{V}_{b}$ results in increased, but small, attraction
+by the bubble on both types of substrates. For larger values of $\hat{V}_{b}$
+however, the force trend for the whole pad mostly follows that of
+the bubble. This is because the bubble gets big enough to entrap all
+the hairs inside it. Thus, the force contribution due to the fluid
+bridges remain unchanged, and only the bubble's contribution drives
+the slight variation in the pad's adhesion at high $\hat{V}_{b}$.
+Once the bubble is small enough such that part of the fluid bridges
+start making contact in water, the force trend changes, with a steep
+decrease (increase) in adhesion force on hydrophilic (hydrophobic)
+substrate as the volume decreases.
+
+\subsection{Effect of hair diameter }
+
+\begin{figure}[H]
+\includegraphics[scale=0.5]{Figure6-Model_effect_of_hair_size}\caption{\label{fig:Effect-of-hair}Normalized adhesion force of a hairy pad
+system on a hydrophilic and hydrophobic substrate as a function of
+hair diameter, $D_{h}$. Volume of each fluid bridge, $V_{f}$, scales
+relative to $D_{h}$ based on the parameter $\phi_{f}=2$. Adhesion
+forces are calculated from the minima of the respective force-distance
+curves, based on the capillary bridge model. A negative value represents
+attraction. The bubble's contribution to the net force for an \emph{underwater:
+bubble} contact is denoted by plus symbols. Pad diameter and bubble
+volume are kept fixed. All lengths are scaled relative to $D_{p}$.}
+\end{figure}
+Hairs on a ladybug's pad terminate in various shapes like ``discoidal''
+or ``pointed''. We studied this geometric effect on adhesion by
+changing the hair diameter, $D_{h}$ (Figure \ref{fig:Effect-of-hair}).
+Here, the pad diameter, total hair contact area and bubble volume
+are constant since $D_{p}$, $\alpha$ and $\hat{V}_{b}$ are kept
+fixed. The adhesive fluid volume is again assumed to scale relative
+to the hair diameter ($\phi_{f}=2$).
 
@@
 
-\begin{figure}[H]
-\includegraphics[scale=0.5]{Figure6-Model_effect_of_hair_size}\caption{\label{fig:Effect-of-hair}Normalized adhesion force of a hairy pad
-system on a hydrophilic and hydrophobic substrate as a function of
-hair diameter, $D_{h}$. Volume of each fluid bridge, $V_{f}$, scales
-relative to $D_{h}$ based on the parameter $\phi_{f}=2$. Adhesion
-forces are calculated from the minima of the respective force-distance
-curves, based on the capillary bridge model. A negative value represents
-attraction. The bubble's contribution to the net force for an \emph{underwater:
-bubble} contact is denoted by plus symbols. Pad diameter and bubble
-volume are kept fixed. All lengths are scaled relative to $D_{p}$.}
-\end{figure}
-
 Similar to the trend in Figure \ref{fig:Effect-of-substrate}, contact
@@
 available to occupy between the pad and the substrate, This results
-in it bulging outwards near the pinned contact line on the top. Thus,
-the bubble's contribution gets repulsive as hair diameter decreases.
+in it bulging outwards near the pinned contact line on the top, causing
+repulsion.
 
@@
 
-Our experiments demonstrate, for the first time, that the ladybug
-beetle can attach underwater to a hydrophobic substrate even without
-a bubble trapped around its hairs. A previous study\cite{RN87} had
-hypothesized that a bubble is necessary for underwater attachment
-in beetles. This is, however, only true for hydrophilic substrates,
-where a trapped bubble can facilitate underwater adhesion due to the
-hairs making contact in a dewetted environment. For a hydrophobic
-substrate, the adhesion is similar regardless of whether the contact
-occurs in air or underwater conditions, with or without a trapped
-bubble. Our theoretical calculations further show that the bubble
-by itself has a negligible capillary contribution to the net underwater
-adhesion of the pad. Direct force measurement of a single similarly
-sized bubble making contact with a hydrophobic substrate shows a maximum
-adhesion less than 50 \textgreek{m}N, which further validates that
-the bubble's contribution is insignificant (\ref{subsec:Capillary-force-due}).
+Our experiments demonstrate that the ladybug beetle can attach underwater
+to a hydrophobic substrate even without a bubble trapped around its
+hairs. A previous study\cite{RN87} had hypothesized that a bubble
+is necessary for underwater attachment in beetles. This is, however,
+only true for hydrophilic substrates, where a trapped bubble can facilitate
+underwater adhesion due to the hairs making contact in a dewetted
+environment. For a hydrophobic substrate, the adhesion is similar
+regardless of whether the contact occurs in air or underwater conditions,
+with or without a trapped bubble. Our theoretical calculations further
+show that the bubble by itself has a negligible capillary contribution
+to the net underwater adhesion of the pad. Direct force measurement
+of a single similarly sized bubble making contact with a hydrophobic
+substrate shows a maximum adhesion less than 50 \textgreek{m}N, which
+further validates that the bubble's contribution is insignificant
+(\ref{subsec:Capillary-force-due}).
 
 Predictions of the ladybug's adhesion from the capillary bridge model
-follow our experimental results (Figure \ref{fig:Effect-of-contact}).
+agree with our experimental results (Figure \ref{fig:Effect-of-contact}).
 In underwater conditions without a trapped bubble, adhesion on a hydrophobic
@@
 contact.
-
-\begin{figure}[H]
-\includegraphics{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
-meniscus in contact with glass and PFOTS in air and underwater conditions.
-The corresponding interfacial tension, \textgreek{g}, and contact
-angle, \ensuremath{\theta}, used to predict the ladybug's adhesion
-are labeled for each case.}
-\end{figure}
 
@@
 
-Our study illustrates that the ladybug beetle relies primarily on
-its oily fluid secretion to achieve adhesion in both air and underwater
-conditions. The beetle can attach underwater on a hydrophobic substrate
-even without a trapped air bubble within its hairy pad, although it
-loses this ability on a hydrophilic substrate. This is explained theoretically
-by the different contact angle and interfacial tension of the adhesive
-fluid in air and underwater conditions. Further, the bubble itself
-has a negligible capillary contribution to the total force. The trapped
-bubble can promote adhesion only on a hydrophilic substrate by providing
-an air medium to the adhesive fluid bridges inside it. Oil wettability,
-thus, primarily controls the insect's adhesion in any given condition.
-A similar argument also explains previously reported underwater measurements
+Ladybug beetles rely primarily on their oily fluid secretion to adhere
+to surfaces in both air and underwater conditions. The beetle can
+attach underwater on a hydrophobic substrate even without a trapped
+air bubble within its hairy pad, although it loses this ability on
+a hydrophilic substrate. This is explained theoretically by the different
+contact angle and interfacial tension of the adhesive fluid in air
+and underwater conditions. Further, the bubble itself has a negligible
+capillary contribution to the total force. The trapped bubble can
+promote adhesion only on a hydrophilic substrate by providing an air
+medium to the adhesive fluid bridges inside it. Oil wettability, thus,
+primarily controls the insect's adhesion in any given condition. A
+similar argument also explains previously reported underwater measurements
 in geckos \cite{RN15}, which highlights the possibility of capillary
@@
 
+\subsection{Statistical comparison}
+
+Pairwise statistical comparison of single leg adhesion force measurements
+of the ladybug beetle (\emph{Coccinella septempuctata}) for each contact
+type and substrate are shown (Table \ref{tab:Statistical-analysis}).
+The uncorrected p-values and Common Language Effect Size (CLES) are
+obtained from post-hoc pair-wise Student t-test between A and B while
+keeping the third parameter fixed. p-values showing statistically
+significant difference between A and B are in boldface. The condition
+for statistical significance is based on the Bonferroni-corrected
+critical p-value of 0.008.
+
+\begin{table}[H]
+\noindent \begin{centering}
+\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|}
+\hline 
+Fixed & A & B & p-value & CLES\tabularnewline
+\hline 
+\hline 
+In air & PFOTS & Glass & 0.959 & 0.48\tabularnewline
+\hline 
+Underwater: bubble & PFOTS & Glass & 0.011 & 0.96\tabularnewline
+\hline 
+Underwater: no bubble & PFOTS & Glass & \textbf{< 0.001} & 1.0\tabularnewline
+\hline 
+PFOTS & In air & Underwater: bubble & 0.897 & 0.48\tabularnewline
+\hline 
+PFOTS & In air & Underwater: no bubble & 0.828 & 0.48\tabularnewline
+\hline 
+PFOTS & Underwater: bubble & Underwater: no bubble & 0.721 & 0.44\tabularnewline
+\hline 
+Glass & In air & Underwater: bubble & \textbf{0.002} & 1.0\tabularnewline
+\hline 
+Glass & In air & Underwater: no bubble & \textbf{< 0.001} & 1.0\tabularnewline
+\hline 
+Glass & Underwater: bubble & Underwater: no bubble & 0.07 & 0.84\tabularnewline
+\hline 
+\end{tabular}
+\par\end{centering}
+\caption{\label{tab:Statistical-analysis}}
+\end{table}
+
 \subsection{Capillary force due to a bubble\label{subsec:Capillary-force-due}}

### 2021-02-15 source/tex/ladybug_adhesion.tex
Latex edits made by Thomas

@@
 
-\title{Wetting of adhesive fluid controls insect adhesion in air and underwater}
+\title{Wetting properties of the adhesive fluid allows beetles to attach to surfaces not just in air but also underwater}
 
@@
 \begin{abstract}
-Insects like beetles can stick to various surfaces using hairy pads
-on their legs. It was previously shown that these pads can even attach
-underwater, presumably due to an air bubble trapped around the pad.
-However, the bubble's contribution to adhesion via capillary force
-remained unclear. To investigate the role of the bubble, we measured\emph{
-in-vivo} underwater adhesion of a ladybug's pad, in the presence and
-absence of the trapped bubble and compare it with its adhesion in
-air. Our experiments reveal that on a hydrophobic substrate, even
-without a bubble, the pad can show adhesion underwater comparable
-to that in air. On a hydrophilic substrate, underwater adhesion is
-significantly reduced, with or without a trapped bubble. To explain
-these results, we develop a simple theoretical model for the net adhesion
-of a hairy pad due to capillary forces. Our results demonstrate that
-the wetting properties of the adhesive fluid determines the insect's
-adhesion in both air and underwater conditions.
+
+Many beetles can climb smooth surfaces using hairy adhesive pads on their legs.
+It was previously shown that a terrestrial beetle can even adhere and walk underwater.
+The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air.
+However, it remained unclear to what extend such an air bubble is necessary for underwater adhesion and if the bubble contributes to the net adhesive force.
+To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air.
+Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air.
+On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble.
+We modelled the adhesion of a hairy pad using capillary forces.
+Coherent with our experiments, the model demonstrates that the wetting properties of the adhesive fluid alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion.
 \end{abstract}
@@
 
-The question of how insects and other small animals can walk on smooth
-surfaces against gravity has fascinated scientists for at least the
-past three centuries \cite{RN198,RN59}. We now know that such animals
-are able to adhere by using specialized organs on their feet called
-adhesive pads. These adhesive pads exist in a variety of types depending
-on the animal, but are generally categorized into: 1) ``smooth pads''
-found in ants\cite{RN201}, stick insects \cite{RN182}, etc. and
-2) ``hairy pads'' seen in flies \cite{RN155}, geckos \cite{RN202}
-and others. The hairy pads show: 1) compliance to rough surfaces due
-to their lower effective modulus, 2) angle dependent adhesion due
-to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20},
-which makes them suitable to adhere to most surfaces reversibly. Many
-of these insects pads also secrete an adhesive fluid, as seen in flies
-and ants \cite{RN201} (``wet adhesion''), while others such as
-spiders and geckos rely on their dry hairy pads for attachment (``dry
-adhesion''). In the ``wet adhesion'' case, fluid secretion can
-enforce adhesion through surface tension and viscous forces \cite{RN71},
-while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.
-
-Terrestrial beetles such as the dock beetle or the ladybug have hairy
-pads consisting of a dense array of hair-like structures called setae.
-The setae tips can be discoidal, spatula or pointed shaped, which
-are distributed throughout the pad depending on sex or species\cite{RN19}.
-Single seta force measurements revealed that discoidal shaped seta
-shows larger pull-off force than spatula and pointed setae\cite{RN79},
-illustrating the role of hair geometry in adhesion. The tip of each
-seta secretes approximately one femtoliter of oily adhesive fluid
-\cite{RN108}. The fluid's chemical composition is identified as a
-mixture of mostly long chain hydrocarbons\cite{RN96} with traces
-of triglycerides, fatty acids and cholesterol\cite{RN221,RN222}.
-A recent study by Gernay et. al.\cite{RN77}, based on an elastocapillary
-model, has been able to reasonably predict single seta adhesion forces
-theoretically, confirming the dominant role of surface tension in
-the ``wet adhesion'' of beetles.
-
-While most of the studies on insect adhesion are done under natural
-conditions in air, insect attachment underwater has been relatively
-unexplored. Typically, underwater adhesion is complicated to achieve
-due to the difficulty in displacing the water layer and enable good
-contact\cite{RN123}. Regardless, a study on leaf beetles\cite{RN87}
-has revealed that they can in fact attach quite well to surfaces underwater.
-Its hairy pad traps an air bubble underwater, which dewets the surface
-on contact. It has been hypothesized that a combination of capillary
-forces due the air bubble and hair secretions within the dewetted
-area results in its adhesion underwater. However, a detailed investigation
-of the bubble's contribution and necessity to adhere to different
-surfaces is lacking. Geckos are also known to adhere underwater, where
-its shear adhesion force on hydrophobic substrates are similar in
-both air and underwater conditions. Interestingly, its adhesion on
-a fluorinated substrate is even larger underwater than in air\cite{RN15}.
-This has been partially explained by a thermodynamic work of adhesion
-model, assuming full displacement of water at the interface, leading
-to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.
-
-The goal of this paper is to provide a generalized picture of adhesion
-for insects which use hairy pads and secrete a oily fluid for attachment.
-First, we measured adhesion of a single constrained pad of a live
-ladybug beetle in air and underwater conditions, both on smooth hydrophilic
-and hydrophobic glass surfaces, with a microscopic observation of
-the contact process. Second, we developed a simple theoretical model
-considering capillary forces to predict the net adhesion force of
-a hairy pad under different conditions. The case of underwater adhesion
-was studied both in the presence and absence of a trapped bubble,
-to decouple the bubble's role in the insect's adhesion. Finally, we
-discuss key insights gained from our experiments and model with regards
-to understanding adhesion in other animals.
+The question on how insects and other small arboreal animals climb smooth and slippery
+surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}.
+We now know that such animals are able to adhere by using specialised organs on their feet called adhesive pads.
+These adhesive pads can generally be described as either ``smooth'' or ``hairy''.
+Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads.
+Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly.
+The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) like seen in spiders and lizards but are typically undivided in most insects.
+The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}.
+Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion.
+All insect pads secrete an adhesive fluid while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion'').
+In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.
+
+While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored.
+Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} using suction cups to adhere to surfaces.
+However, underwater adhesion using secreted liquids (glue-like substances or the adhesive fluid) requires the displacement of the water in the interface first and a spreading of the fluid on the substrate.
+Furthermore, the spreading coefficient of the secreted liquid needs to be larger than that of the water in order to utilise the interfacial tension between the liquids as an adhesive force.
+One relative simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}.
+This has been shown in a recent study by \citet{RN87} on the ability of a terrestrial leaf beetle which can attach quite well to surfaces underwater by using such an air bubble.
+Their naturally hydrophobic hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact.
+It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the dewetted area results in its adhesion underwater.
+However, it remained unclear whether an air bubble is strictly necessary and its exact contribution to the adhesive force.
+The oily adhesive fluid found in insects alone might be sufficient in creating the necessary interfacial tension even without an bubble, given that the adhesive fluid remains on the hairs when submerged.
+In beetles, the tip of each seta secretes approximately one femtoliter of oily adhesive fluid \cite{RN108}.
+The fluid's chemical composition is identified as a mixture of mostly long chain hydrocarbons\cite{RN96} with traces
+of triglycerides, fatty acids and cholesterol\cite{RN221,RN222} rendering it immiscible with water.
+%A recent study by Gernay et.
+al.\cite{RN77}, based on an elastocapillary model, has been able to reasonably predict single seta adhesion forces theoretically, confirming the dominant role of surface tension in the ``wet adhesion'' of beetles.
+
+% Geckos are also known to adhere underwater, where its shear adhesion force on hydrophobic substrates are similar in both air and underwater conditions.
+Interestingly, its adhesion on a fluorinated substrate is even larger underwater than in air\cite{RN15}.
+This has been partially explained by a thermodynamic work of adhesion model, assuming full displacement of water at the interface, leading to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.
+
+The goal of this paper is to provide a generalised picture of adhesion in insects which use hairy pads and secrete a oily fluid for attachment.
+We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion of individual adhesive pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces.
+We further tested whether the chemical profile of the adhesive fluid changes when the hairs being submerged in water.
+Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions.
+The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion.
+Finally, we
+discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.
 
@@
 
-Normal adhesion force measurements on a restrained leg of a live ladybug
-beetle were performed. We characterize adhesion by the pull-off force
-during detachment. Measurements were done against smooth glass and
-fluorinated surfaces to represent hydrophilic and hydrophobic substrates
-respectively. When no water was present, we labeled the contact type
-as ``\emph{in air}''. For the underwater conditions, measurements
+Normal adhesion force measurements on a restrained leg in a live
+beetle were performed. We characterised adhesion by the pull-off force
+during detachment and tested smooth glass and
+fluorinated surfaces representing hydrophilic and hydrophobic substrates
+respectively. When no water was present, we labelled the contact type
+as ``\emph{in air}''. Underwater, measurements
 were done both in the presence and absence of a trapped bubble (``\emph{underwater:
@@
 investigate the bubble's role in underwater adhesion. Adhesion force
-for each of the labeled contact types were compared for both substrates.
+for each of the labelled contact types were compared for both substrates.
 
@@
 Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
-purchased from Katz Biotech (Baruth, Germany) were used for adhesion
-tests. The beetles were housed in a plastic box filled with leaves,
+purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
 twigs and stones at room temperature and 60-80\% relative humidity
 with daily access to sunlight. They were fed with raisins, honey and
-water\emph{ ad libitum}.
-
-Each leg of the beetle has a pair of hairy pads covered with mostly
-discoidal shaped setae, capable of strong adhesion. For the test,
-we only allowed the distal-end pad to make contact. The beetle's leg
-was constrained similar to the method described by Bullock et al \cite{RN19}.
-A steel ball fixed with a piece of thick solder wire served as a rotatable
-holder to fix the beetle and align its leg (Figure \ref{fig:Setup}).
-The beetle was first anesthetized using CO\textsubscript{2} sublimating
-from a piece of dry ice and then glued to the steel ball on its back.
-Its front left leg was carefully fixed to the solder wire of the holder
-using Blue-Tac. Its claws were fixed using epoxy glue to prevent any
-wiggling. A small piece of non-sticky Teflon tape helped to keep its
-other legs tucked close to the body and avoid their interference during
-the adhesion test.
-
-After measurements, the beetle was freed by carefully removing the
-epoxy glue and Blue-Tac without harming it and set free.
-
-\subsubsection{Substrate preparation}
-
-Standard 20 mm wide glass coverslips were used as the hydrophilic
-substrate. Glass was wiped with isopropanol, rinsed in water and dried
-under nitrogen flow. The surface was then plasma cleaned in a oxygen
-plasma chamber (Diener Electronic Femto) for 10 min at 120 W. The
-surface was further rinsed with water and dried under nitrogen flow.
-
-For the hydrophobic substrate, the glass cover slip was coated with
-a fluorosilane via chemical vapor deposition (CVD). First, the glass
-was cleaned using IPA and plasma treated as before. Next, 0.2 ml of
-Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
-Sigma Aldrich, was put in a sealed chamber along with the the cleaned
-glass. The chamber was placed under 100 mbar pressure for 10 min for
-the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
-for 3 hours.
-
-The substrate wettability was characterized by dynamic contact angle
-measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
-Milli-Q water and n-hexadecane were used as test liquids. Advancing
-and receding contact angles were measured for a maximum drop volume
-of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate.
-
-\begin{table}[H]
-\centering{}%
-\begin{tabular}{|c|c|c|c|}
-\hline 
-Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
-\hline 
-\hline 
-\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
-\cline{2-4} \cline{3-4} \cline{4-4} 
- & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
-\hline 
-\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
-\cline{2-4} \cline{3-4} \cline{4-4} 
- & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
-\hline 
-\end{tabular}\caption{Dynamic contact angles measurements \label{tab:Contact-Angles}}
-\end{table}
+water \emph{ad libitum}.
+
+ %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
+An individual beetle was first carefully anesthetised using small amounts of CO\textsubscript{2} sublimating
+from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball.
+The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}).
+The bracket with the ball and the beetle could be further positioned by manual micromanipulators in all three axes before the experiments.
+One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blue-Tac (X) allowing us to further align the leg to the substrate.
+The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate.
+Each leg of a male ladybug beetle has two pads.
+For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one.
+A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test.
+After the measurements, the beetle was freed by carefully removing the epoxy glue and Blue-Tac without harming it and set free.
 
@@
 with a steel bending beam (spring constant = 68.1 N/m) constitutes
-the vertical force sensor. Beam deflection was calibrated using 4
+the (vertical) force sensor. Beam deflection was calibrated using 4
 different known weights to get the corresponding force. A plastic
@@
 was used for vertical up-down motion, bringing the insect in contact
-with the substrate from the top. A 3 axis manual micro-manipulator
-together with the rotatable steel ball allowed good alignment of the
-beetle's foot to the substrate. A coaxial illuminated tube microscope
+with the substrate from the top. A coaxial illuminated tube microscope
 (\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
-with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with cameras
+with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 pixel; XBasler)
 were used to record the sample contact with the substrate from ventral
-and side views respectively. Pad contact area was visualized through
-the substrate in total reflection mode by the ventral view camera.
+and side views respectively. Pad contact area was visualised through
+the substrate with help of epi-illumination.
 The data acquisition from the force sensor and cameras, together with
-the appropriate piezo motion steps were synchronized using a custom
+the appropriate piezo motion steps were synchronised using a custom
 LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
@@
 
-The vertical and lateral piezos were together used to perform approach-retract
+The vertical and lateral piezos were used together to perform approach-retract
 adhesion tests with the substrate to get the pull-off force. However,
-instead of a simple down-up motion, some additional motion steps were
-included (Figure \ref{fig:Setup}). A 100 \textgreek{m}m lateral sliding
-motion was done after the leg makes contact, to give it a proximal
-pull which will orient its hairs with the substrate \cite{RN19}.
-An additional 10 \textgreek{m}m compression step (approach) was done
-to ensure all hairs were loaded in compression and made good contact
-with the surface. A short pause (1 s) was introduced to minimize any
+instead of a simple down-up motion, an additional 100 \textgreek{m}m lateral sliding motion was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
+A further 10 \textgreek{m}m compression step (approach) set all hairs in slight compression which helped further contact
+with the surface. Next, a short pause (1 s) removed any
 viscoelastic effects before finally retracting the leg away from the
@@
 a trapped air bubble, the water was first degassed in a vacuum chamber
-at 10 mbar pressure for 3 hours and used immediately. Before experiment,
-the pad was repeatedly brought into contact with the surface 10 times
-to equilibriate the pad system. 5 force measurements were subsequently
-performed on a fresh spot of the substrate and averaged for data analysis.
-Experiments were repeated with 5 individual beetles for each type
-of contact and substrate. In total, 30 beetles were tested.
+at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
+the pad was brought into contact with the surface 10 times repeatedly 
+to equilibrate the pad system (X what do you mean by equilibrate?).
+
+Five force measurements were subsequently performed on a fresh spot of the substrate and averaged for data analysis.
+Experiments were repeated with five individual beetles for each type of contact and substrate.
+In total, 30 beetles were tested.
 
@@
 \par\end{centering}
-\caption{\label{fig:Setup} Adhesion test setup. The recorded force data and
-contact area of distal pad are shown in the plot, in which, the shaded
-regions represent distinct piezo motion steps, negative force values
+\caption{\label{fig:Setup} Adhesion setup (for explanation see text). The recorded force data and
+contact area of a distal pad are shown in the plot, in which, the shaded
+regions represent distinct movements like approach, lateral pull, pre-load and detachment... (please explain which ones X). Negative force values
 represent attraction and the minimum force peak during the final retraction
-step is the adhesion force.}
-\end{figure}
-
-\subsubsection{Field desorption mass spectroscopy}
-
-A previous study on archanids \cite{RN223} reported that its secreted
-fluid does not dissolve in water. To confirm if even the beetle retains
-its adhesive fluid underwater, we perform Field Desorption Mass Spectroscopy
-(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
-were done on the extracted secretions before and after rinsing its
-legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
-axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
-to the measurement chamber of the FDMS. As a reference, pure THF was
-used. The second middle leg of the same ladybird was subsequently
-immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
-20 min and then transferred to the measurement chamber of the spectrometer.
-Molecular composition was extracted from the peak positions of the
-FDMS spectra.
+step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material Xshould we provide one?}
+\end{figure}
 
@@
 
+\subsubsection{Substrate preparation}
+
+Standard 20 mm wide glass coverslips were used as the hydrophilic
+substrate. Glass was wiped with isopropanol, rinsed in water and dried
+under nitrogen flow. The surface was then plasma cleaned in a oxygen
+plasma chamber (Diener Electronic Femto) for 10 min at 120 W. The
+surface was further rinsed with water and dried under nitrogen flow.
+
+For the hydrophobic substrate, the glass cover slip was coated with
+a fluorosilane via chemical vapor deposition (CVD). First, the glass
+was cleaned using IPA and plasma treated as before. Next, 0.2 ml of
+Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
+Sigma Aldrich, was put in a sealed chamber along with the the cleaned
+glass. The chamber was placed under 100 mbar pressure for 10 min for
+the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
+for 3 hours.
+
+The substrate wettability was characterised by dynamic contact angle
+measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
+Milli-Q water and n-hexadecane were used as test liquids. Advancing
+and receding contact angles were measured for a maximum drop volume
+of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate.
+
+\begin{table}[H]
+\centering{}%
+\begin{tabular}{|c|c|c|c|}
+\hline 
+Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
+\hline 
+\hline 
+\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
+\cline{2-4} \cline{3-4} \cline{4-4} 
+ & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
+\hline 
+\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
+\cline{2-4} \cline{3-4} \cline{4-4} 
+ & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
+\hline 
+\end{tabular}\caption{Dynamic contact angles measurements \label{tab:Contact-Angles}}
+\end{table}
+
+\subsubsection{Field desorption mass spectroscopy}
+
+A previous study on archanids \cite{RN223} reported that its secreted
+fluid does not dissolve in water. To test whether the beetles retain
+their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
+(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
+were done on the extracted secretions before and after rinsing its
+legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
+axyridis} X the fact we are introducing a new species is a bit odd and could raise a question with the reviewer but I don't know a good way around it.
+we could bring it in the introduction and say that these are preliminary/unpublished results.
+that would be perfectly viable) was immersed in 50 \textmu L THF for 20 min and then transferred
+to the measurement chamber of the FDMS. As a reference, pure THF was
+used. The second middle leg of the same ladybird was subsequently
+immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
+20 min and then transferred to the measurement chamber of the spectrometer.
+Molecular composition was extracted from the peak positions of the
+FDMS spectra.
+
 \subsection{Results}
@@
 In air, adhesion forces of the distal pad of ladybug beetle against
-glass and PFOTS are rather similar; no significant differences are
+glass and PFOTS were similar, i.e. no significant differences were
 detected (Figure \ref{fig:Effect-of-contact} and Table \ref{tab:Statistical-analysis}).
-In contrast, underwater adhesion on PFOTS surface is significantly
+In contrast, the underwater adhesion on a PFOTS surface was significantly
 larger than on glass (p < 0.001). This stronger adhesion on PFOTS
@@
 to dry conditions, irrespective of the presence of a trapped bubble
-(p $\leq$ 0.002). Underwater adhesion on glass tends to be slightly
-higher in the presence of a bubble (CLES = 0.84). However, this difference
-is small and not statistically significant (p = 0.07).
+(p $\leq$ 0.002). In the presence of a bubble, underwater adhesion on glass was slightly higher (CLES = 0.84, p = 0.07).
 
@@
 
+(X check for the past tense where applicable X)
 \begin{figure}[H]
@@
 \end{figure}
-We model the hairy pad as an array of $N$ cylindrical rods of length,
+
+We modelled the hairy pad as an array of $N$ cylindrical rods of length,
 $L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
@@
 
-To characterize the adhesive fluid and bubble volume we define two
+To characterise the adhesive fluid and bubble volume we defined two
 radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
@@
 
-All lengths are normalized w.r.t. $s_{f}$ and forces are normalized
+All lengths are normalised w.r.t. $s_{f}$ and forces are normalized
 w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values are fixed relative
@@
 
-First, we calculate force-distance curves for a single pinned liquid
+We first calculated force-distance curves for a single pinned liquid
 capillary bridge. Second, the effect of substrate on the force-distance
-curves of the hairy pad system is compared for each type of contact.
+curves of the hairy pad system was compared for each type of contact.
 Third, the effect of varying hair diameter, $D_{h}$, on net adhesion
@@
 Forces due to a single pinned capillary liquid bridge in contact with
-a substrate are obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
+a substrate were obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
 We see that, generally, the shape of the liquid meniscus determines
@@
 \subcaption{Force contributions}%
-\end{minipage}\caption{\label{fig:Single-bridge}Normalized capillary force of a single liquid
+\end{minipage}\caption{\label{fig:Single-bridge}Normalised capillary force of a single liquid
 bridge in contact with a substrate and pinned to a circular perimeter
@@
 
-The normalized force-distance curves of a hairy pad system on a hydrophilic
+The normalised force-distance curves of a hairy pad system on a hydrophilic
 and hydrophobic substrate are predicted based on the capillary bridge
@@
 air and underwater conditions. A negative force value represents attraction.
-Normalized forces are calculated from the capillary bridge model,
+Normalised forces are calculated from the capillary bridge model,
 with model parameters listed in Table \ref{tab:Model-parameters}.
@@
 angle, \ensuremath{\theta}, used to predict the ladybug's adhesion
-are labeled for each case.}
+are labelled for each case.}
 \end{figure}
@@
 
-We see that the bubble itself doesn't contribute much to the net force
+We observed that the bubble itself doesn't contribute much to the net force
 on either substrate (Figure \ref{fig:Effect-of-substrate}). Its contribution
@@
 \begin{figure}[H]
-\includegraphics{Figure7-Model_effect_of_bubble_volume}\caption{\label{fig:Effect-of-bubble}Normalized adhesion force of a hairy
+\includegraphics{Figure7-Model_effect_of_bubble_volume}\caption{\label{fig:Effect-of-bubble}Normalised adhesion force of a hairy
 pad system as a function of bubble volume, $\hat{V}_{b}$, for the
@@
 \end{figure}
+
 The volume of the bubble can influence its capillary force contribution,
@@
 
-From previous section, we know that on the hydrophilic substrate,
+From the previous section, we know that on the hydrophilic substrate,
 fluid bridges outside the bubble show poor adhesion due to the positive
@@
 the bubble. In contrast, on the hydrophobic substrate, fluid bridges
-outside the bubble show higher capillary forces, due to its low contact
+outside the bubble showed higher capillary forces, due to its low contact
 angle and high interfacial tension in water. Thus, adhesion force
@@
 
-A smaller $\hat{V}_{b}$ results in increased, but small, attraction
+A smaller $\hat{V}_{b}$ resulted in increased, but small, attraction
 by the bubble on both types of substrates. For larger values of $\hat{V}_{b}$
@@
 \begin{figure}[H]
-\includegraphics[scale=0.5]{Figure6-Model_effect_of_hair_size}\caption{\label{fig:Effect-of-hair}Normalized adhesion force of a hairy pad
+\includegraphics[scale=0.5]{Figure6-Model_effect_of_hair_size}\caption{\label{fig:Effect-of-hair}Normalised adhesion force of a hairy pad
 system on a hydrophilic and hydrophobic substrate as a function of
@@
 to a hydrophobic substrate even without a bubble trapped around its
-hairs. A previous study\cite{RN87} had hypothesized that a bubble
+hairs. A previous study\cite{RN87} proposed that a bubble
 is necessary for underwater attachment in beetles. This is, however,
@@
 agree with our experimental results (Figure \ref{fig:Effect-of-contact}).
-In underwater conditions without a trapped bubble, adhesion on a hydrophobic
-substrate is significantly larger than on a hydrophilic substrate.
-This is explained by the different oil interfacial tension and contact
+In underwater conditions without a trapped bubble, adhesion to a hydrophobic
+substrate is significantly larger than to a hydrophilic substrate.
+This is explained by the different interfacial tension of the oil and contact
 angles with the substrates in air and underwater, which determines
@@
 properties is thus essential to better predict the insect's adhesion,
-and will be a subject of future study. Further, due to surface inhomogeneities,
+and will be a subject of future studies. Further, due to surface inhomogeneities,
 not all the hairs might be able to completely drain the interfacial
@@
 give a theoretical maximum achievable adhesion force. In our experiments,
-however, the pad always makes contact with the substrate at a random
-orientation, which is difficult to control precisely. During detachment,
-the pad typically peels off from its proximal to distal end rather
+however, not all hairs make a perfect contact with the substrate despite our best efforts to align the pad with surface.
+Furthermore, during detachment, the pad typically peels off from its proximal to distal end rather
 than detach simultaneously. Our model also assumes the hairs to be
@@
 
-Our study provides further validation that capillary forces by the
-adhesive fluid control the insect's adhesion and van der Waals contribution,
+Our study provides further validation that capillary forces governs insect adhesion and van der Waals contribution,
 if any, must be negligible. Further, the capillary forces can even
 enable insect attachment underwater depending on the substrate chemistry.
-When underwater, without a trapped bubble, the pad adheres strongly
+When underwater, without a trapped bubble, the pads adhere strongly
 to a hydrophobic substrate, but poorly to a hydrophilic substrate,
 even though it shows similarly strong adhesion to both substrates
-in air. This behavior can only be explained by capillary forces. Our
+in air. This behavior can only be explained by capillary forces and the wetting properties of the fluid. Our
 preliminary FDMS results further provides validation to our assumption
@@
 The findings can also be extended to other animals relying on oily
-secretions for adhesion. Ants, for example, show similar adhesion
-on hydrophobic substrates under wet and dry conditions\cite{RN213},
-similar to what we see in a ladybug. Recent adhesion experiments on
-geckos reveal that they can attach well to fluoropolymer substrates
+secretions for adhesion. Some ants, for example, show similar adhesion
+on hydrophobic substrates under wet and dry conditions \cite{RN213},
+similar to what we see in a ladybug. Recent experiments on
+geckos revealed that they can attach well to fluoropolymer substrates
 underwater while they show little adhesion to the same substrate in
@@
 
-We have so far limited our analysis to only smooth substrates. Insects
-in the real world, however, interact with rough substrates very often.
+We have so far limited our analysis to only smooth substrates. Of course insects
+have to cope with all kinds of surfaces including rough ones.
 Previous studies \cite{RN136} have shown that substrate roughness
@@
 insect adhesion. Future work will explore how roughness can impact
-the net capillary force. Our study can have potential applications
-in the design of bio-inspired materials to achieve underwater adhesion
-via capillary bridges. Bubble can possibly be used to control underwater
+the net capillary force also in wet and submerged conditions. 
+Our study thus can contribute to potential applications in the design of bio-inspired materials to achieve underwater adhesion
+via capillary bridges. Introduced bubbles can possibly be used to control underwater
 adhesion by changing the relative proportion of the arrays inside
@@
 Ladybug beetles rely primarily on their oily fluid secretion to adhere
-to surfaces in both air and underwater conditions. The beetle can
+to surfaces in both air and underwater conditions. The beetles can
 attach underwater on a hydrophobic substrate even without a trapped
@@
 in geckos \cite{RN15}, which highlights the possibility of capillary
-contributions to gecko adhesion. Future studies should characterize
+contributions to gecko adhesion. Future studies should characterise
 the fluid secretion's interfacial properties with a particular substrate
@@
 We are grateful to Eduard Arzt and Ren\textcyr{\`\cyre} Hensel for
-fruitful discussions. This work was funded by \emph{Deutsche Forschungsgemeinschaft}
+fruitful discussions. This work was funded by the \emph{Deutsche Forschungsgemeinschaft}
 (Grant number: PI 1351/2-1).
@@
 For the case of a bubble meniscus, $\theta$ is defined w.r.t. the
-surrounding water, since $\theta$ can also directly characterize
+surrounding water, since $\theta$ can also directly characterise
 the substrate wettability. The capillary bridge spans a gap distance
@@
 the top face and constant interfacial tension with the substrate on
-the bottom. All lengths are normalized relative to length $s=\left(3V/4\pi\right)^{1/3}$.
+the bottom. All lengths are normalised relative to length $s=\left(3V/4\pi\right)^{1/3}$.
 An appropriate geometry refinement routine is chosen to evolve the
-capillary bridge shape to its minimum energy state. The normalized
+capillary bridge shape to its minimum energy state. The normalised
 total capillary force, $\hat{f}=f/\gamma s$, is the sum of the Laplace
@@
 \begin{centering}
-\includegraphics{FigureS2-Effect_of_fluid_volume}\caption{Normalized maximum capillary force for a single bridge as a function
+\includegraphics{FigureS2-Effect_of_fluid_volume}\caption{Normalised maximum capillary force for a single bridge as a function
 of fluid volume}
@@
 
-\caption{Normalized adhesion force of hairy pad system on a hydrophilic and
+\caption{Normalised adhesion force of hairy pad system on a hydrophilic and
 hydrophobic substrate as a function of hair diameter ($D_{h}$), calculated

### 2021-02-15 source/tex/ladybug_adhesion.tex
modified Thomas corrections
checked British English spelling
updated figure 9 reference number

@@
 
-\title{Wetting properties of the adhesive fluid allows beetles to attach to surfaces not just in air but also underwater}
+\title{Wetting of the adhesive fluid controls underwater adhesion in insects}
 
@@
 \email{endlein01@mpip-mainz.mpg.de}
-
-\phone{+49 6131 379 111}
-
-\fax{+49 6131 379 310}
 
@@
 
-Many beetles can climb smooth surfaces using hairy adhesive pads on their legs.
+Many insects can climb smooth surfaces using hairy adhesive pads on their legs.
 It was previously shown that a terrestrial beetle can even adhere and walk underwater.
 The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air.
-However, it remained unclear to what extend such an air bubble is necessary for underwater adhesion and if the bubble contributes to the net adhesive force.
+However, it remained unclear to what extent such an air bubble is necessary for underwater adhesion.
 To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air.
@@
 We modelled the adhesion of a hairy pad using capillary forces.
-Coherent with our experiments, the model demonstrates that the wetting properties of the adhesive fluid alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion.
+Coherent with our experiments, the model demonstrates that the wetting properties of the adhesive fluid secretion alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion.
 \end{abstract}
@@
 Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly.
-The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) like seen in spiders and lizards but are typically undivided in most insects.
+The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects.
 The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}.
 Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion.
-All insect pads secrete an adhesive fluid while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion'').
+All insect pads secrete an adhesive fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion'').
 In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.
@@
 While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored.
-Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} using suction cups to adhere to surfaces.
-However, underwater adhesion using secreted liquids (glue-like substances or the adhesive fluid) requires the displacement of the water in the interface first and a spreading of the fluid on the substrate.
-Furthermore, the spreading coefficient of the secreted liquid needs to be larger than that of the water in order to utilise the interfacial tension between the liquids as an adhesive force.
-One relative simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}.
-This has been shown in a recent study by \citet{RN87} on the ability of a terrestrial leaf beetle which can attach quite well to surfaces underwater by using such an air bubble.
+Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces.
+However, underwater adhesion using secreted liquids (glue-like substances or the adhesive fluid) requires the displacement of the water at the interface first and a spreading of the fluid on the substrate.
+One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}.
+This has been shown in a recent study by \citet{RN87} that a terrestrial leaf beetle can attach quite well to surfaces underwater by using such an air bubble.
 Their naturally hydrophobic hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact.
-It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the dewetted area results in its adhesion underwater.
+It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater.
 However, it remained unclear whether an air bubble is strictly necessary and its exact contribution to the adhesive force.
-The oily adhesive fluid found in insects alone might be sufficient in creating the necessary interfacial tension even without an bubble, given that the adhesive fluid remains on the hairs when submerged.
-In beetles, the tip of each seta secretes approximately one femtoliter of oily adhesive fluid \cite{RN108}.
-The fluid's chemical composition is identified as a mixture of mostly long chain hydrocarbons\cite{RN96} with traces
-of triglycerides, fatty acids and cholesterol\cite{RN221,RN222} rendering it immiscible with water.
-%A recent study by Gernay et.
-al.\cite{RN77}, based on an elastocapillary model, has been able to reasonably predict single seta adhesion forces theoretically, confirming the dominant role of surface tension in the ``wet adhesion'' of beetles.
-
-% Geckos are also known to adhere underwater, where its shear adhesion force on hydrophobic substrates are similar in both air and underwater conditions.
-Interestingly, its adhesion on a fluorinated substrate is even larger underwater than in air\cite{RN15}.
-This has been partially explained by a thermodynamic work of adhesion model, assuming full displacement of water at the interface, leading to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.
-
-The goal of this paper is to provide a generalised picture of adhesion in insects which use hairy pads and secrete a oily fluid for attachment.
-We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion of individual adhesive pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces.
-We further tested whether the chemical profile of the adhesive fluid changes when the hairs being submerged in water.
+The oily adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hairs when submerged.
+In beetles, the tip of each seta secretes approximately one femtoliter of adhesive fluid \cite{RN108}.
+The fluid's chemical composition was identified to be an oil-like mixture of mostly long chain hydrocarbons\cite{RN96} with traces
+of triglycerides, fatty acids and cholesterol\cite{RN221,RN222}, rendering it immiscible with water.
+
+The goal of this paper is to provide a generalised picture of adhesion in insects which use hairy pads and secrete an oily fluid for attachment.
+We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces.
+We further tested whether the chemical profile of the adhesive fluid changes when the hairs were submerged in water.
 Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions.
@@
 beetle were performed. We characterised adhesion by the pull-off force
-during detachment and tested smooth glass and
+during detachment, tested on smooth glass and
 fluorinated surfaces representing hydrophilic and hydrophobic substrates
@@
 Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
-purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
+were purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
 twigs and stones at room temperature and 60-80\% relative humidity
@@
  %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
-An individual beetle was first carefully anesthetised using small amounts of CO\textsubscript{2} sublimating
+An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
 from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball.
 The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}).
-The bracket with the ball and the beetle could be further positioned by manual micromanipulators in all three axes before the experiments.
-One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blue-Tac (X) allowing us to further align the leg to the substrate.
+The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments.
+One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.) allowing us to further align the leg to the substrate.
 The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate.
@@
 A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test.
-After the measurements, the beetle was freed by carefully removing the epoxy glue and Blue-Tac without harming it and set free.
+After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.
 
@@
 Adhesion measurements were performed on a custom force measurement
-setup developed in-house (Figure \ref{fig:Setup}). A fiber optic
+setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
 displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
 with a steel bending beam (spring constant = 68.1 N/m) constitutes
-the (vertical) force sensor. Beam deflection was calibrated using 4
+the vertical force sensor. Beam deflection was calibrated using 4
 different known weights to get the corresponding force. A plastic
@@
 as well as observe the contact. The sensor was mounted on a stage
-consisting of a X-piezo, used for precise lateral movements, XYZ motors,
+consisting of a X-piezo element, used for precise lateral movements, XYZ motors,
 for coarse movements and a goniometer, for adjusting substrate alignment
-with the optics. Additionally, a separate Z-piezo, fixed upright,
+with the optics. Additionally, a separate Z-piezo element, fixed upright,
 was used for vertical up-down motion, bringing the insect in contact
@@
 (\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
-with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 pixel; XBasler)
+with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 px; \emph{Basler ace U}, 1280 x 1024 px)
 were used to record the sample contact with the substrate from ventral
 and side views respectively. Pad contact area was visualised through
-the substrate with help of epi-illumination.
+the substrate under reflection mode with the help of epi-illumination.
 The data acquisition from the force sensor and cameras, together with
@@
 adhesion tests with the substrate to get the pull-off force. However,
-instead of a simple down-up motion, an additional 100 \textgreek{m}m lateral sliding motion was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
-A further 10 \textgreek{m}m compression step (approach) set all hairs in slight compression which helped further contact
+instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
+A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
 with the surface. Next, a short pause (1 s) removed any
@@
 substrate. All approach, retract and lateral slide motion was done
-at a speed of 62.5 \textgreek{m}m/s. Ventral view video recordings
+at a speed of 62.5 \textmu m/s. Ventral view video recordings
 were used for contact area extraction while the side view imaging
@@
 the pad was brought into contact with the surface 10 times repeatedly 
-to equilibrate the pad system (X what do you mean by equilibrate?).
+to equilibrate the pad's secretion system.
 
@@
 contact area of a distal pad are shown in the plot, in which, the shaded
-regions represent distinct movements like approach, lateral pull, pre-load and detachment... (please explain which ones X). Negative force values
+regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
 represent attraction and the minimum force peak during the final retraction
-step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material Xshould we provide one?}
+step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material.}
 \end{figure}
@@
 water surface shifted, which influenced the force readout due to surface
-tension effects. This effect needed to be canceled. So, a ``background''
+tension effects. This effect needed to be cancelled. So, a ``background''
 force data was recorded, where the submerged beetle makes no contact
@@
 
-Standard 20 mm wide glass coverslips were used as the hydrophilic
+Standard 20 mm wide glass cover-slips were used as the hydrophilic
 substrate. Glass was wiped with isopropanol, rinsed in water and dried
@@
 For the hydrophobic substrate, the glass cover slip was coated with
-a fluorosilane via chemical vapor deposition (CVD). First, the glass
+a fluorosilane via chemical vapour deposition (CVD). First, the glass
 was cleaned using IPA and plasma treated as before. Next, 0.2 ml of
@@
 
-The substrate wettability was characterised by dynamic contact angle
+The substrate wetting was characterised by dynamic contact angle
 measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
@@
 and receding contact angles were measured for a maximum drop volume
-of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate.
+of 10 \textmu l and with 0.5 \textmu l/s flow rate.
 
@@
 
-A previous study on archanids \cite{RN223} reported that its secreted
+A previous study on arachnids \cite{RN223} reported that its secreted
 fluid does not dissolve in water. To test whether the beetles retain
@@
 legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
-axyridis} X the fact we are introducing a new species is a bit odd and could raise a question with the reviewer but I don't know a good way around it.
-we could bring it in the introduction and say that these are preliminary/unpublished results.
-that would be perfectly viable) was immersed in 50 \textmu L THF for 20 min and then transferred
+axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
 to the measurement chamber of the FDMS. As a reference, pure THF was
@@
 larger than on glass (p < 0.001). This stronger adhesion on PFOTS
-is observed both in the presence and absence of a trapped bubble.
-In both cases, adhesion force reach similar values as in air. In contrast,
-on glass, adhesion underwater is significantly reduced as compared
+was observed both in the presence and absence of a trapped bubble.
+In both cases, the adhesion force reached similar values as in air. In contrast,
+on glass, adhesion underwater was significantly reduced when compared
 to dry conditions, irrespective of the presence of a trapped bubble
@@
 represent the contribution of the bubble itself, calculated from the
-capillary bridge model. In the model, hair diameter = 4 \textgreek{m}m,
-pad diameter = 200 \textgreek{m}m, hair height = 40 \textgreek{m}m,
+capillary bridge model. In the model, hair diameter = 4 \textmu m,
+pad diameter = 200 \textmu m, hair height = 40 \textmu m,
 N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
@@
 to the resultant molecular weights, include mostly aliphatic hydrocarbons
-with traces of aldehydes.
+with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
+to assert that, even for the case of \emph{Coccinella
+septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments.
 
@@
 \end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
-with and without rinsing the beetle's leg in water. Molecular weights
-were extracted from the peaks in the FDMS spectra. \label{tab:Molecular-distribution-of}}
+with and without rinsing the beetle's leg in water. \label{tab:Molecular-distribution-of}}
 \end{table}
@@
 
-(X check for the past tense where applicable X)
 \begin{figure}[H]
@@
 $L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
-$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad are assumed
+$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
 to be perfectly rigid, for simplicity. The tip of each hair has an
@@
 The fluid is pinned to the circumference of the hair and forms a capillary
-bridge of height, $d$. Similar to our experiments, we consider three
+bridge of height, $d$. Similar to our experiments, we considered three
 types of contacts for the pad: 1) \emph{In air}, 2) \emph{Underwater:
@@
 
-To characterise the adhesive fluid and bubble volume we defined two
+To characterise the adhesive fluid and bubble volume, we defined two
 radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
@@
 are the radii of spheres with equivalent volumes. Fluid and bubble
-radii are assumed to scale proportional to their corresponding pinned
+radii were assumed to scale proportional to their corresponding pinned
 contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$
@@
 respectively, to conveniently scale their volumes relative to the
-hair and pad diameters they were pinned to.
+hair and pad diameters they are pinned to.
 
@@
 tension and Laplace pressure (equation \ref{eq:f_bridge}). Force
-versus distance for a single capillary bridge is calculated by Surface
-Evolver simulations\cite{RN206}, (described in \ref{subsec:Simulation-Method})
+versus distance for a single capillary bridge was calculated by Surface
+Evolver simulations\cite{RN206}  (described in \ref{subsec:Simulation-Method}),
 and used to obtain $F_{net}$ as a function of $d$ for each type
-of contact. The adhesion force of the complete hairy pad system is
+of contact. The adhesion force of the complete hairy pad system was
 then obtained from the minima of $F_{net}$, where negative force
@@
 
-We have considered $f_{air}$ and $f_{water}$ to be distinct terms
-because the capillary force by the adhesive fluid will be different
+We considered $f_{air}$ and $f_{water}$ to be distinct terms
+because the capillary force by the adhesive fluid would be different
 in air and underwater due to its different contact angle and interfacial
@@
 
-All lengths are normalised w.r.t. $s_{f}$ and forces are normalized
-w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values are fixed relative
-to $\gamma_{fa}$. Non dimensional bubble volume is expressed as,
+All lengths were normalised w.r.t. $s_{f}$ and forces were normalized
+w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values were fixed relative
+to $\gamma_{fa}$. Non dimensional bubble volume was expressed as,
 $\hat{V}_{b}=V_{b}/s_{f}^{3}$
 
-Geometric parameters and interfacial properties are kept fixed for
+Geometric parameters and interfacial properties were kept fixed for
 all model calculations (Table \ref{tab:Model-parameters}). Here,
-we assume the adhesive fluid to be an oil-lke substance and thus the
+we assumed the adhesive fluid to be an oil-lke substance and thus the
 interfacial tension ratios $\gamma_{wa}/\gamma_{fa}$ and $\gamma_{fw}/\gamma_{fa}$
-are taken corresponding to typical values of oil and water. We consider
+were taken corresponding to typical values for oil and water. We considered
 representative hydrophilic and hydrophobic substrates with $\theta_{fa}$
@@
 pad, $\alpha=ND_{h}^{2}/D_{p}^{2}$, hair aspect ratio, $L/D_{h}$,
-and fluid size parameter, $\phi_{f}$, are fixed to values typical
+and fluid size parameter, $\phi_{f}$, were fixed to values typical
 for a ladybug's hairy pad.
 
-We first calculated force-distance curves for a single pinned liquid
+First, we calculated force-distance curves for a single pinned liquid
 capillary bridge. Second, the effect of substrate on the force-distance
 curves of the hairy pad system was compared for each type of contact.
-Third, the effect of varying hair diameter, $D_{h}$, on net adhesion
-is studied. Finally, we look at the effect of changing the bubble
+Third, we looked at the effect of changing the bubble
 volume, $\hat{V}_{b}$, on the net underwater adhesion.
+Finally, the influence of varying the hair diameter, $D_{h}$, on adhesion
+was studied for each case.
 
@@
 only true for hydrophilic substrates, where a trapped bubble can facilitate
-underwater adhesion due to the hairs making contact in a dewetted
+underwater adhesion due to the hairs making contact in a de-wetted
 environment. For a hydrophobic substrate, the adhesion is similar
@@
 of a single similarly sized bubble making contact with a hydrophobic
-substrate shows a maximum adhesion less than 50 \textgreek{m}N, which
+substrate shows a maximum adhesion less than 50 \textmu N, which
 further validates that the bubble's contribution is insignificant
@@
 
-Our study provides further validation that capillary forces governs insect adhesion and van der Waals contribution,
+Our study provides further validation that capillary forces govern insect adhesion and van der Waals contribution,
 if any, must be negligible. Further, the capillary forces can even
@@
 even though it shows similarly strong adhesion to both substrates
-in air. This behavior can only be explained by capillary forces and the wetting properties of the fluid. Our
+in air. This behaviour can only be explained by capillary forces and the wetting properties of the fluid. Our
 preliminary FDMS results further provides validation to our assumption
@@
 geckos \cite{RN205} could change that picture. Since geckos adhere
-poorly to PTFE (surface energy \textasciitilde{} 20 mN/m) one can
+poorly to PTFE (surface energy $\sim$ 20 mN/m) one can
 speculate that the phospholipid material has a higher surface energy,
@@
 indicate a capillary contribution to gecko adhesion. We suggest performing
-single seta adhesion force tests similar to Autumn et. al. \cite{RN202}
+single seta adhesion force tests similar to \citet{RN202}
 using a hydrophilic and fluorinated probe in air and underwater conditions
@@
 on various substrates. Experimental shear adhesion values are reproduced
-from Stark et. al. \cite{RN15}. Normal adhesion forces for each gecko
+from \citet{RN15}. Normal adhesion forces for each gecko
 toe are theoretically estimated from the capillary bridge model, with
@@
 are 50\textdegree , 85\textdegree , 94\textdegree{} and 97\textdegree{}
-respectively, as reported in Stark et. al. \cite{RN15}.}
+respectively, as reported in \citet{RN15}.}
 \end{figure}
@@
 a hydrophilic substrate. This is explained theoretically by the different
-contact angle and interfacial tension of the adhesive fluid in air
+contact angle and interfacial tension of the secreted fluid in air
 and underwater conditions. Further, the bubble itself has a negligible
@@
 \section{Appendix}
+%reset figure/table/equation numbers and include prefix
+\setcounter{figure}{0} \renewcommand{\thefigure}{A.\arabic{figure}} 
+\setcounter{table}{0} \renewcommand{\thetable}{A.\arabic{table}} 
+\setcounter{equation}{0} \renewcommand{\theequation}{A.\arabic{equation}}
 
@@
 
-\setcounter{figure}{0} \renewcommand{\thefigure}{A.\arabic{figure}} 
-\setcounter{equation}{0} \renewcommand{\theequation}{A.\arabic{equation}} Capillary
-force due to a single adhesive fluid or bubble meniscus (termed ``capillary
+ Capillary force due to a single adhesive fluid or bubble meniscus (termed ``capillary
 bridge'') is calculated by performing simulations in Surface Evolver
-\cite{RN206}, similar to the method described by De Souza et. al.\cite{RN93}.
+\cite{RN206}, similar to the method described by \citet{RN93}.
 A simple cubic geometry, mimicking the capillary bridge, of constant
@@
 is pinned to a micropatterned PDMS substrate on the top. The maximum
-adhesion force of any of the bubble never exceeds 50 \textgreek{m}N,
+adhesion force of any of the bubble never exceeds 50 \textmu N,
 significantly lower than the beetle's underwater adhesion to the same
-substrate (> 400 \textgreek{m}N). Thus, the bubble's contribution
+substrate (> 400 \textmu N). Thus, the bubble's contribution
 to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's

### 2021-02-16 source/tex/ladybug_adhesion.tex
moved appendix section to separate supplementary file.
hard coded references pointing to supplementary file.

@@
 \documentclass[english]{achemso}
+\setkeys{acs}{keywords = true}
 \usepackage[T2A,LGR,T1]{fontenc}
@@
  {hyperref}
+%\usepackage{lineno}
+%\linenumbers
 
@@
 \email{endlein01@mpip-mainz.mpg.de}
+
+\keywords{adhesion; capillary force; underwater;  beetle; gecko}
 
@@
 glass and PFOTS were similar, i.e. no significant differences were
-detected (Figure \ref{fig:Effect-of-contact} and Table \ref{tab:Statistical-analysis}).
+detected (Figure \ref{fig:Effect-of-contact} and Table S.1).
 In contrast, the underwater adhesion on a PFOTS surface was significantly
@@
 The capillary force, $f$, is the sum of two contributions: surface
-tension and Laplace pressure (equation \ref{eq:f_bridge}). Force
+tension and Laplace pressure (equation S.1). Force
 versus distance for a single capillary bridge was calculated by Surface
-Evolver simulations\cite{RN206}  (described in \ref{subsec:Simulation-Method}),
+Evolver simulations\cite{RN206}  (described in supplementary section S.1),
 and used to obtain $F_{net}$ as a function of $d$ for each type
@@
 are plotted as a function of contact angle with the substrate, together
-with its Laplace and surface tension components (equation \ref{eq:f_bridge}).
+with its Laplace and surface tension components (equation S.1).
 Simulation snapshots of the liquid meniscus corresponding to angles
@@
 further validates that the bubble's contribution is insignificant
-(\ref{subsec:Capillary-force-due}).
+(Figure S.3).
 
@@
 We are grateful to Eduard Arzt and Ren\textcyr{\`\cyre} Hensel for
-fruitful discussions. This work was funded by the \emph{Deutsche Forschungsgemeinschaft}
+fruitful discussions. This work was supported by the \emph{Deutsche Forschungsgemeinschaft}
 (Grant number: PI 1351/2-1).
-
-\appendix
-
-\section{Appendix}
-%reset figure/table/equation numbers and include prefix
-\setcounter{figure}{0} \renewcommand{\thefigure}{A.\arabic{figure}} 
-\setcounter{table}{0} \renewcommand{\thetable}{A.\arabic{table}} 
-\setcounter{equation}{0} \renewcommand{\theequation}{A.\arabic{equation}}
-
-\subsection{Simulation method: Single capillary bridge \label{subsec:Simulation-Method}}
-
- Capillary force due to a single adhesive fluid or bubble meniscus (termed ``capillary
-bridge'') is calculated by performing simulations in Surface Evolver
-\cite{RN206}, similar to the method described by \citet{RN93}.
-A simple cubic geometry, mimicking the capillary bridge, of constant
-volume, $V$, is defined as the initial condition with an interfacial
-tension, $\gamma$, with the surrounding medium. Interfacial tension
-of the capillary bridge with the substrate is given by $\gamma\cos\theta$,
-where $\theta$ is the corresponding contact angle inside the bridge.
-For the case of a bubble meniscus, $\theta$ is defined w.r.t. the
-surrounding water, since $\theta$ can also directly characterise
-the substrate wettability. The capillary bridge spans a gap distance
-$d$ between the top face and the substrate. The boundary conditions
-are set corresponding to a pinned contact line of diameter $D$ on
-the top face and constant interfacial tension with the substrate on
-the bottom. All lengths are normalised relative to length $s=\left(3V/4\pi\right)^{1/3}$.
-An appropriate geometry refinement routine is chosen to evolve the
-capillary bridge shape to its minimum energy state. The normalised
-total capillary force, $\hat{f}=f/\gamma s$, is the sum of the Laplace
-pressure and surface tension contributions , where:
-
-\begin{equation}
-f=f_{laplace}+f_{surface\,tension}=\varDelta P_{laplace}A_{_{bottom}}+2\pi R_{bottom}\gamma\sin\theta\label{eq:f_bridge}
-\end{equation}
-
-Here, $\varDelta P_{laplace}$ is the Laplace pressure of the equilibrium
-capillary bridge, $A_{bottom}$ is the contact area of the capillary
-bridge with the substrate at bottom and $R_{bottom}$ is the corresponding
-radius of contact, all obtained from the simulation output for the
-equilibrium surface.
-
-The gap distance $d$ is varied stepwise and the capillary force is
-calculated each time to obtain force-distance curves for a particular
-choice of $D$ and $\theta$.
-
-\subsection{Single capillary bridge: Effect of volume}
-
-Surface Evolver simulation results showing the effect of volume on
-the maximum capillary force of a single fluid bridge. Since the fluid
-is pinned at the top to the same diameter, D, a smaller volume would
-result in high interfacial curvatures, which increases the capillary
-force due to the negative Laplace pressure. In this case, small contact
-angles lead to a greater increase in adhesion.
-
-\begin{figure}[H]
-
-\begin{centering}
-\includegraphics{FigureS2-Effect_of_fluid_volume}\caption{Normalised maximum capillary force for a single bridge as a function
-of fluid volume}
-\par\end{centering}
-\end{figure}
-
-\subsection{Capillary Bridge Model: Effect of hair diameter at constant fluid
-volume}
-
-Here, instead of scaling the fluid volume relative to the hair diameter,
-we now assume a fixed total fluid volume distributed equally among
-the $N$ hairs. Total fluid volume, $V_{total}=NV_{f}=2000$. Hair
-diameter is varied while keeping the total hair contact area constant.
-Length is in arbitrary units. Forces increase at a much smaller rate
-on decreasing diameter when compared to the case with self-similar
-scaling of fluid volume (Figure \ref{fig:Effect-of-hair}).
-
-\begin{figure}[H]
-\includegraphics{FigureS3-Effect_of_hair_size(constant_vol)}
-
-\caption{Normalised adhesion force of hairy pad system on a hydrophilic and
-hydrophobic substrate as a function of hair diameter ($D_{h}$), calculated
-from the capillary bridge model. The total adhesive fluid volume is
-fixed to 2000. Adhesion forces are calculated from minima of the respective
-force-distance curves. Negative force value represents attraction.
-The bubble's contribution to the net force for an \emph{underwater:
-bubble} contact is denoted by plus symbols. Bubble volume and pad
-diameter are kept fixed. All lengths are scaled relative to $D_{p}$.}
-\end{figure}
-
-\subsection{Statistical comparison}
-
-Pairwise statistical comparison of single leg adhesion force measurements
-of the ladybug beetle (\emph{Coccinella septempuctata}) for each contact
-type and substrate are shown (Table \ref{tab:Statistical-analysis}).
-The uncorrected p-values and Common Language Effect Size (CLES) are
-obtained from post-hoc pair-wise Student t-test between A and B while
-keeping the third parameter fixed. p-values showing statistically
-significant difference between A and B are in boldface. The condition
-for statistical significance is based on the Bonferroni-corrected
-critical p-value of 0.008.
-
-\begin{table}[H]
-\noindent \begin{centering}
-\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|}
-\hline 
-Fixed & A & B & p-value & CLES\tabularnewline
-\hline 
-\hline 
-In air & PFOTS & Glass & 0.959 & 0.48\tabularnewline
-\hline 
-Underwater: bubble & PFOTS & Glass & 0.011 & 0.96\tabularnewline
-\hline 
-Underwater: no bubble & PFOTS & Glass & \textbf{< 0.001} & 1.0\tabularnewline
-\hline 
-PFOTS & In air & Underwater: bubble & 0.897 & 0.48\tabularnewline
-\hline 
-PFOTS & In air & Underwater: no bubble & 0.828 & 0.48\tabularnewline
-\hline 
-PFOTS & Underwater: bubble & Underwater: no bubble & 0.721 & 0.44\tabularnewline
-\hline 
-Glass & In air & Underwater: bubble & \textbf{0.002} & 1.0\tabularnewline
-\hline 
-Glass & In air & Underwater: no bubble & \textbf{< 0.001} & 1.0\tabularnewline
-\hline 
-Glass & Underwater: bubble & Underwater: no bubble & 0.07 & 0.84\tabularnewline
-\hline 
-\end{tabular}
-\par\end{centering}
-\caption{\label{tab:Statistical-analysis}}
-\end{table}
-
-\subsection{Capillary force due to a bubble\label{subsec:Capillary-force-due}}
-
-Capillary force of a single bubble against a PFOTS surface are compared
-for two different volumes. The volumes correspond to the expected
-range in the case of the trapped bubble in a ladybug. Here, the bubble
-is pinned to a micropatterned PDMS substrate on the top. The maximum
-adhesion force of any of the bubble never exceeds 50 \textmu N,
-significantly lower than the beetle's underwater adhesion to the same
-substrate (> 400 \textmu N). Thus, the bubble's contribution
-to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
-pad should be negligible.
-
-\begin{figure}[H]
-\begin{centering}
-\includegraphics{FigureS4-Expt_bubble_force}\caption{Capillary force of the bubble}
-\par\end{centering}
-\end{figure}
 

### 2021-02-16 source/tex/supplementary.tex
moved appendix section to separate supplementary file.
hard coded references pointing to supplementary file.

\documentclass[english]{achemso}
\setkeys{acs}{keywords = true, email=false}
\usepackage[T2A,LGR,T1]{fontenc}
\usepackage{babel}
\usepackage{array}
\usepackage{textcomp}
\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subscript}
%\usepackage[unicode=true,pdfusetitle,
% bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
% breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
% {hyperref}
%\usepackage{lineno}
%\linenumbers

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.

\title{Wetting of the adhesive fluid controls underwater adhesion in insects: Supplementary material}

\author{Pranav Sudersan}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Michael Kappl}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Bat-El Pinchasik}

\affiliation{School of Mechanical Engineering, Tel Aviv University, Tel Aviv-Yafo,
Israel}

\author{Hans-J\"{u}rgen Butt}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\author{Thomas Endlein}

\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
Mainz, Germany}

\DeclareRobustCommand{\greektext}{%
  \fontencoding{LGR}\selectfont\def\encodingdefault{LGR}}
\DeclareRobustCommand{\textgreek}[1]{\leavevmode{\greektext #1}}
\ProvideTextCommand{\~}{LGR}[1]{\char126#1}

\DeclareRobustCommand{\cyrtext}{%
  \fontencoding{T2A}\selectfont\def\encodingdefault{T2A}}
\DeclareRobustCommand{\textcyr}[1]{\leavevmode{\cyrtext #1}}

\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\SectionNumbersOn
%\setkeys{acs}{doi = true}
\setkeys{Gin}{width=\linewidth}
\usepackage{subcaption}

\makeatother

\begin{document}
%reset figure/table/equation numbers and include prefix
\renewcommand{\thesection}{S.\arabic{section}}
\setcounter{figure}{0} \renewcommand{\thefigure}{S.\arabic{figure}} 
\setcounter{table}{0} \renewcommand{\thetable}{S.\arabic{table}} 
\setcounter{equation}{0} \renewcommand{\theequation}{S.\arabic{equation}}

\section{Simulation method: Single capillary bridge \label{subsec:Simulation-Method}}

 Capillary force due to a single adhesive fluid or bubble meniscus (termed ``capillary
bridge'') is calculated by performing simulations in Surface Evolver
\cite{RN206}, similar to the method described by \citet{RN93}.
A simple cubic geometry, mimicking the capillary bridge, of constant
volume, $V$, is defined as the initial condition with an interfacial
tension, $\gamma$, with the surrounding medium. Interfacial tension
of the capillary bridge with the substrate is given by $\gamma\cos\theta$,
where $\theta$ is the corresponding contact angle inside the bridge.
For the case of a bubble meniscus, $\theta$ is defined w.r.t. the
surrounding water, since $\theta$ can also directly characterise
the substrate wettability. The capillary bridge spans a gap distance
$d$ between the top face and the substrate. The boundary conditions
are set corresponding to a pinned contact line of diameter $D$ on
the top face and constant interfacial tension with the substrate on
the bottom. All lengths are normalised relative to length $s=\left(3V/4\pi\right)^{1/3}$.
An appropriate geometry refinement routine is chosen to evolve the
capillary bridge shape to its minimum energy state. The normalised
total capillary force, $\hat{f}=f/\gamma s$, is the sum of the Laplace
pressure and surface tension contributions , where:

\begin{equation}
f=f_{laplace}+f_{surface\,tension}=\varDelta P_{laplace}A_{_{bottom}}+2\pi R_{bottom}\gamma\sin\theta\label{eq:f_bridge}
\end{equation}

Here, $\varDelta P_{laplace}$ is the Laplace pressure of the equilibrium
capillary bridge, $A_{bottom}$ is the contact area of the capillary
bridge with the substrate at bottom and $R_{bottom}$ is the corresponding
radius of contact, all obtained from the simulation output for the
equilibrium surface.

The gap distance $d$ is varied stepwise and the capillary force is
calculated each time to obtain force-distance curves for a particular
choice of $D$ and $\theta$.

\section{Single capillary bridge: Effect of volume}

Surface Evolver simulation results showing the effect of volume on
the maximum capillary force of a single fluid bridge. Since the fluid
is pinned at the top to the same diameter, D, a smaller volume would
result in high interfacial curvatures, which increases the capillary
force due to the negative Laplace pressure. In this case, small contact
angles lead to a greater increase in adhesion.

\begin{figure}[H]

\begin{centering}
\includegraphics{FigureS2-Effect_of_fluid_volume}\caption{Normalised maximum capillary force for a single bridge as a function
of fluid volume}
\par\end{centering}
\end{figure}

bsection{Capillary Bridge Model: Effect of hair diameter at constant fluid
volume}

Here, instead of scaling the fluid volume relative to the hair diameter,
we now assume a fixed total fluid volume distributed equally among
the $N$ hairs. Total fluid volume, $V_{total}=NV_{f}=2000$. Hair
diameter is varied while keeping the total hair contact area constant.
Length is in arbitrary units. Forces increase at a much smaller rate
on decreasing diameter when compared to the case with self-similar
scaling of fluid volume (Figure 8 in main text).

\begin{figure}[H]
\includegraphics{FigureS3-Effect_of_hair_size(constant_vol)}

\caption{Normalised adhesion force of hairy pad system on a hydrophilic and
hydrophobic substrate as a function of hair diameter ($D_{h}$), calculated
from the capillary bridge model. The total adhesive fluid volume is
fixed to 2000. Adhesion forces are calculated from minima of the respective
force-distance curves. Negative force value represents attraction.
The bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Bubble volume and pad
diameter are kept fixed. All lengths are scaled relative to $D_{p}$.}
\end{figure}

\section{Statistical comparison}

Pairwise statistical comparison of single leg adhesion force measurements
of the ladybug beetle (\emph{Coccinella septempuctata}) for each contact
type and substrate are shown (Table \ref{tab:Statistical-analysis}).
The uncorrected p-values and Common Language Effect Size (CLES) are
obtained from post-hoc pair-wise Student t-test between A and B while
keeping the third parameter fixed. p-values showing statistically
significant difference between A and B are in boldface. The condition
for statistical significance is based on the Bonferroni-corrected
critical p-value of 0.008.

\begin{table}[H]
\noindent \begin{centering}
\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|}
\hline 
Fixed & A & B & p-value & CLES\tabularnewline
\hline 
\hline 
In air & PFOTS & Glass & 0.959 & 0.48\tabularnewline
\hline 
Underwater: bubble & PFOTS & Glass & 0.011 & 0.96\tabularnewline
\hline 
Underwater: no bubble & PFOTS & Glass & \textbf{< 0.001} & 1.0\tabularnewline
\hline 
PFOTS & In air & Underwater: bubble & 0.897 & 0.48\tabularnewline
\hline 
PFOTS & In air & Underwater: no bubble & 0.828 & 0.48\tabularnewline
\hline 
PFOTS & Underwater: bubble & Underwater: no bubble & 0.721 & 0.44\tabularnewline
\hline 
Glass & In air & Underwater: bubble & \textbf{0.002} & 1.0\tabularnewline
\hline 
Glass & In air & Underwater: no bubble & \textbf{< 0.001} & 1.0\tabularnewline
\hline 
Glass & Underwater: bubble & Underwater: no bubble & 0.07 & 0.84\tabularnewline
\hline 
\end{tabular}
\par\end{centering}
\caption{\label{tab:Statistical-analysis}}
\end{table}

\section{Capillary force due to a bubble\label{subsec:Capillary-force-due}}

Capillary force of a single bubble against a PFOTS surface are compared
for two different volumes. The volumes correspond to the expected
range in the case of the trapped bubble in a ladybug. Here, the bubble
is pinned to a micropatterned PDMS substrate on the top. The maximum
adhesion force of any of the bubble never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible.

\begin{figure}[H]
\begin{centering}
\includegraphics{FigureS4-Expt_bubble_force}\caption{Capillary force of the bubble}
\par\end{centering}
\end{figure}

\bibliography{references}

\end{document}

### 2021-02-17 source/tex/ladybug_adhesion.tex
minor edits in supplementary file
organized supporting info
included evolver script and other relevant files

@@
 glass and PFOTS were similar, i.e. no significant differences were
-detected (Figure \ref{fig:Effect-of-contact} and Table S.1).
+detected (Figure \ref{fig:Effect-of-contact} and Table S1.1).
 In contrast, the underwater adhesion on a PFOTS surface was significantly
@@
 The capillary force, $f$, is the sum of two contributions: surface
-tension and Laplace pressure (equation S.1). Force
+tension and Laplace pressure (equation S1.1). Force
 versus distance for a single capillary bridge was calculated by Surface
-Evolver simulations\cite{RN206}  (described in supplementary section S.1),
+Evolver simulations\cite{RN206}  (described in supplementary section S1.1),
 and used to obtain $F_{net}$ as a function of $d$ for each type
@@
 are plotted as a function of contact angle with the substrate, together
-with its Laplace and surface tension components (equation S.1).
+with its Laplace and surface tension components (equation S1.1).
 Simulation snapshots of the liquid meniscus corresponding to angles
@@
 further validates that the bubble's contribution is insignificant
-(Figure S.3).
+(Figure S1.3).
 
@@
 fruitful discussions. This work was supported by the \emph{Deutsche Forschungsgemeinschaft}
-(Grant number: PI 1351/2-1).
+(Grant number: PI 1351/2-1) and the \emph{Max Planck Graduate Center} with the \emph{Johannes Gutenberg-Universit\"{a}t Mainz} (MPGC).
 

### 2021-05-04 source/tex/ladybug_adhesion.tex
minor comments of referees implemented partially

@@
 
-\title{Wetting of the adhesive fluid controls underwater adhesion in insects}
+\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles}
 
@@
 
-\keywords{adhesion; capillary force; underwater;  beetle; gecko}
+\keywords{bio-adhesion; capillary force; bubble; insects; gecko}
 
@@
 We modelled the adhesion of a hairy pad using capillary forces.
-Coherent with our experiments, the model demonstrates that the wetting properties of the adhesive fluid secretion alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion.
+Coherent with our experiments, the model demonstrates that the wetting properties of the tarsal adhesive fluid secretion alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion.
 \end{abstract}
@@
 
-The question on how insects and other small arboreal animals climb smooth and slippery
+The question on how insects and other small animals climb smooth and slippery
 surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}.
-We now know that such animals are able to adhere by using specialised organs on their feet called adhesive pads.
+We know that such animals are able to adhere by using specialised organs on their feet called adhesive pads.
 These adhesive pads can generally be described as either ``smooth'' or ``hairy''.
@@
 Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion.
-All insect pads secrete an adhesive fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion'').
+Insect tarsal hairs secrete an adhesion-mediating fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion'').
 In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.
@@
 Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces.
-However, underwater adhesion using secreted liquids (glue-like substances or the adhesive fluid) requires the displacement of the water at the interface first and a spreading of the fluid on the substrate.
+However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate.
 One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}.
-This has been shown in a recent study by \citet{RN87} that a terrestrial leaf beetle can attach quite well to surfaces underwater by using such an air bubble.
-Their naturally hydrophobic hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact.
+This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
+Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact.
 It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater.
-However, it remained unclear whether an air bubble is strictly necessary and its exact contribution to the adhesive force.
-The oily adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hairs when submerged.
-In beetles, the tip of each seta secretes approximately one femtoliter of adhesive fluid \cite{RN108}.
-The fluid's chemical composition was identified to be an oil-like mixture of mostly long chain hydrocarbons\cite{RN96} with traces
-of triglycerides, fatty acids and cholesterol\cite{RN221,RN222}, rendering it immiscible with water.
+However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force.
+The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hairs when submerged.
+In ladybug beetles, the tip of each seta secretes approximately one femtoliter of adhesive fluid by each step \cite{RN108}.
+The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
+of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water.
 
@@
 beetle were performed. We characterised adhesion by the pull-off force
-during detachment, tested on smooth glass and
-fluorinated surfaces representing hydrophilic and hydrophobic substrates
-respectively. When no water was present, we labelled the contact type
+during detachment, tested on smooth normal and
+fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
+respectively. When no water was present, we labelled the mode of contact
 as ``\emph{in air}''. Underwater, measurements
-were done both in the presence and absence of a trapped bubble (``\emph{underwater:
+were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
 bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
-investigate the bubble's role in underwater adhesion. Adhesion force
-for each of the labelled contact types were compared for both substrates.
+investigate the air bubble's role in underwater adhesion. Adhesion force
+for each of the labelled contact modes were compared for both substrates.
 
@@
 
-Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
+The seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
 were purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
@@
 The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate.
+Care was taken to ensure the glue doesn't contaminate the pads.
 Each leg of a male ladybug beetle has two pads.
@@
 which allowed us to fill it with water for the underwater experiments
-as well as observe the contact. The sensor was mounted on a stage
-consisting of a X-piezo element, used for precise lateral movements, XYZ motors,
-for coarse movements and a goniometer, for adjusting substrate alignment
-with the optics. Additionally, a separate Z-piezo element, fixed upright,
+as well as observe the contact. The force sensor was mounted on a stage
+consisting of a X-piezo element, used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
 was used for vertical up-down motion, bringing the insect in contact
-with the substrate from the top. A coaxial illuminated tube microscope
+with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors.
+A coaxial illuminated tube microscope
 (\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
@@
 and side views respectively. Pad contact area was visualised through
-the substrate under reflection mode with the help of epi-illumination.
+the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
+with the ventral view optics to achieve total internal reflection.
 The data acquisition from the force sensor and cameras, together with
@@
 at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
-the pad was brought into contact with the surface 10 times repeatedly 
+the pad was brought into contact with the dry surface 10 times repeatedly 
 to equilibrate the pad's secretion system.
@@
 \par\end{centering}
-\caption{\label{fig:Setup} Adhesion setup (for explanation see text). The recorded force data and
+\caption{\label{fig:Setup} Adhesion test setup (for explanation see text). The recorded force data and
 contact area of a distal pad are shown in the plot, in which, the shaded
@@
 and statistical analysis were all performed in ``\emph{Buggee}'',
-a tool written in Python using open-source libraries for synchronous
+a software tool written in Python using open-source libraries for synchronous
 analysis of force data and video recordings (\url{https://github.com/PranavSudersan/Buggee}).
@@
 For underwater measurements, an additional correction was necessary.
-When the beetle was submerged underwater, its contact line at the
+When the beetle was partially submerged underwater, its contact line at the
 water surface shifted, which influenced the force readout due to surface
-tension effects. This effect needed to be cancelled. So, a ``background''
+tension and buoyancy. This effect needed to be cancelled. So, a ``background''
 force data was recorded, where the submerged beetle makes no contact
@@
 septempuctata}) on glass and PFOTS substrates in air and underwater
-conditions. The two types of contact during underwater experiments
+conditions. The two modes of contact during underwater experiments
 are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
@@
 for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
-fingerprint remained unchanged This indicates that the adhesion fluid
+fingerprint remained unchanged. This indicates that the adhesion fluid
 was not washed away underwater. Probable compounds in the fluid, corresponding
@@
 (\ref{eq:f_bubble})). For the given bubble volume, only part of the
-hairs are inside the bubble for the hydrophilic substrate, while,
-all the hairs are inside the bubble for the hydrophobic substrate.
+hairs make contact with the surface inside the bubble for the hydrophilic case, while,
+all the hairs contact the surface inside the bubble for the hydrophobic case.
 Therefore, the force curve lies between \emph{in air} and \emph{underwater:
@@
 bubble's volume is kept constant, it will then have a lesser space
-available to occupy between the pad and the substrate, This results
+available to occupy between the pad and the substrate. This results
 in it bulging outwards near the pinned contact line on the top, causing
@@
 single seta adhesion force tests similar to \citet{RN202}
-using a hydrophilic and fluorinated probe in air and underwater conditions
-to validate the role of capillary contributions to gecko adhesion.
+using a hydrophilic and fluorinated probe in air and underwater conditions. 
+If the fluorinated probe shows higher adhesion underwater than in air on a single seta, this
+would confirm the role of capillary contributions due to an oil-like phospholipid layer to gecko adhesion.
 

### 2021-05-07 source/tex/ladybug_adhesion.tex
referee 1 further comments included to MS

@@
 
-The goal of this paper is to provide a generalised picture of adhesion in insects which use hairy pads and secrete an oily fluid for attachment.
+The goal of this paper is to provide a generalised picture of underwater adhesion in insects which use hairy pads and secrete an oily fluid for attachment.
 We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces.
-We further tested whether the chemical profile of the adhesive fluid changes when the hairs were submerged in water.
+Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \cite{RN145}.
 Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions.
@@
 
-The seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
-were purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
+The seven-spotted adult male adult ladybug beetles (\emph{Coccinella septempuctata})
+were purchased from Katz Biotech (Baruth, Germany). The beetles were housed in a plastic box filled with leaves,
 twigs and stones at room temperature and 60-80\% relative humidity
 with daily access to sunlight. They were fed with raisins, honey and
-water \emph{ad libitum}.
+water \emph{ad libitum}. The beetles on average weighed 34 $\pm$ 4 mg and were experimented on within three weeks of being housed under above conditions.
 
@@
 The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments.
-One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.) allowing us to further align the leg to the substrate.
+One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate.
+Each leg of a male ladybug beetle has two hairy adhesive pads.
+For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one.
+The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack.
 The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate.
-Care was taken to ensure the glue doesn't contaminate the pads.
-Each leg of a male ladybug beetle has two pads.
-For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one.
+Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres.
 A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test.
@@
 displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
-with a steel bending beam (spring constant = 68.1 N/m) constitutes
+with a steel bending beam (spring constant = 68.1 Nm\protect\textsuperscript{-1}) constituted
 the vertical force sensor. Beam deflection was calibrated using 4
-different known weights to get the corresponding force. A plastic
-3D printed substrate holder was glued to the end of the bending beam.
+different known weights to get the corresponding force. A
+3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
 The holder was designed to enable switching from one substrate to
@@
 as well as observe the contact. The force sensor was mounted on a stage
-consisting of a X-piezo element, used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
+consisting of a X-piezo element (\emph{Physik Instrumente, Germany}), used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
 was used for vertical up-down motion, bringing the insect in contact
-with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors.
+with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors (\emph{OWIS GmbH, Germany}).
 A coaxial illuminated tube microscope
-(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
-with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 px; \emph{Basler ace U}, 1280 x 1024 px)
+(\emph{Navitar, USA}) with 2$\times$ objective and a stereo-microscope
+with 1$\times$ objective (\emph{Wild Heerbrugg, Switzerland}) fit with digital video cameras 
+(\emph{Blackfly S, FLIR, USA}, 2448 $\times$ 2048 px; \emph{Basler ace U, Germany}, 1280 $\times$ 1024 px)
 were used to record the sample contact with the substrate from ventral
@@
 the appropriate piezo motion steps were synchronised using a custom
-LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
+LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
 averaged to 512 points per motion step. Videos were recorded at 20
@@
 
-The vertical and lateral piezos were used together to perform approach-retract
+The vertical and lateral piezos were used simultaneously to perform approach-retract
 adhesion tests with the substrate to get the pull-off force. However,
-instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
+instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
+was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
 A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
@@
 substrate. All approach, retract and lateral slide motion was done
-at a speed of 62.5 \textmu m/s. Ventral view video recordings
+at a speed of 62.5 \textmu ms\protect\textsuperscript{-1}. Ventral view video recordings
 were used for contact area extraction while the side view imaging
@@
 For underwater experiments, 1 ml Milli-Q water was pipetted into the
-substrate holder. In order to achieve an underwater contact without
-a trapped air bubble, the water was first degassed in a vacuum chamber
-at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
-the pad was brought into contact with the dry surface 10 times repeatedly 
-to equilibrate the pad's secretion system.
+substrate holder (roughly 3 mm water level). The beetle was then partially 
+submerged to allow underwater contact of the pad with the substrate. In order to achieve contact without
+a trapped air bubble, the water was first degassed separately in a vacuum chamber
+at 10 mbar pressure for 3 hours and then pipetted into the holder immediately. Before the experiments,
+the pad was brought into contact with the clean dry surface 10 times repeatedly 
+to ensure the hairs are free of any contaminating particles.
 
 Five force measurements were subsequently performed on a fresh spot of the substrate and averaged for data analysis. 
-Experiments were repeated with five individual beetles for each type of contact and substrate.
-In total, 30 beetles were tested.
+Experiments were repeated five times with unique male beetles for each mode of contact (``\emph{in air}'', (``\emph{underwater:
+bubble}'' and (``\emph{underwater: no bubble}'') and substrate (hydrophilic, hydrophobic). Thus, in total, 30 beetles were tested.
+%CHECK TYPE OF CONTACT CHANGE TO MODE OF CONTACT%
 
@@
 For measurements in air, the pull-off force was defined as the minimum
-negative force during the final retraction step (Figure \ref{fig:Setup}).
+negative force during the retraction step (Figure \ref{fig:Setup}).
 For underwater measurements, an additional correction was necessary.
@@
 substrate. Glass was wiped with isopropanol, rinsed in water and dried
-under nitrogen flow. The surface was then plasma cleaned in a oxygen
-plasma chamber (Diener Electronic Femto) for 10 min at 120 W. The
-surface was further rinsed with water and dried under nitrogen flow.
-
-For the hydrophobic substrate, the glass cover slip was coated with
+under nitrogen flow. For the hydrophobic substrate, the glass cover slip was coated with
 a fluorosilane via chemical vapour deposition (CVD). First, the glass
-was cleaned using IPA and plasma treated as before. Next, 0.2 ml of
+was cleaned using IPA. The surface was then plasma cleaned in a oxygen
+plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
 Trichloro(1H,1H,2H,2H-perfluorooctyl) silane (PFOTS), procured from
@@
 the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
-for 3 hours.
+for 3 hours. Henceforth, we refer to the hydrophilic normal glass substrate 
+as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.
 
-The substrate wetting was characterised by dynamic contact angle
-measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
-Milli-Q water and n-hexadecane were used as test liquids. Advancing
+The surface chemistry was characterised by dynamic contact angle
+measurements, performed with a contact angle goniometer (\emph{OCA 35, DataPhysics Instruments GmbH, Germany})
+The substrate's wetting towards a polar (Milli-Q water) and a non-polar (n-hexadecane) liquid was tested. Advancing
 and receding contact angles were measured for a maximum drop volume
-of 10 \textmu l and with 0.5 \textmu l/s flow rate.
+of 10 \textmu l and with 0.5 \textmu ls\protect\textsuperscript{-1} flow rate (Table \ref{tab:Contact-Angles}).
 
@@
 \hline 
-\end{tabular}\caption{Dynamic contact angles measurements \label{tab:Contact-Angles}}
+\end{tabular}\caption{Dynamic contact angles (Mean \ensuremath{\pm} SD, n = 3) of Milli-Q water and n-hexadecane on the different test substrates. \label{tab:Contact-Angles}}
 \end{table}
 
-\subsubsection{Field desorption mass spectroscopy}
-
-A previous study on arachnids \cite{RN223} reported that its secreted
-fluid does not dissolve in water. To test whether the beetles retain
-their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
-(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
-were done on the extracted secretions before and after rinsing its
-legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
-axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
-to the measurement chamber of the FDMS. As a reference, pure THF was
-used. The second middle leg of the same ladybird was subsequently
-immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
-20 min and then transferred to the measurement chamber of the spectrometer.
-Molecular composition was extracted from the peak positions of the
-FDMS spectra.
+%\subsubsection{Field desorption mass spectroscopy}
+%
+%A previous study on arachnids \cite{RN223} reported that its secreted
+%fluid does not dissolve in water. To test whether the beetles retain
+%their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
+%(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
+%were done on the extracted secretions before and after rinsing its
+%legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
+%axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
+%to the measurement chamber of the FDMS. As a reference, pure THF was
+%used. The second middle leg of the same ladybird was subsequently
+%immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
+%20 min and then transferred to the measurement chamber of the spectrometer.
+%Molecular composition was extracted from the peak positions of the
+%FDMS spectra.
 
@@
 
-\subsubsection{Adhesion measurements}
+%\subsubsection{Adhesion measurements}
 
@@
 \begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing single
-leg adhesion force measurements of ladybug beetle (\emph{Coccinella
-septempuctata}) on glass and PFOTS substrates in air and underwater
+\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
+ adhesion force measurements of ladybug beetle's (\emph{Coccinella
+septempuctata}) distal pad on glass (blue) and PFOTS (red) substrates in air and underwater
 conditions. The two modes of contact during underwater experiments
@@
 and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
-represent theoretical predictions of adhesion force, while, circles
+represent theoretical predictions (see text) of adhesion force, while, circles
 represent the contribution of the bubble itself, calculated from the
 capillary bridge model. In the model, hair diameter = 4 \textmu m,
-pad diameter = 200 \textmu m, hair height = 40 \textmu m,
+pad diameter = 200 \textmu m, hair length = 40 \textmu m,
 N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
 = 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
-tension of the adhesive fluid in air and water were assumed to be
-24 mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
+tension of the tarsal adhesive fluid in air and water were assumed to be
+24 mNm\protect\textsuperscript{-1} and 48 mNm\protect\textsuperscript{-1} respectively and water surface tension is 72 mNm\protect\textsuperscript{-1}.}
 \end{figure}
 
-Apart from the three depicted contact types, we observed an additional
+Apart from the three depicted contact modes, we observed an additional
 fourth type which occurred in roughly 25\% of our underwater experiments.
-In this scenario, the ventral view recordings show that the hairs
-did not appear to contact well with the substrate, unlike the other
-three contact types. This ``bad contact'' scenario shows no adhesion
+In this scenario, the ventral view recordings show that none of the hairs
+appear to contact well with either glass or PFOTS substrate, unlike the other
+three contact modes (see supplementary info). This ``bad contact'' scenario shows no adhesion %INCLUDE SUPPLEMENTARY%
 with either glass or PFOTS substrate. While it was not completely
@@
 
-\subsubsection{Field desorption mass spectroscopy}
-
-FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
-leg when underwater (Table \ref{tab:Molecular-distribution-of}).
-Molecular weights of the secreted fluid mixtures extracted from the
-beetle's leg, without and after immersion in water, show that, except
-for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
-fingerprint remained unchanged. This indicates that the adhesion fluid
-was not washed away underwater. Probable compounds in the fluid, corresponding
-to the resultant molecular weights, include mostly aliphatic hydrocarbons
-with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
-to assert that, even for the case of \emph{Coccinella
-septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments.
-
-\begin{table}[H]
-\centering{}%
-\begin{tabular}{|c|c|c|}
-\hline 
-Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
-\hline 
-\hline 
-324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
-\hline 
- & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
-\hline 
-350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
-\hline 
-352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
-\hline 
-378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
-\hline 
-404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
-\hline 
-406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
-\hline 
-432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
-\hline 
-\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
-with and without rinsing the beetle's leg in water. \label{tab:Molecular-distribution-of}}
-\end{table}
+%\subsubsection{Field desorption mass spectroscopy}
+%
+%FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
+%leg when underwater (Table \ref{tab:Molecular-distribution-of}).
+%Molecular weights of the secreted fluid mixtures extracted from the
+%beetle's leg, without and after immersion in water, show that, except
+%for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
+%fingerprint remained unchanged. This indicates that the adhesion fluid
+%was not washed away underwater. Probable compounds in the fluid, corresponding
+%to the resultant molecular weights, include mostly aliphatic hydrocarbons
+%with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
+%to assert that, even for the case of \emph{Coccinella
+%septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments. 
+%
+%\begin{table}[H]
+%\centering{}%
+%\begin{tabular}{|c|c|c|}
+%\hline 
+%Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
+%\hline 
+%\hline 
+%324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
+%\hline 
+% & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
+%\hline 
+%350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
+%\hline 
+%352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
+%\hline 
+%378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
+%\hline 
+%404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
+%\hline 
+%406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
+%\hline 
+%432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
+%\hline 
+%\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
+%with and without rinsing the beetle's leg in water. \label{tab:Molecular-distribution-of}}
+%\end{table}
 
@@
 \includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
-with the substrate in three ways: a) \emph{In air}, where the adhesive
+with the substrate (hydrophilic or hydrophobic) in three ways: a) \emph{In air}, where the tarsal adhesive
 fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
-where the adhesive fluid bridges are fully surrounded by water; c)\emph{
-Underwater: bubble}, where part of the adhesive fluid bridges are
-inside the bubble while others are outside in water. The corresponding
+where the tarsal adhesive fluid bridges are fully surrounded by water; c)\emph{
+Underwater: bubble}, where part of the tarsal adhesive fluid bridges are
+inside the bubble while others are outside in water (see text for details). The corresponding
 ventral view contact images of the beetle's pad are shown on the right.}
@@
 that the adhesive fluid can form capillary bridges with the substrate
-in water, instead of getting washed away (Table \ref{tab:Molecular-distribution-of}).
+in water, instead of getting washed away (Table \ref{tab:Molecular-distribution-of}). %CHANGE REFERENCE!%
 

### 2021-05-08 source/tex/ladybug_adhesion.tex

@@
 
-Many insects can climb smooth surfaces using hairy adhesive pads on their legs.
+Many insects can climb smooth surfaces using hairy adhesive pads on their legs mediated by tarsal fluid secretions.
 It was previously shown that a terrestrial beetle can even adhere and walk underwater.
@@
 We modelled the adhesion of a hairy pad using capillary forces.
-Coherent with our experiments, the model demonstrates that the wetting properties of the tarsal adhesive fluid secretion alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion.
+Coherent with our experiments, the model demonstrates that the wetting properties of the tarsal fluid alone can determine the ladybugs'  adhesion to smooth surfaces in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion.
+The study highlights how such a mediating fluid can serve as a potential strategy to achieve underwater adhesion via capillary forces, which could inspire artificial adhesives for underwater applications.
 \end{abstract}
@@
 Insect tarsal hairs secrete an adhesion-mediating fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion'').
-In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.
+In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN201,RN155,RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.
 
@@
 This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
-Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact.
+Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact.
 It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater.
 However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force.
-The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hairs when submerged.
-In ladybug beetles, the tip of each seta secretes approximately one femtoliter of adhesive fluid by each step \cite{RN108}.
+The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged.
+In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \cite{RN108}.
 The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
@@
 
-The goal of this paper is to provide a generalised picture of underwater adhesion in insects which use hairy pads and secrete an oily fluid for attachment.
+The goal of this paper is to clarify the current understanding of underwater adhesion seen in terrestrial insects which use hairy pads and secrete an oily fluid for attachment.
 We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces.
-Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \cite{RN145}.
+Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \cite{RN145} and they can also walk underwater.
 Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions.
 The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion.
-Finally, we
-discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.
+Finally, we discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.
+We hope our study to provide new strategies to design bio-inspired materials that show good adhesive properties in both air and underwater conditions, similar to what has been previously reported for terrestrial beetles \cite{RN87}.
 
@@
 Normal adhesion force measurements on a restrained leg in a live
-beetle were performed. We characterised adhesion by the pull-off force
+beetle were performed.
+We focus our study only on a single tarsal adhesive pad of the leg by carefully fixing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion.
+We characterised adhesion by the pull-off force
 during detachment, tested on smooth normal and
@@
 The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack.
-The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate.
+The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset).
 Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres.
@@
 displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
-with a steel bending beam (spring constant = 68.1 Nm\protect\textsuperscript{-1}) constituted
+with a steel bending beam (spring constant = 68.1 N m\protect\textsuperscript{-1}) constituted
 the vertical force sensor. Beam deflection was calibrated using 4
@@
 substrate. All approach, retract and lateral slide motion was done
-at a speed of 62.5 \textmu ms\protect\textsuperscript{-1}. Ventral view video recordings
+at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
 were used for contact area extraction while the side view imaging
@@
 
-Five force measurements were subsequently performed on a fresh spot of the substrate and averaged for data analysis. 
-Experiments were repeated five times with unique male beetles for each mode of contact (``\emph{in air}'', (``\emph{underwater:
-bubble}'' and (``\emph{underwater: no bubble}'') and substrate (hydrophilic, hydrophobic). Thus, in total, 30 beetles were tested.
-%CHECK TYPE OF CONTACT CHANGE TO MODE OF CONTACT%
+Five force measurements were subsequently performed, each on a fresh spot of the substrate, and averaged for data analysis. 
+Experiments were repeated with five distinct male beetles for each combination of contact mode (``\emph{in air}'', (``\emph{underwater:
+bubble}'' and (``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic).
+Thus, in total, 30 distinct beetles were tested.
+After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.
 
@@
 \par\end{centering}
-\caption{\label{fig:Setup} Adhesion test setup (for explanation see text). The recorded force data and
-contact area of a distal pad are shown in the plot, in which, the shaded
+\caption{\label{fig:Setup} Adhesion test setup (see text for details).
+Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange).
+The recorded force data and
+contact area of a distal pad are shown in the bottom-right plot, in which, the shaded
 regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
 represent attraction and the minimum force peak during the final retraction
-step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material.}
+step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material (S2-S4).}
 \end{figure}
@@
 For measurements in air, the pull-off force was defined as the minimum
-negative force during the retraction step (Figure \ref{fig:Setup}).
+negative force during the retraction step (bottom-right plot in Figure \ref{fig:Setup}).
 For underwater measurements, an additional correction was necessary.
@@
 substrate. Glass was wiped with isopropanol, rinsed in water and dried
-under nitrogen flow. For the hydrophobic substrate, the glass cover slip was coated with
+under nitrogen flow before use. For the hydrophobic substrate, the glass cover slip was coated with
 a fluorosilane via chemical vapour deposition (CVD). First, the glass
-was cleaned using IPA. The surface was then plasma cleaned in a oxygen
+was cleaned using IPA. The surface was then plasma cleaned in an oxygen
 plasma chamber (\emph{Femto, Diener Electronic GmbH, Germany}) for 10 min at 120 W. Next, 0.2 ml of
@@
 and receding contact angles were measured for a maximum drop volume
-of 10 \textmu l and with 0.5 \textmu ls\protect\textsuperscript{-1} flow rate (Table \ref{tab:Contact-Angles}).
+of 10 \textmu l and with 0.5 \textmu l s\protect\textsuperscript{-1} flow rate (Table \ref{tab:Contact-Angles}).
 
@@
 
-%\subsubsection{Field desorption mass spectroscopy}
-%
-%A previous study on arachnids \cite{RN223} reported that its secreted
-%fluid does not dissolve in water. To test whether the beetles retain
-%their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
-%(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
-%were done on the extracted secretions before and after rinsing its
-%legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
-%axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
-%to the measurement chamber of the FDMS. As a reference, pure THF was
-%used. The second middle leg of the same ladybird was subsequently
-%immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
-%20 min and then transferred to the measurement chamber of the spectrometer.
-%Molecular composition was extracted from the peak positions of the
-%FDMS spectra.
-
 \subsection{Results}
@@
  adhesion force measurements of ladybug beetle's (\emph{Coccinella
-septempuctata}) distal pad on glass (blue) and PFOTS (red) substrates in air and underwater
-conditions. The two modes of contact during underwater experiments
+septempuctata}) distal pad on normal hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
+conditions (n=30). The two modes of contact during underwater experiments
 are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
@@
 tension of the tarsal adhesive fluid in air and water were assumed to be
-24 mNm\protect\textsuperscript{-1} and 48 mNm\protect\textsuperscript{-1} respectively and water surface tension is 72 mNm\protect\textsuperscript{-1}.}
+24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
 \end{figure}
@@
 Apart from the three depicted contact modes, we observed an additional
-fourth type which occurred in roughly 25\% of our underwater experiments.
+fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
 In this scenario, the ventral view recordings show that none of the hairs
-appear to contact well with either glass or PFOTS substrate, unlike the other
-three contact modes (see supplementary info). This ``bad contact'' scenario shows no adhesion %INCLUDE SUPPLEMENTARY%
+appear to contact well with either glass or PFOTS substrate (supplementary video S5), unlike the other
+three contact modes (supplementary video S2-S4). This ``bad contact'' scenario only happened underwater and shows no adhesion 
 with either glass or PFOTS substrate. While it was not completely
@@
 
-%\subsubsection{Field desorption mass spectroscopy}
-%
-%FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
-%leg when underwater (Table \ref{tab:Molecular-distribution-of}).
-%Molecular weights of the secreted fluid mixtures extracted from the
-%beetle's leg, without and after immersion in water, show that, except
-%for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
-%fingerprint remained unchanged. This indicates that the adhesion fluid
-%was not washed away underwater. Probable compounds in the fluid, corresponding
-%to the resultant molecular weights, include mostly aliphatic hydrocarbons
-%with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
-%to assert that, even for the case of \emph{Coccinella
-%septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments. 
-%
-%\begin{table}[H]
-%\centering{}%
-%\begin{tabular}{|c|c|c|}
-%\hline 
-%Without rinsing (g/mol) & After rinsing (g/mol) & Probable compounds\tabularnewline
-%\hline 
-%\hline 
-%324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
-%\hline 
-% & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
-%\hline 
-%350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
-%\hline 
-%352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
-%\hline 
-%378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
-%\hline 
-%404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
-%\hline 
-%406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
-%\hline 
-%432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
-%\hline 
-%\end{tabular}\caption{Molecular weights of adhesive fluid secretion of \emph{Harmonia axyridis}
-%with and without rinsing the beetle's leg in water. \label{tab:Molecular-distribution-of}}
-%\end{table}
-
 \section{Theory}
@@
 \begin{figure}[H]
-\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
-with the substrate (hydrophilic or hydrophobic) in three ways: a) \emph{In air}, where the tarsal adhesive
+\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}
+\caption{\label{fig:Model}The capillary bridge model of a hairy adhesive pad. The hairs make contact
+with the substrate (hydrophilic or hydrophobic) in three modes: a) \emph{In air}, where the tarsal adhesive
 fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
-where the tarsal adhesive fluid bridges are fully surrounded by water; c)\emph{
-Underwater: bubble}, where part of the tarsal adhesive fluid bridges are
+where the fluid bridges are fully surrounded by water; c)\emph{
+Underwater: bubble}, where part of the fluid bridges are
 inside the bubble while others are outside in water (see text for details). The corresponding
-ventral view contact images of the beetle's pad are shown on the right.}
+ventral view contact images of the beetle's pad seen during adhesion experiments are shown on the right.}
 \end{figure}
@@
 $D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad were assumed
-to be perfectly rigid, for simplicity. The tip of each hair has an
-adhesive fluid of volume, $V_{f}$, making contact with the substrate.
+to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
+adhesive fluid of volume, $V_{f}$, mediating contact with the substrate.
 The fluid is pinned to the circumference of the hair and forms a capillary
 bridge of height, $d$. Similar to our experiments, we considered three
-types of contacts for the pad: 1) \emph{In air}, 2) \emph{Underwater:
+modes of contact for the pad: 1) \emph{In air}, 2) \emph{Underwater:
 no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
@@
 
-To characterise the adhesive fluid and bubble volume, we defined two
+To characterise the tarsal adhesive fluid and bubble volume, we defined two
 radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
@@
 radii were assumed to scale proportional to their corresponding pinned
-contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$
-and $\phi_{b}=D_{p}/\left(2s_{b}\right)$ for the fluid and bubble
+contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/(2s_{f})$
+and $\phi_{b}=D_{p}/(2s_{b})$ for the fluid and bubble
 respectively, to conveniently scale their volumes relative to the
@@
 Evolver simulations\cite{RN206}  (described in supplementary section S1.1),
-and used to obtain $F_{net}$ as a function of $d$ for each type
+and used to obtain $F_{net}$ as a function of $d$ for each mode
 of contact. The adhesion force of the complete hairy pad system was
@@
 We considered $f_{air}$ and $f_{water}$ to be distinct terms
-because the capillary force by the adhesive fluid would be different
+because the capillary force by the tarsal adhesive fluid would be different
 in air and underwater due to its different contact angle and interfacial
@@
 for each case of fluid-air, fluid-water and water-air interface, one
-can derive the following relation for the contact angle of the adhesive
+can derive the following relation for the contact angle of the tarsal adhesive
 fluid underwater:
@@
 Here, $\theta_{fw}$ and $\theta_{fa}$ are the contact angles of
-the adhesive fluid with the substrate in water and air respectively,
+the tarsal adhesive fluid with the substrate in water and air respectively,
 $\theta_{wa}$ is the contact angle of water with the substrate in
-air, $\gamma_{fa}$ is the surface tension of the adhesive fluid,
+air, $\gamma_{fa}$ is the surface tension of the tarsal adhesive fluid,
 $\gamma_{wa}$ is the surface tension of water and $\gamma_{fw}$
-is the interfacial tension of the adhesive fluid with water.
+is the interfacial tension of the tarsal adhesive fluid with water.
 
-All lengths were normalised w.r.t. $s_{f}$ and forces were normalized
+All lengths ($D_{h}$, $D_{p}$, $L$, $d$) were normalised w.r.t. $s_{f}$ and forces were normalized
 w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values were fixed relative
@@
 all model calculations (Table \ref{tab:Model-parameters}). Here,
-we assumed the adhesive fluid to be an oil-lke substance and thus the
+we assumed the tarsal adhesive fluid to be an oil-like substance and thus the
 interfacial tension ratios $\gamma_{wa}/\gamma_{fa}$ and $\gamma_{fw}/\gamma_{fa}$
-were taken corresponding to typical values for oil and water. We considered
+were assumed to correspond to typical values for oil and water. We considered
 representative hydrophilic and hydrophobic substrates with $\theta_{fa}$
 and $\theta_{wa}$ values corresponding to a typical glass and fluorinated
-surface, respectively. Area fraction of the hairs relative to the
+surface, respectively. The contact area fraction of the hairs relative to the
 pad, $\alpha=ND_{h}^{2}/D_{p}^{2}$, hair aspect ratio, $L/D_{h}$,
@@
 capillary bridge. Second, the effect of substrate on the force-distance
-curves of the hairy pad system was compared for each type of contact.
+curves of the hairy pad system was compared for each mode of contact.
 Third, we looked at the effect of changing the bubble
@@
 \hline 
-Area fraction, $\alpha$ & 0.1\tabularnewline
+Contact area fraction, $\alpha$ & 0.1\tabularnewline
 \hline 
@@
 \hline 
-Fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\tabularnewline
+Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\tabularnewline
 \hline 
-Fluid size parameter, $\phi_{f}$ & 2\tabularnewline
+Tarsal fluid size parameter, $\phi_{f}$ & 2\tabularnewline
 \hline 
@@
 \hline 
-\end{tabular}\caption{\label{tab:Model-parameters}Fixed parameters of the capillary bridge
-model}
+\end{tabular}\caption{\label{tab:Model-parameters}Fixed parameter values corresponding to the pad's geometry, 
+tarsal fluid and substrate wetting properties used in the capillary bridge model}
 \end{table}
 
-\subsection{Capillary force of a pinned liquid bridge\label{subsec:Capillary-force-of}}
+\subsection{Capillary force of a single liquid bridge\label{subsec:Capillary-force-of}}
 
@@
 the strength of its adhesion force. High adhesion is seen for contact
-angles less than $\sim$ 70\textdegree{} due to a net negative curvature
+angles less than $\sim$ 70\textdegree{} due to a net negative (convex) curvature
 of the meniscus, while low adhesion is seen for contact angles greater
@@
 low volume of the liquid and its pinned contact line prevents the
-meniscus from having a high positive curvature due to geometric constraints.
+meniscus from having a high positive (concave) curvature due to geometric constraints.
 Only for a contact angle of 150\textdegree , the liquid's curvature
@@
 \subcaption{Force contributions}%
-\end{minipage}\caption{\label{fig:Single-bridge}Normalised capillary force of a single liquid
+\end{minipage}\caption{\label{fig:Single-bridge}Simulation of normalised capillary force of a single liquid
 bridge in contact with a substrate and pinned to a circular perimeter
@@
 
-The force-distance curves show a general trend of being repulsive
+The force-distance curves show a general trend of repulsive forces
 at small distances (Figure \ref{fig:Single-bridge}a). This is a result
@@
 
-\subsection{Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}
+\subsection{Adhesion of a hairy pad: Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}
 
@@
 and hydrophobic substrate are predicted based on the capillary bridge
-model and compared for the different contact types (Figure \ref{fig:Effect-of-substrate}).
+model and compared for the different contact modes (Figure \ref{fig:Effect-of-substrate}).
 The forces in each case are calculated from equations (\ref{eq:f_air/water})
@@
 \centering{}\includegraphics{Figure5-Model_effect_of_substrate}\caption{\label{fig:Effect-of-substrate}Theoretical force-distance curves
-of a hairy pad system on a hydrophilic and hydrophobic substrate in
+of a hairy pad on a hydrophilic and hydrophobic substrate in
 air and underwater conditions. A negative force value represents attraction.
@@
 
-The observed trend in forces can be explained by how the adhesive
+The observed trend in forces can be explained by how the tarsal adhesive
 fluid wets the surface in each case. On a hydrophilic substrate, the
-contact angle of the oily adhesive fluid is 6\textdegree , when surrounded
+contact angle of the oily fluid is 6\textdegree , when surrounded
 by air (Table \ref{tab:Model-parameters}) and 150\textdegree , when
@@
 \includegraphics{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
-meniscus in contact with glass and PFOTS in air and underwater conditions.
+meniscus in contact with normal glass and PFOTS-coated glass in air and underwater conditions.
 The corresponding interfacial tension, \textgreek{g}, and contact
@@
 
-\subsection{Effect of bubble volume}
+\subsection{Adhesion of a hairy pad: Effect of the air bubble volume}
 
@@
 \includegraphics{Figure7-Model_effect_of_bubble_volume}\caption{\label{fig:Effect-of-bubble}Normalised adhesion force of a hairy
-pad system as a function of bubble volume, $\hat{V}_{b}$, for the
-\emph{underwater: bubble} contact type. Adhesion forces are calculated
+pad as a function of bubble volume, $\hat{V}_{b}$, for the
+\emph{underwater: bubble} contact mode. Adhesion forces are calculated
 from the minima of the respective force-distance curves. Negative
@@
 
-The volume of the bubble can influence its capillary force contribution,
+The volume of the trapped air bubble can influence its capillary force contribution,
 as well as change the relative proportion of hairs inside and outside
@@
 curvature of their meniscus. Thus, decreasing $\hat{V}_{b}$ decreases
-the adhesion force due to a larger proportion of hairs being outside
+the adhesion force due to a larger proportion of tarsal hairs being outside
 the bubble. In contrast, on the hydrophobic substrate, fluid bridges
@@
 
-\subsection{Effect of hair diameter }
+\subsection{Adhesion of a hairy pad: Effect of the hair tip diameter}
 
 \begin{figure}[H]
-\includegraphics[scale=0.5]{Figure6-Model_effect_of_hair_size}\caption{\label{fig:Effect-of-hair}Normalised adhesion force of a hairy pad
-system on a hydrophilic and hydrophobic substrate as a function of
-hair diameter, $D_{h}$. Volume of each fluid bridge, $V_{f}$, scales
+\includegraphics[scale=0.5]{Figure6-Model_effect_of_hair_size}
+\caption{\label{fig:Effect-of-hair}Normalised adhesion force of a hairy pad on a hydrophilic and hydrophobic substrate as a function of
+hair tip diameter, $D_{h}$. Volume of each fluid bridge, $V_{f}$, scales
 relative to $D_{h}$ based on the parameter $\phi_{f}=2$. Adhesion
@@
 curves, based on the capillary bridge model. A negative value represents
-attraction. The bubble's contribution to the net force for an \emph{underwater:
+attraction. The air bubble's contribution to the net force for an \emph{underwater:
 bubble} contact is denoted by plus symbols. Pad diameter and bubble
@@
 \end{figure}
-Hairs on a ladybug's pad terminate in various shapes like ``discoidal''
+The tarsal hairs on a ladybug's adhesive pad terminate in various shapes, such as ``discoidal''
 or ``pointed''. We studied this geometric effect on adhesion by
-changing the hair diameter, $D_{h}$ (Figure \ref{fig:Effect-of-hair}).
+changing the hair tip diameter, $D_{h}$ (Figure \ref{fig:Effect-of-hair}).
 Here, the pad diameter, total hair contact area and bubble volume
 are constant since $D_{p}$, $\alpha$ and $\hat{V}_{b}$ are kept
-fixed. The adhesive fluid volume is again assumed to scale relative
+fixed. The tarsal adhesive fluid volume is again assumed to scale relative
 to the hair diameter ($\phi_{f}=2$).
@@
 Adhesion force increases with decreasing $D_{h}$ for both hydrophilic
-and hydrophobic substrates in all contact types. This is consistent
+and hydrophobic substrates in all contact modes. This is consistent
 with the ``contact splitting'' theory, which predicts higher adhesion
@@
 bubble} contact shows intermediate adhesion between \emph{in air}
-and \emph{underwater: no bubble} contact types.
+and \emph{underwater: no bubble} contact modes.
 
@@
 to a hydrophobic substrate even without a bubble trapped around its
-hairs. A previous study\cite{RN87} proposed that a bubble
-is necessary for underwater attachment in beetles. This is, however,
-only true for hydrophilic substrates, where a trapped bubble can facilitate
+tarsal hairs. A previous study\cite{RN87} proposed that an air bubble
+is necessary for underwater attachment in terrestrial beetles. This is, however,
+only true for hydrophilic substrates, where a trapped air bubble can facilitate
 underwater adhesion due to the hairs making contact in a de-wetted
@@
 agree with our experimental results (Figure \ref{fig:Effect-of-contact}).
-In underwater conditions without a trapped bubble, adhesion to a hydrophobic
+In underwater conditions without a trapped air bubble, adhesion to a hydrophobic
 substrate is significantly larger than to a hydrophilic substrate.
-This is explained by the different interfacial tension of the oil and contact
+This is explained by the different interfacial tension of the oily tarsal secretion and its contact
 angles with the substrates in air and underwater, which determines
@@
 increase in underwater adhesion relative to that in air on the hydrophobic
-PFOTS surface. This discrepancy could be due to our assumptions of
+PFOTS-coated surface. This discrepancy could be due to our assumptions of
 the oily fluid's interfacial properties. If we choose $\gamma_{fa}$=30
-mN/m and $\gamma_{fw}$=40 mN/m, the corresponding increase in adhesion
+mN m\protect\textsuperscript{-1} and $\gamma_{fw}$=40 mN m\protect\textsuperscript{-1}, the corresponding increase in adhesion
 will be $\sim$ 1.7, closer to our experimental value of $\sim$ 1.
@@
 not all the hairs might be able to completely drain the interfacial
-water layer, in order for the adhesive fluid to make a direct contact
+water layer, in order for the tarsal adhesive fluid to make a direct contact
 with the substrate. This can further reduce underwater adhesion, in
 comparison to our theoretical predictions which assumes a perfect
-contact.
+contact of all hairs' terminals.
 
@@
 give a theoretical maximum achievable adhesion force. In our experiments,
-however, not all hairs make a perfect contact with the substrate despite our best efforts to align the pad with surface.
-Furthermore, during detachment, the pad typically peels off from its proximal to distal end rather
+however, not all hairs make a perfect contact with the substrate despite our 
+best efforts to align the pad parallel to the surface. Furthermore, during detachment, 
+the constrained pad typically peels off from its proximal to distal end rather
 than detach simultaneously. Our model also assumes the hairs to be
-of similar geometry, unlike the beetle's pad which has a distribution
+of similar geometry, unlike the male beetle's pad which has a distribution
 of flat or pointed tipped hairs. Thus, it's not surprising that the
@@
 
-Our study provides further validation that capillary forces govern insect adhesion and van der Waals contribution,
+Our study provides further validation that capillary forces govern the ladybug's adhesion and van der Waals contribution,
 if any, must be negligible. Further, the capillary forces can even
-enable insect attachment underwater depending on the substrate chemistry.
+enable ladybug attachment underwater depending on the substrate chemistry.
 When underwater, without a trapped bubble, the pads adhere strongly
@@
 even though it shows similarly strong adhesion to both substrates
-in air. This behaviour can only be explained by capillary forces and the wetting properties of the fluid. Our
-preliminary FDMS results further provides validation to our assumption
-that the adhesive fluid can form capillary bridges with the substrate
-in water, instead of getting washed away (Table \ref{tab:Molecular-distribution-of}). %CHANGE REFERENCE!%
+in air. This effect can be explained by capillary forces and the wetting properties of the fluid. Our
+preliminary chemical composition analysis of a beetle's tarsal secretions before and after immersing its leg underwater 
+validates our assumption that the tarsal adhesive fluid should form capillary bridges with the substrate
+underwater, instead of getting washed away (see supplementary info Section S1.5).
 
-The findings can also be extended to other animals relying on oily
-secretions for adhesion. Some ants, for example, show similar adhesion
-on hydrophobic substrates under wet and dry conditions \cite{RN213},
-similar to what we see in a ladybug. Recent experiments on
-geckos revealed that they can attach well to fluoropolymer substrates
+To some extent, the findings could be extended to other animals relying on oily
+secretions for adhesion. For example, ants are known to possess smooth adhesive pads which secrete a fluid containing oily substances \cite{RN201}.
+It has been reported that some ants show similar adhesion on hydrophobic substrates under wet and dry conditions \cite{RN213},
+similar to what we see in a ladybug. This observation can again be explained by a capillary model as before. Recent experiments on
+geckos revealed that they can attach well to fluoropolymer substrates (such as PTFE)
 underwater while they show little adhesion to the same substrate in
@@
 geckos \cite{RN205} could change that picture. Since geckos adhere
-poorly to PTFE (surface energy $\sim$ 20 mN/m) one can
+poorly to PTFE (surface energy $\sim$ 20 mN m\protect\textsuperscript{-1}) one can
 speculate that the phospholipid material has a higher surface energy,
@@
 us assume the phosopholipid substance to be a fluid similar to oil 
-with $\gamma_{fa}$= 30 mN/m and $\gamma_{fw}$= 42 mN/m such that
+with $\gamma_{fa}$= 30 mN m\protect\textsuperscript{-1} and $\gamma_{fw}$= 42 mN m\protect\textsuperscript{-1} such that
 its contact angle with PTFE is 80\textdegree . Equation \ref{eq:theta_fw}
@@
 that the underwater experiments performed on geckos \cite{RN199,RN15}
-indicate a capillary contribution to gecko adhesion. We suggest performing
-single seta adhesion force tests similar to \citet{RN202}
+indicate a capillary contribution to gecko adhesion. Previous studies on gecko adhesion have attributed capillary effects to be a result of
+water condensation from ambient humid air onto the setal hair tips \cite{RN197, RN203, RN218}.
+We however emphasize that capillary contribution in gecko adhesion could rather be a result of its setal phospholipid layer rather than water. %SURFACE TENSION SOURCE%
+The previously reported influence of humidity on gecko adhesion \cite{RN197} could possibly be an effect of change in surface tension of the oily phospholipid layer at different humidity, which will in-turn influence the capillary adhesion force.
+We suggest performing single seta adhesion force tests similar to \citet{RN202}
 using a hydrophilic and fluorinated probe in air and underwater conditions. 
@@
 would confirm the role of capillary contributions due to an oil-like phospholipid layer to gecko adhesion.
+Further work is also necessary to validate if the phospholipid layer in geckos' toes indeed has fluid-like properties.
 
@@
 toe are theoretically estimated from the capillary bridge model, with
-hair diameter = 400 nm, toe diameter = 4 mm, adhesive fluid volume
+hair diameter = 400 nm, toe diameter = 4 mm, phospholipid fluid volume
 = 4.19x10\protect\textsuperscript{-3} fL and 10\% hair coverage.
 \textquotedblleft\emph{Underwater: no bubble}\textquotedblright{}
-type contact is assumed for the \textquotedblleft Wet\textquotedblright{}
+contact mode is assumed for the \textquotedblleft Wet\textquotedblright{}
 case. Net adhesion force is calculated by assuming 5 toes on each
 leg and 4 legs in total on a gecko. Interfacial tension of the phospholipid
-layer (PL) in air and water are assumed to be 30 mN/m and 42 mN/m
+layer (PL) in air and water are assumed to be 30 mN m\protect\textsuperscript{-1} and 42 mN m\protect\textsuperscript{-1}
 respectively. PL contact angles with glass, PMMA, OTS-SAM and PTFE
@@
 is a more dominant parameter than substrate chemistry in controlling
-insect adhesion. Future work will explore how roughness can impact
+ladybug beetle traction force. Future work will explore how roughness can impact
 the net capillary force also in wet and submerged conditions.
-Our study thus can contribute to potential applications in the design of bio-inspired materials to achieve underwater adhesion
+We have limited our analysis only to normal adhesive forces, but insects like beetles in general rely on friction or shear forces during locomotion.
+Friction force usually correlates directly with the normal force, which is probably why previously reported shear adhesion forces of the dock beetle \cite{RN87} follow a similar qualitative trend as our normal adhesion force measurements on the ladybug beetle in both air and underwater conditions.
+However, the details of the interplay between friction and normal adhesion forces in animals is an open question and is beyond the scope of this paper.
+
+Our study can contribute to potential applications in the design of bio-inspired materials to achieve underwater adhesion
 via capillary bridges. Introduced bubbles can possibly be used to control underwater
 adhesion by changing the relative proportion of the arrays inside
-and outside the bubble. A suitable choice of adhesive fluid can be
-made tailored to the substrate and environment of application to achieve
-optimal adhesion performance.
+and outside the bubble. A suitable choice of an adhesion-mediating fluid can be
+made tailored to the substrate and environment of application to form capillary bridges with 
+optimal adhesion performance in bio-inspired fibrillar adhesive systems.
 
@@
 
-Ladybug beetles rely primarily on their oily fluid secretion to adhere
+Ladybug beetles rely primarily on their oily fluid secretion at the tarsal hair tips to adhere
 to surfaces in both air and underwater conditions. The beetles can
@@
 medium to the adhesive fluid bridges inside it. Oil wettability, thus,
-primarily controls the insect's adhesion in any given condition. A
-similar argument also explains previously reported underwater measurements
-in geckos \cite{RN15}, which highlights the possibility of capillary
-contributions to gecko adhesion. Future studies should characterise
+primarily controls the insect's adhesion in any given condition. 
+Our study highlights how a fluid-mediated strategy can help achieve strong adhesion even underwater. A
+similar argument also explains previously reported underwater adhesion force measurements
+in geckos \cite{RN15}, which suggests the possibility of capillary
+contributions to gecko adhesion mediated by an oil-like phospholipid layer. Future studies should characterise
 the fluid secretion's interfacial properties with a particular substrate
-to better understand the nature of the animal's adhesion.
+to better understand the fundamental nature of an animal's adhesion.
 
@@
 
-We are grateful to Eduard Arzt and Ren\textcyr{\`\cyre} Hensel for
+We are grateful to Eduard Arzt and Ren\textcyr{\`\cyre} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for
 fruitful discussions. This work was supported by the \emph{Deutsche Forschungsgemeinschaft}

### 2021-05-08 source/tex/supplementary.tex
minor edits in supplementary file
organized supporting info
included evolver script and other relevant files

@@
 
-\title{Wetting of the adhesive fluid controls underwater adhesion in insects: Supplementary material}
+\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary material}
 
@@
 %reset figure/table/equation numbers and include prefix
-\renewcommand{\thesection}{S.\arabic{section}}
-\setcounter{figure}{0} \renewcommand{\thefigure}{S.\arabic{figure}} 
-\setcounter{table}{0} \renewcommand{\thetable}{S.\arabic{table}} 
-\setcounter{equation}{0} \renewcommand{\theequation}{S.\arabic{equation}}
+\renewcommand{\thesection}{S1.\arabic{section}}
+\setcounter{figure}{0} \renewcommand{\thefigure}{S1.\arabic{figure}} 
+\setcounter{table}{0} \renewcommand{\thetable}{S1.\arabic{table}} 
+\setcounter{equation}{0} \renewcommand{\theequation}{S1.\arabic{equation}}
 
@@
 
-bsection{Capillary Bridge Model: Effect of hair diameter at constant fluid
+\section{Capillary Bridge Model: Effect of hair diameter at constant fluid
 volume}
@@
 keeping the third parameter fixed. p-values showing statistically
-significant difference between A and B are in boldface. The condition
+significant difference between A and B are in boldface. 
+CLES represents the statistical proportion of samples under A with higher adhesion than under B. The condition
 for statistical significance is based on the Bonferroni-corrected
@@
 
+\section{Field desorption mass spectroscopy}
+
+To test whether the ladybug beetles retain
+their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
+(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments, Malaysia). The measurements
+were done on the extracted secretions before and after submerging its
+legs under water. The middle leg of an Asian ladybird (\emph{Harmonia
+axyridis}) was immersed in 50 \textmu L Tetrahydrofuran (THF) for 20 min and then transferred
+to the measurement chamber of the FDMS. As a reference, pure THF was
+used. The second middle leg of the same ladybird was subsequently
+immersed in 100 \textmu L Milli-Q water for 15 min (close to the time-scale of the underwater adhesion tests), then in THF for
+20 min and then transferred to the measurement chamber of the spectrometer.
+Molecular weights were extracted from the peak positions of the
+FDMS spectra. Probable compostion was identified from the molecular weights by assuming the secretion fluid consists possibly of hydrocarbons, alcohols, aldehydes or carboxylic acids.
+
+FDMS results confirm the presence of adhesive fluid on the Asian ladybird's
+leg when underwater (Table \ref{tab:Molecular-distribution-of}).
+Molecular weights of the epicuticular grease extracted from the beetle’s leg, without and after immersion in water, show that, except
+for two molecular weights (406.8 g mol\protect\textsuperscript{-1} and 331.6 g mol\protect\textsuperscript{-1}), the chemical
+fingerprint remained unchanged. This let us assume that the tarsal adhesive fluid
+was not washed away underwater. Probable compounds in the fluid, corresponding
+to the resultant molecular weights, include mostly aliphatic hydrocarbons
+with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} let us conjecture that, 
+even for the case of \emph{Coccinella septempuctata}, the tarsal adhesive fluid was not washed away from the hairs during the underwater experiments.
+A detailed study is however essential to ensure that the difference in the ladybug species between our adhesion and FDMS tests doesn't qualitatively change the above outcome.
+Further, the detected compounds would also include cuticular secretions from the leg apart from the tarsal fluid.
+Thus, a more precise fluid extraction method is necessary to definitely confirm the above conjecture, and will be a subject of future study.
+
+\begin{table}[H]
+\centering{}%
+\begin{tabular}{|c|c|c|}
+\hline 
+Without submerging (g mol\protect\textsuperscript{-1}) & After submerging (g mol\protect\textsuperscript{-1}) & Probable compounds\tabularnewline
+\hline 
+\hline 
+324.5 & 324.5 & C\textsubscript{23}H\textsubscript{48}, C\textsubscript{22}H\textsubscript{44}O\tabularnewline
+\hline 
+ & 331.6 & C\textsubscript{24}H\textsubscript{44}\tabularnewline
+\hline 
+350.5 & 350.5 & C\textsubscript{25}H\textsubscript{50}\tabularnewline
+\hline 
+352.5 & 352.5 & C\textsubscript{25}H\textsubscript{52}, C\textsubscript{24}H\textsubscript{48}O\tabularnewline
+\hline 
+378.5 & 378.5 & C\textsubscript{27}H\textsubscript{54}\tabularnewline
+\hline 
+404.6 & 404.5 & C\textsubscript{29}H\textsubscript{56}\tabularnewline
+\hline 
+406.8 &  & C\textsubscript{29}H\textsubscript{58}\tabularnewline
+\hline 
+432.8 & 432.7 & C\textsubscript{31}H\textsubscript{60}\tabularnewline
+\hline 
+\end{tabular}\caption{Molecular weights of the tarsal adhesive fluid secretion of \emph{Harmonia axyridis}
+without and after submerging the beetle's leg in water. \label{tab:Molecular-distribution-of}}
+\end{table}
+
 \section{Capillary force due to a bubble\label{subsec:Capillary-force-due}}
@@
 to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
-pad should be negligible.
+pad should be negligible. Measurement videos are included in the supplementary material (S6).
 

### 2021-05-10 source/tex/ladybug_adhesion.tex
some of edits suggested by Thomas added

@@
 
-\keywords{bio-adhesion; capillary force; bubble; insects; gecko}
+\keywords{bio-adhesion; capillary force; air plastron; insects; gecko}
 
@@
 The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
-of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water.
+of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water. %split references%
 
@@
 \section{Experimental}
-
+%normal to untrated glass%
 Normal adhesion force measurements on a restrained leg in a live
 beetle were performed.
-We focus our study only on a single tarsal adhesive pad of the leg by carefully fixing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion.
+We focused our study only on a single tarsal adhesive pad of the leg by carefully immobilizing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion.
 We characterised adhesion by the pull-off force
@@
 
-The seven-spotted adult male adult ladybug beetles (\emph{Coccinella septempuctata})
+The adult seven-spotted male ladybug beetles (\emph{Coccinella septempuctata})
 were purchased from Katz Biotech (Baruth, Germany). The beetles were housed in a plastic box filled with leaves,
 twigs and stones at room temperature and 60-80\% relative humidity
-with daily access to sunlight. They were fed with raisins, honey and
-water \emph{ad libitum}. The beetles on average weighed 34 $\pm$ 4 mg and were experimented on within three weeks of being housed under above conditions.
+with natural daylight. They were fed with raisins, honey and
+water \emph{ad libitum}. The beetles on average weighed 34 $\pm$ 4 mg and were used within three weeks of being housed under above conditions.
 
@@
 The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack.
-The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset).
+The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset).
 Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres.
@@
 Five force measurements were subsequently performed, each on a fresh spot of the substrate, and averaged for data analysis. 
-Experiments were repeated with five distinct male beetles for each combination of contact mode (``\emph{in air}'', (``\emph{underwater:
-bubble}'' and (``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic).
+Experiments were repeated with five distinct male beetles for each combination of contact mode (``\emph{in air}'', ``\emph{underwater:
+bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic).
 Thus, in total, 30 distinct beetles were tested.
 After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.
+%mention data points number clearly for each box, what is averaged etc. also%
 
@@
 water surface shifted, which influenced the force readout due to surface
-tension and buoyancy. This effect needed to be cancelled. So, a ``background''
+tension and buoyancy. This effect needed to be cancelled. Therefore, a ``background''
 force data was recorded, where the submerged beetle makes no contact
@@
 comparison between groups.
-
+%Include ANOVA as well, include F, t, degrees of freedom%
 \subsubsection{Substrate preparation}
@@
 \end{figure}
-
+%outlier%
 Apart from the three depicted contact modes, we observed an additional
@@
 substrate as the volume decreases.
-
+%change 1e6 to 1 10^6%
 \subsection{Adhesion of a hairy pad: Effect of the hair tip diameter}
@@
 contact of all hairs' terminals.
-
+%FDMS keep as unpublished data, remove from supplementary.%
 In the model, we assume that all the hairs detach simultaneously to

### 2021-05-10 source/tex/ladybug_adhesion.tex
finalized manuscript based on thomas's suggestions
ready to send to JEB

@@
 \usepackage{subcaption}
+\usepackage[pagewise]{lineno}
+\linenumbers
 
@@
 
-While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored.
+While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored.
 Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces.
@@
 It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater.
-However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force.
+However, it remained unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force.
 The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged.
@@
 The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
-of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water. %split references%
+of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \cite{RN221} and \emph{Epilachna vingtipunctuata} \cite{RN222}, rendering it immiscible with water.
 
@@
 \section{Experimental}
-%normal to untrated glass%
+
 Normal adhesion force measurements on a restrained leg in a live
@@
 We characterised adhesion by the pull-off force
-during detachment, tested on smooth normal and
+during detachment, tested on smooth untreated and
 fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
@@
 
-Five force measurements were subsequently performed, each on a fresh spot of the substrate, and averaged for data analysis. 
-Experiments were repeated with five distinct male beetles for each combination of contact mode (``\emph{in air}'', ``\emph{underwater:
-bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic).
-Thus, in total, 30 distinct beetles were tested.
+Five force measurements were subsequently performed, each on a fresh spot of the substrate, and were averaged to avoid pseudo-replication during data analysis.
+Experiments were repeated with 30 distinct male beetles for all combinations of contact mode (``\emph{in air}'', ``\emph{underwater:
+bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic), 5 beetles for each  combination.
 After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.
-%mention data points number clearly for each box, what is averaged etc. also%
 
@@
 
-Data sets were compared for statistical differences using pairwise
-Student t-test and their corresponding p-value and Common Language
+Data sets were compared for statistical differences using two-way ANOVA analysis, with \emph{contact mode} and \emph{substrate chemistry} as the categorical variables and \emph{adhesion force} as the dependant variable.
+Pairwise
+Student t-test were done for post-hoc analysis and their corresponding p-value and Common Language
 Effect Size (CLES) are reported. Shapiro-Wilk test was done for each
@@
 comparison between groups.
-%Include ANOVA as well, include F, t, degrees of freedom%
+
 \subsubsection{Substrate preparation}
@@
 the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
-for 3 hours. Henceforth, we refer to the hydrophilic normal glass substrate 
+for 3 hours. Henceforth, we refer to the hydrophilic untreated glass substrate 
 as simply \emph{Glass} and the hydrophobic fluorinated glass substrate as \emph{PFOTS}.
@@
  adhesion force measurements of ladybug beetle's (\emph{Coccinella
-septempuctata}) distal pad on normal hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
-conditions (n=30). The two modes of contact during underwater experiments
+septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
+conditions (n=5 per box). The two modes of contact during underwater experiments
 are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
-and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
+and \textquotedblleft\emph{no bubble}\textquotedblright . The small diamonds represent outlier points. Crosses
 represent theoretical predictions (see text) of adhesion force, while, circles
@@
 \end{figure}
-%outlier%
+
 Apart from the three depicted contact modes, we observed an additional
@@
 In this scenario, the ventral view recordings show that none of the hairs
-appear to contact well with either glass or PFOTS substrate (supplementary video S5), unlike the other
-three contact modes (supplementary video S2-S4). This ``bad contact'' scenario only happened underwater and shows no adhesion 
+appear to contact well with either glass or PFOTS substrate (supplementary video S3), unlike the other
+three contact modes (supplementary video S2). This ``bad contact'' scenario only happened underwater and shows no adhesion 
 with either glass or PFOTS substrate. While it was not completely
@@
 \includegraphics{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
-meniscus in contact with normal glass and PFOTS-coated glass in air and underwater conditions.
+meniscus in contact with untreated glass and PFOTS-coated glass in air and underwater conditions.
 The corresponding interfacial tension, \textgreek{g}, and contact
@@
 contact of all hairs' terminals.
-%FDMS keep as unpublished data, remove from supplementary.%
+
 In the model, we assume that all the hairs detach simultaneously to
@@
 in air. This effect can be explained by capillary forces and the wetting properties of the fluid. Our
-preliminary chemical composition analysis of a beetle's tarsal secretions before and after immersing its leg underwater 
-validates our assumption that the tarsal adhesive fluid should form capillary bridges with the substrate
-underwater, instead of getting washed away (see supplementary info Section S1.5).
+preliminary chemical composition analysis of a beetle's tarsal secretions before and after immersing its leg underwater (unpublished data) suggests that the tarsal adhesive fluid do not get washed away when underwater.
+Therefore, the fluid should be able to form capillary bridges and help mediate adhesion even when underwater.
 
@@
 that the underwater experiments performed on geckos \cite{RN199,RN15}
-indicate a capillary contribution to gecko adhesion. Previous studies on gecko adhesion have attributed capillary effects to be a result of
-water condensation from ambient humid air onto the setal hair tips \cite{RN197, RN203, RN218}.
-We however emphasize that capillary contribution in gecko adhesion could rather be a result of its setal phospholipid layer rather than water. %SURFACE TENSION SOURCE%
+indicate a capillary contribution to gecko adhesion.
+Previous studies on gecko adhesion have attributed capillary effects to be a result of water monolayers adsorbed from ambient humid air onto the spatuale hair tips \cite{RN197, RN203, RN218}.
+We however emphasize that capillary contribution in gecko adhesion could rather be a result of its setal phospholipid layer rather than water.
 The previously reported influence of humidity on gecko adhesion \cite{RN197} could possibly be an effect of change in surface tension of the oily phospholipid layer at different humidity, which will in-turn influence the capillary adhesion force.

### 2021-05-10 source/tex/supplementary.tex
finalized manuscript based on thomas's suggestions
ready to send to JEB

--- 2021-02-16 source/tex/supplementary.tex
@@
 
-\title{Wetting of the adhesive fluid controls underwater adhesion in insects: Supplementary material}
+\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information (S1)}
 
@@
 
-Pairwise statistical comparison of single leg adhesion force measurements
-of the ladybug beetle (\emph{Coccinella septempuctata}) for each contact
-type and substrate are shown (Table \ref{tab:Statistical-analysis}).
+Two-way ANOVA test showed a significant effect of the \emph{Contact mode} (p=0.001, F=9.596, degrees of freedom=2) 
+and \emph{Substrate} (p<0.001, F=36.231, degrees of freedom=1) categories on the single leg adhesion force measurements
+of the ladybug beetle (\emph{Coccinella septempuctata}).
+Signifanct interaction between the above two was seen (p=0.001, F=10.551, degrees of freedom=2).
+Post-hoc analysis results are shown below (Table \ref{tab:Statistical-analysis}).
 The uncorrected p-values and Common Language Effect Size (CLES) are
-obtained from post-hoc pair-wise Student t-test between A and B while
+obtained from pair-wise Student t-test between A and B while
 keeping the third parameter fixed. p-values showing statistically
-significant difference between A and B are in boldface. The condition
+significant difference between A and B are in boldface. 
+CLES represents the statistical proportion of samples under A with higher adhesion than under B. The condition
 for statistical significance is based on the Bonferroni-corrected
@@
 \noindent \begin{centering}
-\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|>{\centering}m{0.15\linewidth}|}
+\begin{tabular}{|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}|>{\raggedright}m{0.15\linewidth}||>{\centering}m{0.1\linewidth}|>{\centering}m{0.1\linewidth}|>{\centering}m{0.1\linewidth}|}
 \hline
-Fixed & A & B & p-value & CLES\tabularnewline
+Fixed variable & A & B & T & p-value & CLES\tabularnewline
 \hline 
 \hline 
-In air & PFOTS & Glass & 0.959 & 0.48\tabularnewline
+In air & PFOTS & Glass & -0.053 & 0.959 & 0.48\tabularnewline
 \hline
-Underwater: bubble & PFOTS & Glass & 0.011 & 0.96\tabularnewline
+Underwater: bubble & PFOTS & Glass & 3.292 & 0.011 & 0.96\tabularnewline
 \hline
-Underwater: no bubble & PFOTS & Glass & \textbf{< 0.001} & 1.0\tabularnewline
+Underwater: no bubble & PFOTS & Glass & 10.044 & 0.0 & 1.0\tabularnewline
 \hline
-PFOTS & In air & Underwater: bubble & 0.897 & 0.48\tabularnewline
+PFOTS & In air & Underwater: bubble & 0.133 & 0.897 & 0.48\tabularnewline
 \hline
-PFOTS & In air & Underwater: no bubble & 0.828 & 0.48\tabularnewline
+PFOTS & In air & Underwater: no bubble & -0.224 & 0.828 & 0.48\tabularnewline
 \hline
-PFOTS & Underwater: bubble & Underwater: no bubble & 0.721 & 0.44\tabularnewline
+PFOTS & Underwater: bubble & Underwater: no bubble & -0.37 & 0.721 & 0.44\tabularnewline
 \hline
-Glass & In air & Underwater: bubble & \textbf{0.002} & 1.0\tabularnewline
+Glass & In air & Underwater: bubble & 4.688 & 0.002 & 1.0\tabularnewline
 \hline
-Glass & In air & Underwater: no bubble & \textbf{< 0.001} & 1.0\tabularnewline
+Glass & In air & Underwater: no bubble & 11.341 & 0.0 & 1.0\tabularnewline
 \hline
-Glass & Underwater: bubble & Underwater: no bubble & 0.07 & 0.84\tabularnewline
+Glass & Underwater: bubble & Underwater: no bubble & 2.086 & 0.07 & 0.84\tabularnewline
 \hline 
@@
 to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
-pad should be negligible.
+pad should be negligible. Example measurement video is included in the supplementary data (S4).
 

### 2021-05-11 source/tex/ladybug_adhesion.tex
final formatting edits for submission to JEB

@@
 \begin{document}
+
+\section*{Summary statement}
+
+Fluid-mediated adhesion seen in animals such as ladybug beetles allow them to attach to surfaces not just in air but also in underwater conditions.
+
 \begin{abstract}
@@
 One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}.
-This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
+This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
 Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact.
@@
 Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres.
-A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test.
+A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test.
 After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.
@@
 represent attraction and the minimum force peak during the final retraction
-step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material (S2-S4).}
+step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the supplementary material (see Movie1).}
 \end{figure}
@@
 data set to verify a normal distribution of its residuals and Levene's
-test was done to check for variance homogeneity, to validate the t-test
+test was done to check for variance homogeneity, to validate the ANOVA 
 assumptions. Bonferroni's correction was used to account for multiple
@@
 and receding contact angles were measured for a maximum drop volume
-of 10 \textmu l and with 0.5 \textmu l s\protect\textsuperscript{-1} flow rate (Table \ref{tab:Contact-Angles}).
-
-\begin{table}[H]
-\centering{}%
-\begin{tabular}{|c|c|c|c|}
-\hline 
-Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
-\hline 
-\hline 
-\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
-\cline{2-4} \cline{3-4} \cline{4-4} 
- & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
-\hline 
-\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
-\cline{2-4} \cline{3-4} \cline{4-4} 
- & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
-\hline 
-\end{tabular}\caption{Dynamic contact angles (Mean \ensuremath{\pm} SD, n = 3) of Milli-Q water and n-hexadecane on the different test substrates. \label{tab:Contact-Angles}}
-\end{table}
+of 10 \textmu l and with 0.5 \textmu l s\protect\textsuperscript{-1} flow rate (see supplementary section S2).
 
@@
 glass and PFOTS were similar, i.e. no significant differences were
-detected (Figure \ref{fig:Effect-of-contact} and Table S1.1).
+detected (Figure \ref{fig:Effect-of-contact} and supplementary section S3).
 In contrast, the underwater adhesion on a PFOTS surface was significantly
@@
 and \textquotedblleft\emph{no bubble}\textquotedblright . The small diamonds represent outlier points. Crosses
-represent theoretical predictions (see text) of adhesion force, while, circles
+represent theoretical predictions of adhesion force, while, circles
 represent the contribution of the bubble itself, calculated from the
-capillary bridge model. In the model, hair diameter = 4 \textmu m,
+capillary bridge model (see text). In the model, hair diameter = 4 \textmu m,
 pad diameter = 200 \textmu m, hair length = 40 \textmu m,
@@
 In this scenario, the ventral view recordings show that none of the hairs
-appear to contact well with either glass or PFOTS substrate (supplementary video S3), unlike the other
-three contact modes (supplementary video S2). This ``bad contact'' scenario only happened underwater and shows no adhesion 
+appear to contact well with either glass or PFOTS substrate (supplementary data: Movie2), unlike the other
+three contact modes (supplementary data: Movie1). This ``bad contact'' scenario only happened underwater and shows no adhesion 
 with either glass or PFOTS substrate. While it was not completely
@@
 The capillary force, $f$, is the sum of two contributions: surface
-tension and Laplace pressure (equation S1.1). Force
+tension and Laplace pressure. Force
 versus distance for a single capillary bridge was calculated by Surface
-Evolver simulations\cite{RN206}  (described in supplementary section S1.1),
+Evolver simulations\cite{RN206}  (see supplementary section S1 for details),
 and used to obtain $F_{net}$ as a function of $d$ for each mode
@@
 are plotted as a function of contact angle with the substrate, together
-with its Laplace and surface tension components (equation S1.1).
+with its Laplace and surface tension components (equation S1 in supplementary section).
 Simulation snapshots of the liquid meniscus corresponding to angles
@@
 further validates that the bubble's contribution is insignificant
-(Figure S1.3).
+(see supplementary section S4).
 
@@
 the net capillary force also in wet and submerged conditions.
-We have limited our analysis only to normal adhesive forces, but insects like beetles in general rely on friction or shear forces during locomotion.
+In our study, we have only considered normal adhesive forces, but insects like beetles in general rely on friction or shear forces during locomotion.
 Friction force usually correlates directly with the normal force, which is probably why previously reported shear adhesion forces of the dock beetle \cite{RN87} follow a similar qualitative trend as our normal adhesion force measurements on the ladybug beetle in both air and underwater conditions.
@@
 
-\section{Acknowledgement}
+\section{Acknowledgements}
 
-We are grateful to Eduard Arzt and Ren\textcyr{\`\cyre} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for
-fruitful discussions. This work was supported by the \emph{Deutsche Forschungsgemeinschaft}
+We are grateful to Prof. Dr. Eduard Arzt and Dr. Ren\textcyr{\`\cyre} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for fruitful discussions.
+
+\section{Competing interests}
+The authors declare no competing or financial interests.
+
+%\section{Data availability}
+%Data are available from the Dryad digital repository. %CHECK THIS%
+
+\section{Funding}
+This work was supported by the \emph{Deutsche Forschungsgemeinschaft}
 (Grant number: PI 1351/2-1) and the \emph{Max Planck Graduate Center} with the \emph{Johannes Gutenberg-Universit\"{a}t Mainz} (MPGC).

### 2021-05-11 source/tex/supplementary.tex
final formatting edits for submission to JEB

@@
 
-\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information (S1)}
+\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information}
 
@@
 %reset figure/table/equation numbers and include prefix
-\renewcommand{\thesection}{S1.\arabic{section}}
-\setcounter{figure}{0} \renewcommand{\thefigure}{S1.\arabic{figure}} 
-\setcounter{table}{0} \renewcommand{\thetable}{S1.\arabic{table}} 
-\setcounter{equation}{0} \renewcommand{\theequation}{S1.\arabic{equation}}
+\renewcommand{\thesection}{S\arabic{section}}
+\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} 
+\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} 
+\setcounter{equation}{0} \renewcommand{\theequation}{S\arabic{equation}}
 
@@
 Capillary force due to a single adhesive fluid or bubble meniscus (termed ``capillary
-bridge'') is calculated by performing simulations in Surface Evolver
+bridge'') was calculated by performing simulations in Surface Evolver
 \cite{RN206}, similar to the method described by \citet{RN93}.
 A simple cubic geometry, mimicking the capillary bridge, of constant
-volume, $V$, is defined as the initial condition with an interfacial
+volume, $V$, was defined as the initial condition with an interfacial
 tension, $\gamma$, with the surrounding medium. Interfacial tension
@@
 $d$ between the top face and the substrate. The boundary conditions
-are set corresponding to a pinned contact line of diameter $D$ on
+were set corresponding to a pinned contact line of diameter $D$ on
 the top face and constant interfacial tension with the substrate on
-the bottom. All lengths are normalised relative to length $s=\left(3V/4\pi\right)^{1/3}$.
-An appropriate geometry refinement routine is chosen to evolve the
+the bottom. All lengths were normalised relative to length $s=\left(3V/4\pi\right)^{1/3}$.
+An appropriate geometry refinement routine was chosen to evolve the
 capillary bridge shape to its minimum energy state. The normalised
@@
 
-The gap distance $d$ is varied stepwise and the capillary force is
+The gap distance $d$ was varied stepwise and the capillary force was
 calculated each time to obtain force-distance curves for a particular
@@
 
-\section{Single capillary bridge: Effect of volume}
+%\section{Single capillary bridge: Effect of volume}
+%
+%Surface Evolver simulation results showing the effect of volume on
+%the maximum capillary force of a single fluid bridge. Since the fluid
+%is pinned at the top to the same diameter, D, a smaller volume would
+%result in high interfacial curvatures, which increases the capillary
+%force due to the negative Laplace pressure. In this case, small contact
+%angles lead to a greater increase in adhesion.
+%
+%\begin{figure}[H]
+%
+%\begin{centering}
+%\includegraphics{FigureS2-Effect_of_fluid_volume}\caption{Normalised maximum capillary force for a single bridge as a function
+%of fluid volume}
+%\par\end{centering}
+%\end{figure}
+%
+%
+%\section{Capillary Bridge Model: Effect of hair diameter at constant fluid
+%volume}
+%
+%Here, instead of scaling the fluid volume relative to the hair diameter,
+%we now assume a fixed total fluid volume distributed equally among
+%the $N$ hairs. Total fluid volume, $V_{total}=NV_{f}=2000$. Hair
+%diameter is varied while keeping the total hair contact area constant.
+%Length is in arbitrary units. Forces increase at a much smaller rate
+%on decreasing diameter when compared to the case with self-similar
+%scaling of fluid volume (Figure 8 in main text).
+%
+%\begin{figure}[H]
+%\includegraphics{FigureS3-Effect_of_hair_size(constant_vol)}
+%
+%\caption{Normalised adhesion force of hairy pad system on a hydrophilic and
+%hydrophobic substrate as a function of hair diameter ($D_{h}$), calculated
+%from the capillary bridge model. The total adhesive fluid volume is
+%fixed to 2000. Adhesion forces are calculated from minima of the respective
+%force-distance curves. Negative force value represents attraction.
+%The bubble's contribution to the net force for an \emph{underwater:
+%bubble} contact is denoted by plus symbols. Bubble volume and pad
+%diameter are kept fixed. All lengths are scaled relative to $D_{p}$.}
+%\end{figure}
 
-Surface Evolver simulation results showing the effect of volume on
-the maximum capillary force of a single fluid bridge. Since the fluid
-is pinned at the top to the same diameter, D, a smaller volume would
-result in high interfacial curvatures, which increases the capillary
-force due to the negative Laplace pressure. In this case, small contact
-angles lead to a greater increase in adhesion.
+\section{Substrate characterization}
 
-\begin{figure}[H]
-
-\begin{centering}
-\includegraphics{FigureS2-Effect_of_fluid_volume}\caption{Normalised maximum capillary force for a single bridge as a function
-of fluid volume}
-\par\end{centering}
-\end{figure}
-
-\section{Capillary Bridge Model: Effect of hair diameter at constant fluid
-volume}
-
-Here, instead of scaling the fluid volume relative to the hair diameter,
-we now assume a fixed total fluid volume distributed equally among
-the $N$ hairs. Total fluid volume, $V_{total}=NV_{f}=2000$. Hair
-diameter is varied while keeping the total hair contact area constant.
-Length is in arbitrary units. Forces increase at a much smaller rate
-on decreasing diameter when compared to the case with self-similar
-scaling of fluid volume (Figure 8 in main text).
-
-\begin{figure}[H]
-\includegraphics{FigureS3-Effect_of_hair_size(constant_vol)}
-
-\caption{Normalised adhesion force of hairy pad system on a hydrophilic and
-hydrophobic substrate as a function of hair diameter ($D_{h}$), calculated
-from the capillary bridge model. The total adhesive fluid volume is
-fixed to 2000. Adhesion forces are calculated from minima of the respective
-force-distance curves. Negative force value represents attraction.
-The bubble's contribution to the net force for an \emph{underwater:
-bubble} contact is denoted by plus symbols. Bubble volume and pad
-diameter are kept fixed. All lengths are scaled relative to $D_{p}$.}
-\end{figure}
+The surface chemistry of untreated glass (hydrophilic) and PFOTS-coated glass (hydrophobic) were characterized using dynamic contact angle measurements (Table \ref{tab:Contact-Angles}).
+\begin{table}[H]
+\centering{}%
+\begin{tabular}{|c|c|c|c|}
+\hline 
+Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
+\hline 
+\hline 
+\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
+\cline{2-4} \cline{3-4} \cline{4-4} 
+ & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
+\hline 
+\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
+\cline{2-4} \cline{3-4} \cline{4-4} 
+ & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
+\hline 
+\end{tabular}\caption{Dynamic contact angles (Mean \ensuremath{\pm} SD, n = 3) of Milli-Q water and n-hexadecane on the different test substrates. \label{tab:Contact-Angles}}
+\end{table}
 
@@
 of the ladybug beetle (\emph{Coccinella septempuctata}).
-Signifanct interaction between the above two was seen (p=0.001, F=10.551, degrees of freedom=2).
+Signifanct interaction between the above two categories was seen (p=0.001, F=10.551, degrees of freedom=2).
 Post-hoc analysis results are shown below (Table \ref{tab:Statistical-analysis}).
-The uncorrected p-values and Common Language Effect Size (CLES) are
+The uncorrected p-values and Common Language Effect Size (CLES) were
 obtained from pair-wise Student t-test between A and B while
-keeping the third parameter fixed. p-values showing statistically
+keeping the third parameter fixed (degrees of freedom=8 for each pair). p-values showing statistically
 significant difference between A and B are in boldface. 
@@
 \par\end{centering}
-\caption{\label{tab:Statistical-analysis}}
+\caption{Post-hoc t-test results for each combination of contact mode and substrate\label{tab:Statistical-analysis}}
 \end{table}
 
-\section{Capillary force due to a bubble\label{subsec:Capillary-force-due}}
+\section{Capillary force due to an air bubble\label{subsec:Capillary-force-due}}
 
-Capillary force of a single bubble against a PFOTS surface are compared
-for two different volumes. The volumes correspond to the expected
-range in the case of the trapped bubble in a ladybug. Here, the bubble
-is pinned to a micropatterned PDMS substrate on the top. The maximum
+Capillary force of a single air bubble against a PFOTS-coated glass surface are compared
+for two different volumes (Figure \ref{fig:Bubble_capillary_force}). The volumes correspond to the expected
+range for the case of the trapped air bubble in a ladybug's pad. Here, the bubble
+was pinned to a micropatterned PDMS substrate on the top. Approach-retract tests were performed
+at 62.5 \textmu m s\protect\textsuperscript{-1} speed. The maximum
 adhesion force of any of the bubble never exceeds 50 \textmu N,
@@
 to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
-pad should be negligible. Example measurement video is included in the supplementary data (S4).
+pad should be negligible. Example measurement video is included in the supplementary data (Movie3).
 
@@
 \begin{centering}
-\includegraphics{FigureS4-Expt_bubble_force}\caption{Capillary force of the bubble}
+\includegraphics{FigureS4-Expt_bubble_force}\caption{Capillary force of the pinned bubble against a PFOTS-coated glass surface \label{fig:Bubble_capillary_force}}
 \par\end{centering}
 \end{figure}
+
+\section{Supplementary video files}
+
+\subsection*{Movie1}
+Adhesion test recordings showing the three contact modes: \emph{in air},  \emph{underwater: bubble} and  \emph{underwater: no bubble} on a hydrophobic PFOTS-coated glass substrate.
+The two top panels of the video show the synchronous raw bottom-view and side-view recordings of the pad making contact with the substrate.
+The lower-left panel shows contact area extraction of the hairs with the surface via image processing and lower-right panel shows the corresponding temporal contact force and area data plot, with the data cursor synchronized with the other panels.
+
+\subsection*{Movie2}
+Adhesion test recording corresponding to the case of \emph{bad contact}, which occurred underwater on the PFOTS-coated glass substrate
+
+\subsection*{Movie3}
+Adhesion test recording of an air bubble (2nL volume) pinned to a microstructured PDMS on the top and making contact with a smooth PFOTS-coated glass substrate on the bottom.
 

### 2021-07-13 source/jeb_tex/manuscript.tex
used JEB latex template and ported the manuscript format.
reference style needs correction.

--- 2021-05-11 source/tex/ladybug_adhesion.tex
@@
-%% LyX 2.3.6 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[english]{achemso}
-\setkeys{acs}{keywords = true}
-\usepackage[T2A,LGR,T1]{fontenc}
-\usepackage{babel}
-\usepackage{array}
-\usepackage{textcomp}
-\usepackage{url}
+%% Author_tex.tex
+%% V1.0
+%% developed by Nova Techset
+%%
+%% This file describes the coding for COB.cls
+
+\documentclass[vruler,JEB]{COB}%%%%where COB is the template name
+
+%The authors can define any packages after the \documentclass{COB} command.
+
+%\usepackage{amsmath} for dealing with mathematics,
+%\usepackage{amsthm} for dealing with theorem environments,
+%\usepackage{cite} %for dealing with citations
+%\usepackage{hyperref} for linking the cross references
+%\usepackage{graphics} for dealing with figures.
+%\usepackage{algorithmic} for describing algorithms
+%\usepackage{subfig} for getting the subfigures e.g., "Figure 1a and 1b" etc.
+%\usepackage{url} It provides better support for handling and breaking URLs.
+
+\usepackage{widetext-TI}
+%
+%\usepackage{babel}
+%\usepackage[authoryear]{natbib}
+%\usepackage{array}
+%\usepackage{textcomp}
+%\usepackage{url}
 \usepackage{multirow}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{subscript}
-\usepackage[unicode=true,pdfusetitle,
- bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
- breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
- {hyperref}
-%\usepackage{lineno}
-%\linenumbers
+%\usepackage{amsmath}
+%\usepackage{graphicx}
+%\usepackage{subscript}
+%\usepackage[unicode=true,pdfusetitle,
+% bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
+% breaklinks=false,backref=false,colorlinks=false]
+% {hyperref}
+%
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{condition}{Condition}
+\bibliographystyle{jeb}
+\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
+  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}
+%% Because html converters don't know tabularnewline
+\providecommand{\tabularnewline}{\\}
+\newcommand \newblock{\textbf}
+%The author can find the documentation of the above style file and any additional
+%supporting files if required from "http://www.ctan.org"
 
-\makeatletter
+% *** Do not adjust lengths that control margins, column widths, etc. ***
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
+\begin{document}
+
+\supertitle{Research Article}
 
@@
 
-\author{Pranav Sudersan}
+\author{Pranav Sudersan$^{1}$, Michael Kappl$^{1}$, Bat-El Pinchasik$^{2}$, Hans-J\"{u}rgen Butt$^{1}$ and Thomas Endlein$^{1}$}
 
-\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
-Mainz, Germany}
+\address{\add{1}{Max Planck Institute for Polymer Research, Ackermannweg 10, Mainz, Germany}
+\add{2}{School of Mechanical Engineering, Tel Aviv University, Tel Aviv-Yafo, Israel}}
 
-\author{Michael Kappl}
+\corres{(\email{endlein01@mpip-mainz.mpg.de}; \email{xxxx@xxxx.xxx.xx})}
 
-\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
-Mainz, Germany}
+\date{Received 11 May 2021; revised 11 May 2021} %CHECK DATE
 
-\author{Bat-El Pinchasik}
-
-\affiliation{School of Mechanical Engineering, Tel Aviv University, Tel Aviv-Yafo,
-Israel}
-
-\author{Hans-J\"{u}rgen Butt}
-
-\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
-Mainz, Germany}
-
-\author{Thomas Endlein}
-
-\affiliation{Max Planck Institute for Polymer Research, Ackermannweg 10, 55128
-Mainz, Germany}
-
-\email{endlein01@mpip-mainz.mpg.de}
-
-\keywords{bio-adhesion; capillary force; air plastron; insects; gecko}
-
-\DeclareRobustCommand{\greektext}{%
-  \fontencoding{LGR}\selectfont\def\encodingdefault{LGR}}
-\DeclareRobustCommand{\textgreek}[1]{\leavevmode{\greektext #1}}
-\ProvideTextCommand{\~}{LGR}[1]{\char126#1}
-
-\DeclareRobustCommand{\cyrtext}{%
-  \fontencoding{T2A}\selectfont\def\encodingdefault{T2A}}
-\DeclareRobustCommand{\textcyr}[1]{\leavevmode{\cyrtext #1}}
-
-\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
-  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}
-
-%% Because html converters don't know tabularnewline
-\providecommand{\tabularnewline}{\\}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-\SectionNumbersOn
-%\setkeys{acs}{doi = true}
-\setkeys{Gin}{width=\linewidth}
-\usepackage{subcaption}
-\usepackage[pagewise]{lineno}
-\linenumbers
-
-\makeatother
-
-\begin{document}
-
-\section*{Summary statement}
-
-Fluid-mediated adhesion seen in animals such as ladybug beetles allow them to attach to surfaces not just in air but also in underwater conditions.
+\maketitle
 
 \begin{abstract}
-
 Many insects can climb smooth surfaces using hairy adhesive pads on their legs mediated by tarsal fluid secretions.
@@
 
+\keywords{bio-adhesion; capillary force; air plastron; insects; gecko}
+
 \section{Introduction}
@@
 The question on how insects and other small animals climb smooth and slippery
-surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}.
+surfaces has fascinated scientists for the past three centuries \citep{RN198,RN59}.
 We know that such animals are able to adhere by using specialised organs on their feet called adhesive pads.
 These adhesive pads can generally be described as either ``smooth'' or ``hairy''.
-Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads.
-Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly.
+Several insect orders including earwigs, flies, and beetles \citep{Gorb:2001b} but also several spiders \citep{Coddington:1991} and arboreal lizards \citep{Williams:1982} bear hairy pads.
+Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \citep{RN20}, which makes them suitable to adhere to most surfaces reversibly.
 The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects.
-The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}.
-Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion.
+The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\citep{RN19}.
+Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\citep{RN79}, illustrating the role of hair geometry in adhesion.
 Insect tarsal hairs secrete an adhesion-mediating fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion'').
-In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN201,RN155,RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.
+In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \citep{RN201,RN155,RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \citep{RN202}.
 
 While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored.
-Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces.
+Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces.
 However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate.
-One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}.
-This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
+One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}.
+This has been shown in a recent study by \citep{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
 Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact.
@@
 The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged.
-In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \cite{RN108}.
-The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
-of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \cite{RN221} and \emph{Epilachna vingtipunctuata} \cite{RN222}, rendering it immiscible with water.
+In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \citep{RN108}.
+The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\citep{RN96} with traces
+of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} \citep{RN221} and \emph{Epilachna vingtipunctuata} \citep{RN222}, rendering it immiscible with water.
 
@@
 We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces.
-Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \cite{RN145} and they can also walk underwater.
+Male ladybug beetles were chosen since they possess adhesive pads having mostly flat discoidal tipped hairs, which allow them to show superior adhesion on hard surfaces compared to females \citep{RN145} and they can also walk underwater.
 Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions.
@@
 Finally, we discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.
-We hope our study to provide new strategies to design bio-inspired materials that show good adhesive properties in both air and underwater conditions, similar to what has been previously reported for terrestrial beetles \cite{RN87}.
+We hope our study to provide new strategies to design bio-inspired materials that show good adhesive properties in both air and underwater conditions, similar to what has been previously reported for terrestrial beetles \citep{RN87}.
 
@@
 
- %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
+ %The beetle's leg was constrained similar to the method described by Bullock et al \citep{RN19}.
 An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
@@
 instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
-was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
+was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
 A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
@@
 
-\begin{figure}[H]
-\begin{centering}
-\includegraphics[scale=0.5]{Figure1-Setup_schematic}
-\par\end{centering}
-\caption{\label{fig:Setup} Adhesion test setup (see text for details).
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=6in]{Figure1-Setup_schematic}%
+\caption[]{Adhesion test setup (see text for details).
 Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange).
@@
 step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the supplementary material (see Movie1).}
-\end{figure}
+\label{fig:Setup}
+\end{figure*}
+
+%\begin{figure}
+%\begin{centering}
+%\includegraphics[width=3in]{Figure1-Setup_schematic}
+%\par\end{centering}
+%\caption{\label{fig:Setup} Adhesion test setup (see text for details).
+Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange).
+The recorded force data and
+%contact area of a distal pad are shown in the bottom-right plot, in which, the shaded
+%regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
+%represent attraction and the minimum force peak during the final retraction
+%step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the supplementary material (see Movie1).}
+%\end{figure}
 
@@
 
-\begin{figure}[H]
-\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
+\begin{figure}
+\includegraphics[width=3.5in]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
  adhesion force measurements of ladybug beetle's (\emph{Coccinella
@@
 
-\begin{figure}[H]
-\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}
-\caption{\label{fig:Model}The capillary bridge model of a hairy adhesive pad. The hairs make contact
-with the substrate (hydrophilic or hydrophobic) in three modes: a) \emph{In air}, where the tarsal adhesive
-fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
-where the fluid bridges are fully surrounded by water; c)\emph{
-Underwater: bubble}, where part of the fluid bridges are
-inside the bubble while others are outside in water (see text for details). The corresponding
-ventral view contact images of the beetle's pad seen during adhesion experiments are shown on the right.}
-\end{figure}
-
 We modelled the hairy pad as an array of $N$ cylindrical rods of length,
@@
 to the pad circumference.
+
+\begin{figure}
+\includegraphics[width=3.5in]{Figure3-Model_schematic}
+\caption{\label{fig:Model}The capillary bridge model of a hairy adhesive pad. The hairs make contact
+with the substrate (hydrophilic or hydrophobic) in three modes: a) \emph{In air}, where the tarsal adhesive
+fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
+where the fluid bridges are fully surrounded by water; c)\emph{
+Underwater: bubble}, where part of the fluid bridges are
+inside the bubble while others are outside in water (see text for details). The corresponding
+ventral view contact images of the beetle's pad seen during adhesion experiments are shown on the right.}
+\end{figure}
 
@@
 versus distance for a single capillary bridge was calculated by Surface
-Evolver simulations\cite{RN206}  (see supplementary section S1 for details),
+Evolver simulations\citep{RN206}  (see supplementary section S1 for details),
 and used to obtain $F_{net}$ as a function of $d$ for each mode
@@
 in air and underwater due to its different contact angle and interfacial
-tension in each case. Using the Young-Dupr\textcyr{\`\cyre} equations
+tension in each case. Using the Young-Dupr\'{e} equations
 for each case of fluid-air, fluid-water and water-air interface, one
@@
 
-\begin{table}[H]
-\centering{}%
-\begin{tabular}{|l|c|}
+%\begin{table}
+%\centering{}%
+%\begin{tabular}{|l|c|}
+%\hline 
+%Property & Value\tabularnewline
+%\hline 
+%\hline 
+%Contact area fraction, $\alpha$ & 0.1\tabularnewline
+%\hline 
+%Hair aspect ratio, $L/D_{h}$ & 10\tabularnewline
+%\hline 
+%Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\tabularnewline
+%\hline 
+%Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\tabularnewline
+%\hline 
+%Tarsal fluid size parameter, $\phi_{f}$ & 2\tabularnewline
+%\hline 
+%Hydrophilic substrate & $\theta_{fa}=6\lyxmathsym{\textdegree}$, $\theta_{wa}=24\lyxmathsym{\textdegree}$\tabularnewline
+%\hline 
+%Hydrophobic substrate & $\theta_{fa}=50\lyxmathsym{\textdegree}$, $\theta_{wa}=120\lyxmathsym{\textdegree}$\tabularnewline
+%\hline 
+%\end{tabular}\caption{\label{tab:Model-parameters}Fixed parameter values corresponding to the pad's geometry, 
+%tarsal fluid and substrate wetting properties used in the capillary bridge model}
+%\end{table}
+
+\begin{table}[!t]
+\processtable{Fixed parameters corresponding to the pad's geometry, 
+tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
+{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
 \hline
-Property & Value\tabularnewline
+\TCH{Property} & \TCH{Value} \\
 \hline
-\hline 
-Contact area fraction, $\alpha$ & 0.1\tabularnewline
-\hline 
-Hair aspect ratio, $L/D_{h}$ & 10\tabularnewline
-\hline 
-Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\tabularnewline
-\hline 
-Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\tabularnewline
-\hline 
-Tarsal fluid size parameter, $\phi_{f}$ & 2\tabularnewline
-\hline 
-Hydrophilic substrate & $\theta_{fa}=6\lyxmathsym{\textdegree}$, $\theta_{wa}=24\lyxmathsym{\textdegree}$\tabularnewline
-\hline 
-Hydrophobic substrate & $\theta_{fa}=50\lyxmathsym{\textdegree}$, $\theta_{wa}=120\lyxmathsym{\textdegree}$\tabularnewline
-\hline 
-\end{tabular}\caption{\label{tab:Model-parameters}Fixed parameter values corresponding to the pad's geometry, 
-tarsal fluid and substrate wetting properties used in the capillary bridge model}
+Contact area fraction, $\alpha$ & 0.1\\
+Hair aspect ratio, $L/D_{h}$ & 10\\
+Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\\
+Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\\
+Tarsal fluid size parameter, $\phi_{f}$ & 2\\
+\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
+    & $\theta_{wa}=24\lyxmathsym{\textdegree}$\\
+\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=50\lyxmathsym{\textdegree}$\\
+    & $\theta_{wa}=120\lyxmathsym{\textdegree}$
+\end{tabular*}}{}
 \end{table}
@@
 
-\begin{figure}[H]
-\begin{minipage}[t]{0.5\columnwidth}%
-\includegraphics[scale=0.5]{Figure4a-Single_bridge_fd}
-
-\subcaption{Force-distance curves}%
-\end{minipage}\hfill{}%
-\begin{minipage}[t]{0.5\columnwidth}%
-\includegraphics[scale=0.5]{Figure4b-Single_bridge_force_contribution}
-
-\subcaption{Force contributions}%
-\end{minipage}\caption{\label{fig:Single-bridge}Simulation of normalised capillary force of a single liquid
+\begin{figure*}[!t]
+\centering
+\subfloat[Force-distance curves]{\includegraphics[width=3in]{Figure4a-Single_bridge_fd}\label{fig_first_case}}%
+\hskip3pc
+\subfloat[Force contributions]{\includegraphics[width=3in]{Figure4b-Single_bridge_force_contribution}\label{fig_second_case}}%
+\caption[]{Simulation of normalised capillary force of a single liquid
 bridge in contact with a substrate and pinned to a circular perimeter
@@
 6\textdegree{} and 150\textdegree{} are depicted.}
-\end{figure}
+\label{fig:Single-bridge}
+\end{figure*}
+
+%\begin{figure}
+%%\begin{minipage}[t]{0.5\columnwidth}%
+%\includegraphics[scale=0.5]{Figure4a-Single_bridge_fd}
+%
+%\subcaption{Force-distance curves}%
+%\end{minipage}\hfill{}%
+%\begin{minipage}[t]{0.5\columnwidth}%
+%\includegraphics[scale=0.5]{Figure4b-Single_bridge_force_contribution}
+%
+%\subcaption{Force contributions}%
+%\end{minipage}
+%\caption{\label{fig:Single-bridge}Simulation of normalised capillary force of a single liquid
+%bridge in contact with a substrate and pinned to a circular perimeter
+%on top. Fluid size parameter, $\phi_{f}=2$. Negative force values
+%represents attraction. a) Force-distance curves are shown for different
+%contact angles of the liquid with the substrate. b) Adhesion forces,
+%calculated from the minima of the corresponding force-distance curves,
+%are plotted as a function of contact angle with the substrate, together
+%with its Laplace and surface tension components (equation S1 in supplementary section).
+%Simulation snapshots of the liquid meniscus corresponding to angles
+%6\textdegree{} and 150\textdegree{} are depicted.}
+%\end{figure}
 
@@
 pressure and thus repulsion. Without pinning, the capillary forces
-would have shown high attractive forces on a hydrophilic substrate\cite{RN93}.
+would have shown high attractive forces on a hydrophilic substrate\citep{RN93}.
 
@@
 
-\begin{figure}[H]
-\centering{}\includegraphics{Figure5-Model_effect_of_substrate}\caption{\label{fig:Effect-of-substrate}Theoretical force-distance curves
+\begin{figure*}
+\centering
+\includegraphics[width=6in]{Figure5-Model_effect_of_substrate}\caption{\label{fig:Effect-of-substrate}Theoretical force-distance curves
 of a hairy pad on a hydrophilic and hydrophobic substrate in
@@
 bubble }contact for each substrate.}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[H]
-\includegraphics{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
+\begin{figure}
+\includegraphics[width=3.5in]{Figure-8-contact_angle_schematic}\caption{\label{fig:Oil-contact-images}Simulation snapshots of oil capillary
 meniscus in contact with untreated glass and PFOTS-coated glass in air and underwater conditions.
-The corresponding interfacial tension, \textgreek{g}, and contact
-angle, \ensuremath{\theta}, used to predict the ladybug's adhesion
+The corresponding interfacial tension, $\gamma$, and contact
+angle, $\theta$, used to predict the ladybug's adhesion
 are labelled for each case.}
@@
 \subsection{Adhesion of a hairy pad: Effect of the air bubble volume}
-
-\begin{figure}[H]
-\includegraphics{Figure7-Model_effect_of_bubble_volume}\caption{\label{fig:Effect-of-bubble}Normalised adhesion force of a hairy
-pad as a function of bubble volume, $\hat{V}_{b}$, for the
-\emph{underwater: bubble} contact mode. Adhesion forces are calculated
-from the minima of the respective force-distance curves. Negative
-force value represents attraction. Pad to hair diameter ratio ($D_{p}/D_{h}$)
-is kept fixed. Highlighted regions represent entrapment of all hairs
-within the bubble.}
-\end{figure}
 
@@
 substrate as the volume decreases.
+
+\begin{figure}
+\includegraphics[width=3.5in]{Figure7-Model_effect_of_bubble_volume}\caption{\label{fig:Effect-of-bubble}Normalised adhesion force of a hairy
+pad as a function of bubble volume, $\hat{V}_{b}$, for the
+\emph{underwater: bubble} contact mode. Adhesion forces are calculated
+from the minima of the respective force-distance curves. Negative
+force value represents attraction. Pad to hair diameter ratio ($D_{p}/D_{h}$)
+is kept fixed. Highlighted regions represent entrapment of all hairs
+within the bubble.}
+\end{figure}
+
 %change 1e6 to 1 10^6%
@@
 
-\begin{figure}[H]
-\includegraphics[scale=0.5]{Figure6-Model_effect_of_hair_size}
+\begin{figure*}
+\centering
+\includegraphics[width=6in]{Figure6-Model_effect_of_hair_size}
 \caption{\label{fig:Effect-of-hair}Normalised adhesion force of a hairy pad on a hydrophilic and hydrophobic substrate as a function of
@@
 volume are kept fixed. All lengths are scaled relative to $D_{p}$.}
-\end{figure}
+\end{figure*}
 The tarsal hairs on a ladybug's adhesive pad terminate in various shapes, such as ``discoidal''
@@
 with the ``contact splitting'' theory, which predicts higher adhesion
-when the contact is split into many small contact points\cite{RN24}.
+when the contact is split into many small contact points\citep{RN24}.
 Reducing the hair diameter results in two competing effects: 1) capillary
@@
 to a hydrophobic substrate even without a bubble trapped around its
-tarsal hairs. A previous study\cite{RN87} proposed that an air bubble
+tarsal hairs. A previous study\citep{RN87} proposed that an air bubble
 is necessary for underwater attachment in terrestrial beetles. This is, however,
@@
 To some extent, the findings could be extended to other animals relying on oily
-secretions for adhesion. For example, ants are known to possess smooth adhesive pads which secrete a fluid containing oily substances \cite{RN201}.
-It has been reported that some ants show similar adhesion on hydrophobic substrates under wet and dry conditions \cite{RN213},
+secretions for adhesion. For example, ants are known to possess smooth adhesive pads which secrete a fluid containing oily substances \citep{RN201}.
+It has been reported that some ants show similar adhesion on hydrophobic substrates under wet and dry conditions \citep{RN213},
 similar to what we see in a ladybug. This observation can again be explained by a capillary model as before. Recent experiments on
@@
 underwater while they show little adhesion to the same substrate in
-air\cite{RN199,RN15}. Geckos are thought to rely on van der Waals
-forces via dry contact with the substrate \cite{RN202}, although
+air\citep{RN199,RN15}. Geckos are thought to rely on van der Waals
+forces via dry contact with the substrate \citep{RN202}, although
 recent observations of phospholipid footprints left behind walking
-geckos \cite{RN205} could change that picture. Since geckos adhere
+geckos \citep{RN205} could change that picture. Since geckos adhere
 poorly to PTFE (surface energy $\sim$ 20 mN m\protect\textsuperscript{-1}) one can
@@
 lower adhesion in air than underwater for PTFE. We, thus, propose
-that the underwater experiments performed on geckos \cite{RN199,RN15}
+that the underwater experiments performed on geckos \citep{RN199,RN15}
 indicate a capillary contribution to gecko adhesion.
-Previous studies on gecko adhesion have attributed capillary effects to be a result of water monolayers adsorbed from ambient humid air onto the spatuale hair tips \cite{RN197, RN203, RN218}.
+Previous studies on gecko adhesion have attributed capillary effects to be a result of water monolayers adsorbed from ambient humid air onto the spatuale hair tips \citep{RN197, RN203, RN218}.
 We however emphasize that capillary contribution in gecko adhesion could rather be a result of its setal phospholipid layer rather than water.
-The previously reported influence of humidity on gecko adhesion \cite{RN197} could possibly be an effect of change in surface tension of the oily phospholipid layer at different humidity, which will in-turn influence the capillary adhesion force.
-We suggest performing single seta adhesion force tests similar to \citet{RN202}
+The previously reported influence of humidity on gecko adhesion \citep{RN197} could possibly be an effect of change in surface tension of the oily phospholipid layer at different humidity, which will in-turn influence the capillary adhesion force.
+We suggest performing single seta adhesion force tests similar to \citep{RN202}
 using a hydrophilic and fluorinated probe in air and underwater conditions. 
@@
 
-\begin{figure}[H]
-\includegraphics{Figure-9-Gecko_comparison}\caption{\label{fig:Comparison-with-model}Whole animal adhesion force of geckos
+\begin{figure}
+\centering
+\includegraphics[width=3.5in]{Figure-9-Gecko_comparison}\caption{\label{fig:Comparison-with-model}Whole animal adhesion force of geckos
 on various substrates. Experimental shear adhesion values are reproduced
-from \citet{RN15}. Normal adhesion forces for each gecko
+from \citep{RN15}. Normal adhesion forces for each gecko
 toe are theoretically estimated from the capillary bridge model, with
@@
 are 50\textdegree , 85\textdegree , 94\textdegree{} and 97\textdegree{}
-respectively, as reported in \citet{RN15}.}
+respectively, as reported in \citep{RN15}.}
 \end{figure}
@@
 have to cope with all kinds of surfaces including rough ones.
-Previous studies \cite{RN136} have shown that substrate roughness
+Previous studies \citep{RN136} have shown that substrate roughness
 is a more dominant parameter than substrate chemistry in controlling
@@
 In our study, we have only considered normal adhesive forces, but insects like beetles in general rely on friction or shear forces during locomotion.
-Friction force usually correlates directly with the normal force, which is probably why previously reported shear adhesion forces of the dock beetle \cite{RN87} follow a similar qualitative trend as our normal adhesion force measurements on the ladybug beetle in both air and underwater conditions.
+Friction force usually correlates directly with the normal force, which is probably why previously reported shear adhesion forces of the dock beetle \citep{RN87} follow a similar qualitative trend as our normal adhesion force measurements on the ladybug beetle in both air and underwater conditions.
 However, the details of the interplay between friction and normal adhesion forces in animals is an open question and is beyond the scope of this paper.
@@
 similar argument also explains previously reported underwater adhesion force measurements
-in geckos \cite{RN15}, which suggests the possibility of capillary
+in geckos \citep{RN15}, which suggests the possibility of capillary
 contributions to gecko adhesion mediated by an oil-like phospholipid layer. Future studies should characterise
@@
 
-\section{Acknowledgements}
+%\section{Acknowledgements}
 
-We are grateful to Prof. Dr. Eduard Arzt and Dr. Ren\textcyr{\`\cyre} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for fruitful discussions.
+\ack{We are grateful to Prof. Dr. Eduard Arzt and Dr. Ren\' {e} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for fruitful discussions.}
 
-\section{Competing interests}
-The authors declare no competing or financial interests.
+%\section{Competing interests}
+\competing{The authors declare no competing or financial interests.}
 
 %\section{Data availability}
-%Data are available from the Dryad digital repository. %CHECK THIS%
+%\data{Data are available from the Dryad digital repository.} %CHECK THIS%
 
-\section{Funding}
-This work was supported by the \emph{Deutsche Forschungsgemeinschaft}
-(Grant number: PI 1351/2-1) and the \emph{Max Planck Graduate Center} with the \emph{Johannes Gutenberg-Universit\"{a}t Mainz} (MPGC).
+%\section{Funding}
+\funding{This work was supported by the \emph{Deutsche Forschungsgemeinschaft}
+(Grant number: PI 1351/2-1) and the \emph{Max Planck Graduate Center} with the \emph{Johannes Gutenberg-Universit\"{a}t Mainz} (MPGC).}
 
 \bibliography{references}
+%\begin{thebibliography}{}
+%
+%\bibitem{RN24}
+%{\bf Arzt, E., S.~Gorb, and R.~Spolenak.}  2003.
+%\textit{ Proc Natl Acad Sci U S A}  {\bf 100} (19):10603--6.
+%
+%\bibitem{RN221}
+%{\bf Attygalle, A.~B., D.~J. Aneshansley, J.~Meinwald, and T.~Eisner.}  2000.
+%\textit{ Zoology}  {\bf 103} (1/2):1--6.
+%
+%\bibitem{RN202}
+%{\bf Autumn, K., Metin Sitti, Yiching~A. Liang, Anne~M. Peattie, Wendy~R.
+%  Hansen, Simon Sponberg, Thomas~W. Kenny, Ronald Fearing, Jacob~N.
+%  Israelachvili, and Robert~J. Full.}  2002.
+%\textit{ Proceedings of the National Academy of Sciences}  {\bf 99} (19):12252.
+%
+%\bibitem{RN206}
+%{\bf Brakke, K.~A.}  1992.
+%\textit{ Experiment. Math.} {\bf 1} (2):141--165.
+%
+%\bibitem{RN19}
+%{\bf Bullock, J.~M., and W.~Federle.}  2009.
+%\textit{ J Exp Bio}  {\bf 212} (Pt 12):1876--88.
+%
+%\bibitem{RN79}
+%{\bf Bullock, J.~M., and W.~Federle.}  2011.
+%\textit{ Naturwissenschaften}  {\bf 98} (5):381--7.
+%
+%\bibitem{Chen:2014}
+%{\bf Chen, Y., Ming-Chih Shih, Ming-Huang Wu, En-Cheng Yang, and Kai-Jung Chi.}
+%   2014.
+%\textit{ Journal of The Royal Society Interface}  {\bf 11} (97).
+%
+%\bibitem{Coddington:1991}
+%{\bf Coddington, J.~A., and H~W Levi.}  1991.
+%\textit{ Annual Review of Ecology and Systematics}  {\bf 22}:565--592.
+%
+%\bibitem{RN93}
+%{\bf De~Souza, E.~J., M.~Brinkmann, C.~Mohrdieck, and E.~Arzt.}  2008.
+%\textit{ Langmuir}  {\bf 24} (16):8813--8820.
+%
+%\bibitem{RN71}
+%{\bf Dirks, J.~H.}  2014.
+%\textit{ Beilstein J Nanotechnol}  {\bf 5}:1160--6.
+%
+%\bibitem{RN136}
+%{\bf England, M.~W., Tomoya Sato, Makoto Yagihashi, Atsushi Hozumi,
+%  Stanislav~N. Gorb, and Elena~V. Gorb.}  2016.
+%\textit{ Beilstein journal of nanotechnology}  {\bf 7}:1471--1479.
+%
+%\bibitem{RN20}
+%{\bf Federle, W.}  2006.
+%\textit{ J Exp Biol}  {\bf 209} (Pt 14):2611--21.
+%
+%\bibitem{RN201}
+%{\bf Federle, W., Mathis Riehle, Adam~S.G. Curtis, and Robert~J. Full.}  2002.
+%\textit{ Integrative and Comparative Biology}  {\bf 42} (6):1100--1106.
+%
+%\bibitem{RN96}
+%{\bf Geiselhardt, S.~F., Sven Geiselhardt, and Klaus Peschke.}  2009.
+%\textit{ Chemoecology}  {\bf 19} (4):185.
+%
+%\bibitem{RN145}
+%{\bf Heepe, L., Dennis~S. Petersen, Lisa Tölle, Jonas~O. Wolff, and
+%  Stanislav~N. Gorb.}  2016.
+%\textit{ Applied Physics A}  {\bf 123} (1):34.
+%
+%\bibitem{RN87}
+%{\bf Hosoda, N., and S.~N. Gorb.}  2012.
+%\textit{ Proc Biol Sci}  {\bf 279} (1745):4236--42.
+%
+%\bibitem{RN205}
+%{\bf Hsu, P.~Y., Liehui Ge, Xiaopeng Li, Alyssa~Y. Stark, Chrys Wesdemiotis,
+%  Peter~H. Niewiarowski, and Ali Dhinojwala.}  2012.
+%\textit{ Journal of The Royal Society Interface}  {\bf 9} (69):657--664.
+%
+%\bibitem{RN197}
+%{\bf Huber, G., Hubert Mantz, Ralph Spolenak, Klaus Mecke, Karin Jacobs,
+%  Stanislav~N. Gorb, and Eduard Arzt.}  2005.
+%\textit{ Proceedings of the National Academy of Sciences of the United States
+%  of America}  {\bf 102} (45):16293--16296.
+%
+%\bibitem{RN222}
+%{\bf Ishii, S.}  1987.
+%\textit{ Applied Entomology and Zoology}  {\bf 22} (2):222--228.
+%
+%\bibitem{Kang:2020}
+%{\bf Kang, V., Robin~T. White, Simon Chen, and Walter Federle.}  2020.
+%\textit{ bioRxiv}  {\bf }.
+%
+%\bibitem{RN203}
+%{\bf Kim, T.~W., and Bharat Bhushan.}  2008.
+%\textit{ Journal of The Royal Society Interface}  {\bf 5} (20):319--327.
+%
+%\bibitem{RN155}
+%{\bf Langer, M.~G., J.~P. Ruppersberg, and S.~Gorb.}  2004.
+%\textit{ Proceedings of the Royal Society of London. Series B: Biological
+%  Sciences}  {\bf 271} (1554):2209--2215.
+%
+%\bibitem{RN218}
+%{\bf Mitchell, C.~T., Cem~Balda Dayan, Dirk-M. Drotlef, Metin Sitti, and
+%  Alyssa~Y. Stark.}  2020.
+%\textit{ Scientific Reports}  {\bf 10} (1):19748.
+%
+%\bibitem{RN108}
+%{\bf Peisker, H., and Stanislav~N. Gorb.}  2012.
+%\textit{ The Journal of Experimental Biology}  {\bf 215} (8):1266--1271.
+%
+%\bibitem{Seymour:2013}
+%{\bf Seymour, R.~S., and Philip G.~D. Matthews.}  2013.
+%\textit{ Journal of Experimental Biology}  {\bf 216} (2):164--170.
+%
+%\bibitem{RN15}
+%{\bf Stark, A.~Y., I.~Badge, N.~A. Wucinich, T.~W. Sullivan, P.~H.
+%  Niewiarowski, and A.~Dhinojwala.}  2013.
+%\textit{ Proc Natl Acad Sci U S A}  {\bf 110} (16):6340--5.
+%
+%\bibitem{RN199}
+%{\bf Stark, A.~Y., Daniel~M. Dryden, Jeffrey Olderman, Kelly~A. Peterson,
+%  Peter~H. Niewiarowski, Roger~H. French, and Ali Dhinojwala.}  2015.
+%\textit{ Journal of The Royal Society Interface}  {\bf 12} (108):20150464.
+%
+%\bibitem{RN213}
+%{\bf Stark, A.~Y., and Stephen~P. Yanoviak.}  2018.
+%\textit{ Royal Society open science}  {\bf 5} (11):181540--181540.
+%
+%\bibitem{RN59}
+%{\bf Stork, N.~E.}  1980.
+%\textit{ The Journal of Experimental Biology}  {\bf 88} (1):91.
+%
+%\bibitem{Williams:1982}
+%{\bf Williams, E., and J.A. Peterson.}  1982.
+%\textit{ Science}  {\bf 215}:1509--1511.
+%
+%\end{thebibliography}
+
+%\bibitem{RN198}
+%{\bf Hooke, R.}  1665.
+%\newblock {\em Micrographia, or, Some physiological descriptions of minute
+%  bodies made by magnifying glasses : with observations and inquiries
+%  thereupon}.
+%\newblock The Royal Society.
 

### 2021-07-14 source/jeb_tex/manuscript.tex
changed bibiliography style file to match reference formatting
fixed citations

@@
 One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}.
-This has been shown in a recent study by \citep{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
+This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
 Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact.
@@
 The previously reported influence of humidity on gecko adhesion \citep{RN197} could possibly be an effect of change in surface tension of the oily phospholipid layer at different humidity, which will in-turn influence the capillary adhesion force.
-We suggest performing single seta adhesion force tests similar to \citep{RN202}
+We suggest performing single seta adhesion force tests similar to \citet{RN202}
 using a hydrophilic and fluorinated probe in air and underwater conditions. 
@@
 on various substrates. Experimental shear adhesion values are reproduced
-from \citep{RN15}. Normal adhesion forces for each gecko
+from \citet{RN15}. Normal adhesion forces for each gecko
 toe are theoretically estimated from the capillary bridge model, with
@@
 are 50\textdegree , 85\textdegree , 94\textdegree{} and 97\textdegree{}
-respectively, as reported in \citep{RN15}.}
+respectively, as reported in \citet{RN15}.}
 \end{figure}
-
+%CHANGE REFERENCE FORMAT IN PLOT
 We have so far limited our analysis to only smooth substrates. Of course insects
@@
 \bibliography{references}
-%\begin{thebibliography}{}
-%
-%\bibitem{RN24}
-%{\bf Arzt, E., S.~Gorb, and R.~Spolenak.}  2003.
-%\textit{ Proc Natl Acad Sci U S A}  {\bf 100} (19):10603--6.
-%
-%\bibitem{RN221}
-%{\bf Attygalle, A.~B., D.~J. Aneshansley, J.~Meinwald, and T.~Eisner.}  2000.
-%\textit{ Zoology}  {\bf 103} (1/2):1--6.
-%
-%\bibitem{RN202}
-%{\bf Autumn, K., Metin Sitti, Yiching~A. Liang, Anne~M. Peattie, Wendy~R.
-%  Hansen, Simon Sponberg, Thomas~W. Kenny, Ronald Fearing, Jacob~N.
-%  Israelachvili, and Robert~J. Full.}  2002.
-%\textit{ Proceedings of the National Academy of Sciences}  {\bf 99} (19):12252.
-%
-%\bibitem{RN206}
-%{\bf Brakke, K.~A.}  1992.
-%\textit{ Experiment. Math.} {\bf 1} (2):141--165.
-%
-%\bibitem{RN19}
-%{\bf Bullock, J.~M., and W.~Federle.}  2009.
-%\textit{ J Exp Bio}  {\bf 212} (Pt 12):1876--88.
-%
-%\bibitem{RN79}
-%{\bf Bullock, J.~M., and W.~Federle.}  2011.
-%\textit{ Naturwissenschaften}  {\bf 98} (5):381--7.
-%
-%\bibitem{Chen:2014}
-%{\bf Chen, Y., Ming-Chih Shih, Ming-Huang Wu, En-Cheng Yang, and Kai-Jung Chi.}
-%   2014.
-%\textit{ Journal of The Royal Society Interface}  {\bf 11} (97).
-%
-%\bibitem{Coddington:1991}
-%{\bf Coddington, J.~A., and H~W Levi.}  1991.
-%\textit{ Annual Review of Ecology and Systematics}  {\bf 22}:565--592.
-%
-%\bibitem{RN93}
-%{\bf De~Souza, E.~J., M.~Brinkmann, C.~Mohrdieck, and E.~Arzt.}  2008.
-%\textit{ Langmuir}  {\bf 24} (16):8813--8820.
-%
-%\bibitem{RN71}
-%{\bf Dirks, J.~H.}  2014.
-%\textit{ Beilstein J Nanotechnol}  {\bf 5}:1160--6.
-%
-%\bibitem{RN136}
-%{\bf England, M.~W., Tomoya Sato, Makoto Yagihashi, Atsushi Hozumi,
-%  Stanislav~N. Gorb, and Elena~V. Gorb.}  2016.
-%\textit{ Beilstein journal of nanotechnology}  {\bf 7}:1471--1479.
-%
-%\bibitem{RN20}
-%{\bf Federle, W.}  2006.
-%\textit{ J Exp Biol}  {\bf 209} (Pt 14):2611--21.
-%
-%\bibitem{RN201}
-%{\bf Federle, W., Mathis Riehle, Adam~S.G. Curtis, and Robert~J. Full.}  2002.
-%\textit{ Integrative and Comparative Biology}  {\bf 42} (6):1100--1106.
-%
-%\bibitem{RN96}
-%{\bf Geiselhardt, S.~F., Sven Geiselhardt, and Klaus Peschke.}  2009.
-%\textit{ Chemoecology}  {\bf 19} (4):185.
-%
-%\bibitem{RN145}
-%{\bf Heepe, L., Dennis~S. Petersen, Lisa Tölle, Jonas~O. Wolff, and
-%  Stanislav~N. Gorb.}  2016.
-%\textit{ Applied Physics A}  {\bf 123} (1):34.
-%
-%\bibitem{RN87}
-%{\bf Hosoda, N., and S.~N. Gorb.}  2012.
-%\textit{ Proc Biol Sci}  {\bf 279} (1745):4236--42.
-%
-%\bibitem{RN205}
-%{\bf Hsu, P.~Y., Liehui Ge, Xiaopeng Li, Alyssa~Y. Stark, Chrys Wesdemiotis,
-%  Peter~H. Niewiarowski, and Ali Dhinojwala.}  2012.
-%\textit{ Journal of The Royal Society Interface}  {\bf 9} (69):657--664.
-%
-%\bibitem{RN197}
-%{\bf Huber, G., Hubert Mantz, Ralph Spolenak, Klaus Mecke, Karin Jacobs,
-%  Stanislav~N. Gorb, and Eduard Arzt.}  2005.
-%\textit{ Proceedings of the National Academy of Sciences of the United States
-%  of America}  {\bf 102} (45):16293--16296.
-%
-%\bibitem{RN222}
-%{\bf Ishii, S.}  1987.
-%\textit{ Applied Entomology and Zoology}  {\bf 22} (2):222--228.
-%
-%\bibitem{Kang:2020}
-%{\bf Kang, V., Robin~T. White, Simon Chen, and Walter Federle.}  2020.
-%\textit{ bioRxiv}  {\bf }.
-%
-%\bibitem{RN203}
-%{\bf Kim, T.~W., and Bharat Bhushan.}  2008.
-%\textit{ Journal of The Royal Society Interface}  {\bf 5} (20):319--327.
-%
-%\bibitem{RN155}
-%{\bf Langer, M.~G., J.~P. Ruppersberg, and S.~Gorb.}  2004.
-%\textit{ Proceedings of the Royal Society of London. Series B: Biological
-%  Sciences}  {\bf 271} (1554):2209--2215.
-%
-%\bibitem{RN218}
-%{\bf Mitchell, C.~T., Cem~Balda Dayan, Dirk-M. Drotlef, Metin Sitti, and
-%  Alyssa~Y. Stark.}  2020.
-%\textit{ Scientific Reports}  {\bf 10} (1):19748.
-%
-%\bibitem{RN108}
-%{\bf Peisker, H., and Stanislav~N. Gorb.}  2012.
-%\textit{ The Journal of Experimental Biology}  {\bf 215} (8):1266--1271.
-%
-%\bibitem{Seymour:2013}
-%{\bf Seymour, R.~S., and Philip G.~D. Matthews.}  2013.
-%\textit{ Journal of Experimental Biology}  {\bf 216} (2):164--170.
-%
-%\bibitem{RN15}
-%{\bf Stark, A.~Y., I.~Badge, N.~A. Wucinich, T.~W. Sullivan, P.~H.
-%  Niewiarowski, and A.~Dhinojwala.}  2013.
-%\textit{ Proc Natl Acad Sci U S A}  {\bf 110} (16):6340--5.
-%
-%\bibitem{RN199}
-%{\bf Stark, A.~Y., Daniel~M. Dryden, Jeffrey Olderman, Kelly~A. Peterson,
-%  Peter~H. Niewiarowski, Roger~H. French, and Ali Dhinojwala.}  2015.
-%\textit{ Journal of The Royal Society Interface}  {\bf 12} (108):20150464.
-%
-%\bibitem{RN213}
-%{\bf Stark, A.~Y., and Stephen~P. Yanoviak.}  2018.
-%\textit{ Royal Society open science}  {\bf 5} (11):181540--181540.
-%
-%\bibitem{RN59}
-%{\bf Stork, N.~E.}  1980.
-%\textit{ The Journal of Experimental Biology}  {\bf 88} (1):91.
-%
-%\bibitem{Williams:1982}
-%{\bf Williams, E., and J.A. Peterson.}  1982.
-%\textit{ Science}  {\bf 215}:1509--1511.
-%
-%\end{thebibliography}
-
-%\bibitem{RN198}
-%{\bf Hooke, R.}  1665.
-%\newblock {\em Micrographia, or, Some physiological descriptions of minute
-%  bodies made by magnifying glasses : with observations and inquiries
-%  thereupon}.
-%\newblock The Royal Society.
 

### 2021-08-02 source/jeb_tex/manuscript.tex
sensitivity analysis and LMM analysis done
figures updated

@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=6in]{Figure6-Model_effect_of_hair_size}
+\begin{figure}
+%\centering
+\includegraphics[width=3.5in]{Figure6-Model_effect_of_hair_size}
 \caption{\label{fig:Effect-of-hair}Normalised adhesion force of a hairy pad on a hydrophilic and hydrophobic substrate as a function of
@@
 volume are kept fixed. All lengths are scaled relative to $D_{p}$.}
-\end{figure*}
+\end{figure}
+
 The tarsal hairs on a ladybug's adhesive pad terminate in various shapes, such as ``discoidal''

### 2021-08-02 source/jeb_tex/supplementary.tex
Sensitivity analysis included in supplementary info

--- 2021-05-11 source/tex/supplementary.tex
@@
 
+\section{Capillary bridge model: Sensitivity analysis}
+
+Sensitivity analysis was performed using the one-at-a-time (OAT) method. Dimensionless model parameters were initially set to correspond to the ladybug's case, as given by,
+contact area fraction ($\alpha=0.1$), pad to hair diameter ratio ($D_p/D_h=50$), hair aspect ratio ($L/D_{h}=10$), water surface tension ratio ($\gamma_{wa}/\gamma_{fa}=3$),
+tarsal fluid-water interfacial tension ratio ($\gamma_{fw}/\gamma_{fa}=2$), tarsal fluid size parameter ($\phi_{f}=2$), bubble size parameter ($\phi_{b}=1.6$).
+Substrate contact angles were kept fixed (same as in main text).
+Each parameter was varied within a particular range, one at a time, and the corresponding adhesion forces \emph{in air} (F\textsubscript{a}),   \emph{underwater: no bubble} (F\textsubscript{w}) and \emph{underwater: bubble} (F\textsubscript{b}) were calculated.
+Linear least square regression was performed to quantify the relative change in adhesion for each contact mode with respect to the varied parameter.
+Here, F\textsubscript{w}/F\textsubscript{a} and F\textsubscript{b}/F\textsubscript{a} were taken to be the model output.
+Slope and R\textsuperscript{2} values for each case are reported below (Table \ref{tab:Sens-anal}).
+
+\begin{table}[H]
+\begin{tabular}{|l|c|l|l|l|l|l|}
+\hline
+\multirow{2}{*}{\textbf{Parameter}} & \multirow{2}{*}{\textbf{Range}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Substrate}}} & \multicolumn{2}{c|}{\textbf{F\textsubscript{w}/F\textsubscript{a}}}                                    & \multicolumn{2}{c|}{\textbf{F\textsubscript{b}/F\textsubscript{a}}}                                    \\ \cline{4-7}
+                                    &                                 & \multicolumn{1}{c|}{}                                    & \multicolumn{1}{c|}{\textbf{slope}} & \multicolumn{1}{c|}{\textbf{R\textsuperscript{2}}} & \multicolumn{1}{c|}{\textbf{slope}} & \multicolumn{1}{c|}{\textbf{R\textsuperscript{2}}} \\ \hline
+\multirow{2}{*}{$\alpha$}              & \multirow{2}{*}{0.05, 0.3}      & Hydrophilic                                              & 3.03E-18                                  & 1.52E-03                               & 2.30E-01                                  & 7.72E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & -9.69E-17                                 & 3.03E-03                               & -9.40E-01                                 & 7.72E-01                               \\ \hline
+\multirow{2}{*}{$D_p/D_h$}             & \multirow{2}{*}{30.0, 60.0}     & Hydrophilic                                              & -8.83E-20                                 & 1.48E-01                               & 1.28E-02                                  & 9.73E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & -5.65E-18                                 & 1.48E-01                               & -1.51E-02                                 & 9.82E-01                               \\ \hline
+\multirow{2}{*}{$L/D_{h}$}         & \multirow{2}{*}{8.0, 15.0}      & Hydrophilic                                              & 0.00E+00                                  & 0.00E+00                               & -5.27E-02                                 & 9.11E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 0.00E+00                                  & 0.00E+00                               & 5.41E-02                                  & 8.66E-01                               \\ \hline
+\multirow{2}{*}{$\gamma_{wa}/\gamma_{fa}$}              & \multirow{2}{*}{2.5, 3.5}       & Hydrophilic                                              & -2.01E-01                                 & 8.57E-01                               & -2.43E-01                                 & 9.43E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 4.11E-02                                  & 1.00E+00                               & 6.87E-02                                  & 1.00E+00                               \\ \hline
+\multirow{2}{*}{$\gamma_{fw}/\gamma_{fa}$}              & \multirow{2}{*}{1.5, 2.5}       & Hydrophilic                                              & 2.01E-01                                  & 8.62E-01                               & 1.90E-01                                  & 8.94E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 5.56E-01                                  & 1.00E+00                               & 1.57E-01                                  & 1.00E+00                               \\ \hline
+\multirow{2}{*}{$\phi_{f}$}             & \multirow{2}{*}{1.7, 2.2}       & Hydrophilic                                              & 1.29E-02                                  & 4.52E-01                               & 6.18E-02                                  & 7.94E-02                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 7.67E-02                                  & 9.84E-01                               & -3.06E-01                                 & 9.66E-01                               \\ \hline
+\multirow{2}{*}{$\phi_{b}$}             & \multirow{2}{*}{1.2, 1.8}       & Hydrophilic                                              & 0.00E+00                                  & 0.00E+00                               & -1.14E+00                                 & 8.85E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 0.00E+00                                  & 0.00E+00                               & 1.46E+00                                  & 9.78E-01                               \\ \hline
+\end{tabular}
+\caption{Sensitivity analysis \label{tab:Sens-anal}}
+\end{table}
+
 \section{Supplementary video files}

### 2021-08-03 source/jeb_tex/manuscript.tex
Linear mixed model results included in supplementary info.
Reviewer 1 and 3 responded and changes made in MS.
Reviewer 2 typo suggestions included

@@
 
-\corres{(\email{endlein01@mpip-mainz.mpg.de}; \email{xxxx@xxxx.xxx.xx})}
+\corres{(\email{endlein01@mpip-mainz.mpg.de})}
 
@@
 
+\section{Summary statement}
+
+Fluid-mediated adhesion seen in animals such as ladybug beetles allows them to attach to surfaces not just in air but also in underwater conditions.
+
 \section{Introduction}
@@
 Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces.
-However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate.
+However, underwater adhesion mediated by secreted liquids requires the displacement of the water at the interface first and a spreading of the fluid on the substrate.
 One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}.
@@
 bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
-investigate the air bubble's role in underwater adhesion. Adhesion force
+investigate the air bubble's role in underwater adhesion. Adhesion forces
 for each of the labelled contact modes were compared for both substrates.
 
-\subsection{Material and Methods}
+\subsection{Materials and Methods}
 
@@
 
-The adult seven-spotted male ladybug beetles (\emph{Coccinella septempuctata})
+Adult seven-spotted male ladybug beetles (\emph{Coccinella septempuctata})
 were purchased from Katz Biotech (Baruth, Germany). The beetles were housed in a plastic box filled with leaves,
@@
 The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments.
-One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate.
+The front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate.
 Each leg of a male ladybug beetle has two hairy adhesive pads.
@@
 A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test.
-After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.
+After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack from its claws and tibia using a pair of tweezers without harming it and set free.
 
@@
 the vertical force sensor. Beam deflection was calibrated using 4
-different known weights to get the corresponding force. A
+different known weights (range: 2 - 90 mg) to get the corresponding force (resolution = 5 \textmu N). A
 3D printed substrate holder (22 $\times$ 22 $\times$ 8 mm) was glued to the end of the bending beam.
@@
 The vertical and lateral piezos were used simultaneously to perform approach-retract
-adhesion tests with the substrate to get the pull-off force. However,
+adhesion tests with the substrate to measure the pull-off force. However,
 instead of a simple down-up motion, an additional 100 \textmu m lateral sliding motion in the proximal direction 
 was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \citep{RN19}.
-A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped further contact
+A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped maximize the hair contact
 with the surface. Next, a short pause (1 s) removed any
 viscoelastic effects before finally retracting the leg away from the
-substrate. All approach, retract and lateral slide motion was done
+substrate. All approach, retract and lateral slide motion were done
 at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
@@
 substrate holder (roughly 3 mm water level). The beetle was then partially 
-submerged to allow underwater contact of the pad with the substrate. In order to achieve contact without
+submerged to allow underwater contact of the pad with the substrate (immersion time $\sim$ 15 mins). In order to achieve contact without
 a trapped air bubble, the water was first degassed separately in a vacuum chamber
-at 10 mbar pressure for 3 hours and then pipetted into the holder immediately. Before the experiments,
+at 10 mbar pressure for 3 hours and then pipetted into the holder immediately.
+The beetle was subsequently immersed, where, the trapped air bubble within the pad dissolves into the degassed water in less than 5 mins, as verified by the ventral view contact image.
+Before the experiments,
 the pad was brought into contact with the clean dry surface 10 times repeatedly 
@@
 with the substrate. This background data was then subtracted from
-a typical force data with substrate contact to correct for the external
+a typical force curve with substrate contact to correct for the external
 surface tension effects. The pull-off force was subsequently calculated
@@
 Student t-test were done for post-hoc analysis and their corresponding p-value and Common Language
-Effect Size (CLES) are reported. Shapiro-Wilk test was done for each
+Effect Size (CLES) are reported. Shapiro-Wilk tests were done for each
 data set to verify a normal distribution of its residuals and Levene's
@@
 glass. The chamber was placed under 100 mbar pressure for 10 min for
-the CVD process. Finally, the substrate was annealed at 150\textcelsius{}
+the CVD process. Finally, the substrate was annealed at 150 \textcelsius{}
 for 3 hours. Henceforth, we refer to the hydrophilic untreated glass substrate 
@@
 The surface chemistry was characterised by dynamic contact angle
-measurements, performed with a contact angle goniometer (\emph{OCA 35, DataPhysics Instruments GmbH, Germany})
+measurements, performed with a contact angle goniometer (\emph{OCA 35, DataPhysics Instruments GmbH, Germany}).
 The substrate's wetting towards a polar (Milli-Q water) and a non-polar (n-hexadecane) liquid was tested. Advancing
@@
 
-In air, adhesion forces of the distal pad of ladybug beetle against
+In air, adhesion forces of the distal pad of the ladybug beetles against
 glass and PFOTS were similar, i.e. no significant differences were
@@
 clear why such a contact occurs, there can be two possible reasons.
-First, the hairs could get bundled due to a small air meniscus within
-the hairs, resulting in their disorientation. Second, a thin water
+First, the hairs could get bundled due to a small air bubble trapped within
+them which might not have completely dissolved away in the water.
+The presence of this air-water meniscus could thus lead to elasto-capillary bundling of the hairs, resulting in their disorientation. Second, a thin water
 layer at the substrate interface might not be drained out to allow
@@
 to be perfectly rigid, for simplicity. The tip of each hair has a tarsal 
-adhesive fluid of volume, $V_{f}$, mediating contact with the substrate.
+adhesive fluid of volume $V_{f}$, mediating contact with the substrate.
 The fluid is pinned to the circumference of the hair and forms a capillary
@@
 
-The capillary force, $f$, is the sum of two contributions: surface
-tension and Laplace pressure. Force
-versus distance for a single capillary bridge was calculated by Surface
-Evolver simulations\citep{RN206}  (see supplementary section S1 for details),
+The capillary force, $f$, is the sum of two contributions: Laplace pressure and  surface
+tension, as given by:
+\begin{equation}
+f=\varDelta P_{laplace}A_{_{bottom}}+2\pi R_{bottom}\gamma\sin\theta\label{eq:f_bridge}
+\end{equation}
+
+Here, $\varDelta P_{laplace}$ is the Laplace pressure of the equilibrium
+capillary bridge, $\theta$ is the contact angle, $A_{bottom}$ is the contact area of the capillary
+bridge with the substrate at bottom and $R_{bottom}$ is the corresponding
+radius of contact. Unlike previous analytical treatments \citep{RN203, RN318}, force versus distance for a single capillary bridge was calculated by Surface
+Evolver simulations \citep{RN206, RN93},
 and used to obtain $F_{net}$ as a function of $d$ for each mode
-of contact. The adhesion force of the complete hairy pad system was
+of contact  (see supplementary section S1 for details). The adhesion force of the complete hairy pad system was
 then obtained from the minima of $F_{net}$, where negative force
@@
 is the interfacial tension of the tarsal adhesive fluid with water.
-
-All lengths ($D_{h}$, $D_{p}$, $L$, $d$) were normalised w.r.t. $s_{f}$ and forces were normalized
-w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values were fixed relative
-to $\gamma_{fa}$. Non dimensional bubble volume was expressed as,
-$\hat{V}_{b}=V_{b}/s_{f}^{3}$
+%
+%All lengths ($D_{h}$, $D_{p}$, $L$, $d$) were normalised w.r.t. $s_{f}$ and forces were normalized
+%w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values were fixed relative
+%to $\gamma_{fa}$. Non dimensional bubble volume was expressed as,
+%$\hat{V}_{b}=V_{b}/s_{f}^{3}$
 
@@
 all model calculations (Table \ref{tab:Model-parameters}). Here,
-we assumed the tarsal adhesive fluid to be an oil-like substance and thus the
-interfacial tension ratios $\gamma_{wa}/\gamma_{fa}$ and $\gamma_{fw}/\gamma_{fa}$
-were assumed to correspond to typical values for oil and water. We considered
-representative hydrophilic and hydrophobic substrates with $\theta_{fa}$
-and $\theta_{wa}$ values corresponding to a typical glass and fluorinated
-surface, respectively. The contact area fraction of the hairs relative to the
-pad, $\alpha=ND_{h}^{2}/D_{p}^{2}$, hair aspect ratio, $L/D_{h}$,
-and fluid size parameter, $\phi_{f}$, were fixed to values typical
-for a ladybug's hairy pad.
+we assumed the tarsal adhesive fluid to have similar interfacial tension values as n-hexadecane \citep{RN320}. Experimental receding contact angle values for n-hexadecane and water
+on untreated (hydrophilic) and fluorinated (hydrophobic) glass surface were used as 
+ $\theta_{fa}$ and $\theta_{wa}$, respectively (Table S1).
+Hair and pad geometry, and tarsal fluid volume were assumed to be values typical
+for a ladybug's hairy pad \citep{RN19, RN108}.
 
@@
 
+%\begin{table}[!t]
+%\processtable{Fixed parameters corresponding to the pad's geometry, 
+%tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
+%{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
+%\hline
+%\TCH{Property} & \TCH{Value} \\
+%\hline
+%Contact area fraction, $\alpha$ & 0.1\\
+%Hair aspect ratio, $L/D_{h}$ & 10\\
+%Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\\
+%Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\\
+%Tarsal fluid size parameter, $\phi_{f}$ & 2\\
+%\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
+%    & $\theta_{wa}=24\lyxmathsym{\textdegree}$\\
+%\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=50\lyxmathsym{\textdegree}$\\
+%    & $\theta_{wa}=120\lyxmathsym{\textdegree}$
+%\end{tabular*}}{}
+%\end{table}
+
 \begin{table}[!t]
@@
 \hline
-Contact area fraction, $\alpha$ & 0.1\\
-Hair aspect ratio, $L/D_{h}$ & 10\\
-Water surface tension ratio, $\gamma_{wa}/\gamma_{fa}$ & 3\\
-Tarsal fluid-water interfacial tension ratio, $\gamma_{fw}/\gamma_{fa}$ & 2\\
-Tarsal fluid size parameter, $\phi_{f}$ & 2\\
+Number of hairs, $N$ & 500\\
+Hair diameter, $D_{h}$ & 4 \textmu m\\
+Pad diameter, $D_{p}$ & 200 \textmu m\\
+Hair length, $L_{h}$ & 40 \textmu m\\
+Water surface tension, $\gamma_{wa}$ & 72 mN m\textsuperscript{-1}\\
+Tarsal fluid-air surface tension, $\gamma_{fw}$ & 27 mN m\textsuperscript{-1}\\
+Tarsal fluid-water interfacial tension, $\gamma_{fw}$ & 55 mN m\textsuperscript{-1}\\
+Tarsal fluid volume, $V_{f}$ & 4 fL\\
+Bubble volume, $V_{b}$ & 1 nL\\
 \multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
-    & $\theta_{wa}=24\lyxmathsym{\textdegree}$\\
-\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=50\lyxmathsym{\textdegree}$\\
-    & $\theta_{wa}=120\lyxmathsym{\textdegree}$
+    & $\theta_{wa}=20\lyxmathsym{\textdegree}$\\
+\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=56\lyxmathsym{\textdegree}$\\
+    & $\theta_{wa}=93\lyxmathsym{\textdegree}$
 \end{tabular*}}{}
@@
 would have shown high attractive forces on a hydrophilic substrate\citep{RN93}. 
-
+It is reasonable to expect the contact line to be mechanically pinned around the rim of the discoidal-shaped hair tip.
+Since the male ladybug's pads are majorly composed of discoidal hairs, we proceed with this assumption to estimate the net adhesion
+force of the whole pad.
+%CHECK EVERYWHERE SHOULD BE DIMENSIONAL!
 \subsection{Adhesion of a hairy pad: Effect of the substrate\label{subsec:Capillary-Bridge-Model:}}
@@
 
-We observed that the bubble itself doesn't contribute much to the net force
+We observed that the bubble itself does not contribute much to the net force
 on either substrate (Figure \ref{fig:Effect-of-substrate}). Its contribution
@@
 volume, when compared to the whole pad. Further, opposite trends of
-adhesion is seen on the two substrates with changing $\hat{V}_{b}$.
+adhesion are seen on the two substrates with changing $\hat{V}_{b}$.
 
@@
 
-%change 1e6 to 1 10^6%
+%CHECK THIS!!%
 \subsection{Adhesion of a hairy pad: Effect of the hair tip diameter}
@@
 the capillary adhesive force in each case (Figure \ref{fig:Oil-contact-images}).
-However, the experiments don't show the predicted $\sim$ 2.6 times
+However, the experiments do not show the predicted $\sim$ 2.6 times
 increase in underwater adhesion relative to that in air on the hydrophobic
@@
 not all the hairs might be able to completely drain the interfacial
-water layer, in order for the tarsal adhesive fluid to make a direct contact
+water layer, in order for the tarsal adhesive fluid to make direct contact
 with the substrate. This can further reduce underwater adhesion, in
@@
 the constrained pad typically peels off from its proximal to distal end rather
-than detach simultaneously. Our model also assumes the hairs to be
+than detach simultaneously. Our model also assumes the hairs to be stiff and 
 of similar geometry, unlike the male beetle's pad which has a distribution
-of flat or pointed tipped hairs. Thus, it's not surprising that the
-model overestimates the adhesion forces. The predictions are however
+of flat or pointed tipped soft hairs. Thus, it is not surprising that the
+model overestimates the adhesion forces. However, when comparing the adhesion in air and underwater,
+the effect of pad orientation, peeling, hair geometry or elasticity on adhesion should be similar for both cases, and thus, can be reasonably ignored. The model predictions are
 in the same order of magnitude as experiments, and the qualitative
@@
 
-Our study provides further validation that capillary forces govern the ladybug's adhesion and van der Waals contribution,
+Our study provides further validation that capillary forces govern the ladybug's adhesion and van der Waals contributions,
 if any, must be negligible. Further, the capillary forces can even
@@
 to a hydrophobic substrate, but poorly to a hydrophilic substrate,
-even though it shows similarly strong adhesion to both substrates
+even though the pad shows similarly strong adhesion to both substrates
 in air. This effect can be explained by capillary forces and the wetting properties of the fluid. Our
@@
 Therefore, the fluid should be able to form capillary bridges and help mediate adhesion even when underwater.
+
+The presence of interfacial water was expected to cause adhesion loss during underwater contact.
+However, we see that, underwater adhesion is possible even for a hydrophilic surface without a trapped bubble (Figure \ref{fig:Effect-of-contact}).
+This suggests the possible role of interfacial water drainage dynamics on adhesion.
+The experimental adhesion values lie close the theoretical predictions, which suggests that the interfacial water is drained out within the time-scale of contact ($\sim$ 4 s).
+The tarsal fluid would then form capillary bridges in direct contact with the surface and enable adhesion.
+The details of this drainage mechanism during capillary mediated underwater adhesion would be interesting to look at in a future study.
 
@@
 \end{figure}
-%CHANGE REFERENCE FORMAT IN PLOT
+
 We have so far limited our analysis to only smooth substrates. Of course insects
@@
 is a more dominant parameter than substrate chemistry in controlling
-ladybug beetle traction force. Future work will explore how roughness can impact
+ladybug beetle traction force.
+Here, the length scale of surface roughness relative to the tarsal fluid thickness would be important in the formation of stable capillary bridges.
+Further, the presence of air plastron between the roughness asperities can influence the nature of contact when underwater.
+Future work will explore how roughness can impact
 the net capillary force also in wet and submerged conditions.

### 2021-08-03 source/jeb_tex/supplementary.tex
Linear mixed model results included in supplementary info.
Reviewer 1 and 3 responded and changes made in MS.
Reviewer 2 typo suggestions included

--- 2021-05-11 source/tex/supplementary.tex
@@
 \usepackage{subscript}
+%\usepackage[bottom]{footmisc}
 %\usepackage[unicode=true,pdfusetitle,
@@
 
-The surface chemistry of untreated glass (hydrophilic) and PFOTS-coated glass (hydrophobic) were characterized using dynamic contact angle measurements (Table \ref{tab:Contact-Angles}).
+The surface chemistry of untreated glass (hydrophilic) and PFOTS-coated glass (hydrophobic) was characterized using dynamic contact angle measurements (Table \ref{tab:Contact-Angles}).
 \begin{table}[H]
@@
 
+The effect of substrate, contact mode, tilt angle, beetle identity and repetition number on the adhesion were analysed using a linear mixed-effect model (LMEM) in Python.
+Here, each experimental data point was considered distinctly without averaging the repeats as before.
+Substrate, contact mode, tilt angle and repetition number were taken as fixed-effects, while, beetle identity was considered as the random-effect.
+Interaction between each of the fixed-effects were fitted using the random intercept model.
+Adhesion measurement on hydrophilic glass \emph{in air} was taken as the reference.
+The resultant fixed-effects coefficient estimates, standard error, z-statistic and p-value are reported below (Table \ref{tab:LMEM-analysis}).
+The random-effect (beetle identity) showed an intercept standard deviation of 100.563 \textmu N (std.
+error = 109.771)
+
+\begin{table}[]
+\begin{tabular}{|c|l|l|l|l|}
+\hline
+\multicolumn{1}{|l|}{}           & \multicolumn{1}{c|}{\textbf{Estimate}} & \multicolumn{1}{c|}{\textbf{Std.
+Error}} & \multicolumn{1}{c|}{\textbf{z}} & \multicolumn{1}{c|}{\textbf{p-value}} \\ \hline \hline
+\textbf{Intercept \footnotemark[1]}               & 582.072                                & 170.307                                  & 3.418                           & 0.001                                 \\ \hline
+\textbf{PFOTS}                   & -110.642                               & 206.268                                  & -0.536                          & 0.592                                 \\ \hline
+\textbf{Underwater:   bubble}    & -304.667                               & 89.458                                   & -3.406                          & 0.001                                 \\ \hline
+\textbf{Underwater: no   bubble} & -254.924                               & 117.386                                  & -2.172                          & 0.03                                  \\ \hline
+\textbf{Repetition   number}     & 7.723                                  & 6.703                                    & 1.152                           & 0.249                                 \\ \hline
+\textbf{Tilt angle}              & -5.649                                 & 7.088                                    & -0.797                          & 0.425                                 \\ \hline
+\end{tabular}
+\caption{Linear mixed-effect model statistics\label{tab:LMEM-analysis}}
+\end{table}
+
 \section{Capillary force due to an air bubble\label{subsec:Capillary-force-due}}
+
+\footnotetext[1]{Adhesion on glass \emph{in air}}
 
@@
 at 62.5 \textmu m s\protect\textsuperscript{-1} speed. The maximum
-adhesion force of any of the bubble never exceeds 50 \textmu N,
+adhesion force of any of the bubbles never exceeds 50 \textmu N,
 significantly lower than the beetle's underwater adhesion to the same
@@
 \end{figure}
+
+\section{Capillary bridge model: Sensitivity analysis}
+
+Sensitivity analysis was performed using the one-at-a-time (OAT) method. Dimensionless model parameters were initially set to correspond to the ladybug's case, as given by,
+contact area fraction ($\alpha=ND_{h}^{2}/D_{p}^{2}=0.1$), pad to hair diameter ratio ($D_p/D_h=50$), hair aspect ratio ($L/D_{h}=10$), water surface tension ratio ($\gamma_{wa}/\gamma_{fa}=3$),
+tarsal fluid-water interfacial tension ratio ($\gamma_{fw}/\gamma_{fa}=2$), tarsal fluid size parameter ($\phi_{f}=2$), bubble size parameter ($\phi_{b}=1.6$).
+Substrate contact angles were kept fixed (same as in main text).
+Each parameter was varied within a particular range, one at a time, and the corresponding adhesion forces \emph{in air} (F\textsubscript{a}),   \emph{underwater: no bubble} (F\textsubscript{w}) and \emph{underwater: bubble} (F\textsubscript{b}) were calculated.
+Linear least square regression was performed to quantify the relative change in adhesion for each contact mode with respect to the varied parameter.
+Here, F\textsubscript{w}/F\textsubscript{a} and F\textsubscript{b}/F\textsubscript{a} were taken to be the model output.
+Slope and R\textsuperscript{2} values for each case are reported below (Table \ref{tab:Sens-anal}).
+Slope with absolute values greater than 0.5 are highlighted in bold.
+
+\begin{table}[H]
+\begin{tabular}{|l|l|l|l|l|l|l|}
+\hline
+\multirow{2}{*}{\textbf{Parameter}} & \multirow{2}{*}{\textbf{Range}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Substrate}}} & \multicolumn{2}{c|}{\textbf{F\textsubscript{w}/F\textsubscript{a}}}                                    & \multicolumn{2}{c|}{\textbf{F\textsubscript{b}/F\textsubscript{a}}}                                    \\ \cline{4-7}
+                                    &                                 & \multicolumn{1}{c|}{}                                    & \multicolumn{1}{c|}{\textbf{slope}} & \multicolumn{1}{c|}{\textbf{R\textsuperscript{2}}} & \multicolumn{1}{c|}{\textbf{slope}} & \multicolumn{1}{c|}{\textbf{R\textsuperscript{2}}} \\ \hline  \hline
+\multirow{2}{*}{$\alpha$}              & \multirow{2}{*}{0.05 - 0.3}      & Hydrophilic                                              & 3.03E-18                                  & 1.52E-03                               & 2.30E-01                                  & 7.72E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & -9.69E-17                                 & 3.03E-03                               &\textbf{ -9.40E-01}                                 & 7.72E-01                               \\ \hline
+\multirow{2}{*}{$D_p/D_h$}             & \multirow{2}{*}{30.0 - 60.0}     & Hydrophilic                                              & -8.83E-20                                 & 1.48E-01                               & 1.28E-02                                  & 9.73E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & -5.65E-18                                 & 1.48E-01                               & -1.51E-02                                 & 9.82E-01                               \\ \hline
+\multirow{2}{*}{$L/D_{h}$}         & \multirow{2}{*}{8.0 - 15.0}      & Hydrophilic                                              & 0.00E+00                                  & 0.00E+00                               & -5.27E-02                                 & 9.11E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 0.00E+00                                  & 0.00E+00                               & 5.41E-02                                  & 8.66E-01                               \\ \hline
+\multirow{2}{*}{$\gamma_{wa}/\gamma_{fa}$}              & \multirow{2}{*}{2.5 - 3.5}       & Hydrophilic                                              & -2.01E-01                                 & 8.57E-01                               & -2.43E-01                                 & 9.43E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 4.11E-02                                  & 1.00E+00                               & 6.87E-02                                  & 1.00E+00                               \\ \hline
+\multirow{2}{*}{$\gamma_{fw}/\gamma_{fa}$}              & \multirow{2}{*}{1.5 - 2.5}       & Hydrophilic                                              & 2.01E-01                                  & 8.62E-01                               & 1.90E-01                                  & 8.94E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & \textbf{5.56E-01}                                  & 1.00E+00                               & 1.57E-01                                  & 1.00E+00                               \\ \hline
+\multirow{2}{*}{$\phi_{f}$}             & \multirow{2}{*}{1.7 - 2.2}       & Hydrophilic                                              & 1.29E-02                                  & 4.52E-01                               & 6.18E-02                                  & 7.94E-02                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 7.67E-02                                  & 9.84E-01                               & -3.06E-01                                 & 9.66E-01                               \\ \hline
+\multirow{2}{*}{$\phi_{b}$}             & \multirow{2}{*}{1.2 - 1.8}       & Hydrophilic                                              & 0.00E+00                                  & 0.00E+00                               & \textbf{-1.14E+00}                                 & 8.85E-01                               \\ \cline{3-7}
+                                    &                                 & Hydrophobic                                              & 0.00E+00                                  & 0.00E+00                               & \textbf{1.46E+00}                                  & 9.78E-01                               \\ \hline
+\end{tabular}
+\caption{Sensitivity analysis \label{tab:Sens-anal}}
+\end{table}
 

### 2021-08-05 source/jeb_tex/manuscript.tex
responded to Reviewer 2 comments.
updated MS and figures and supplementary based on his elaborate comments.

@@
 
-\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles}
+\title{Wetting of the tarsal adhesive fluid determines underwater adhesion in ladybug beetles}
 
@@
 While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much rarer and has been relatively unexplored.
-Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces.
+Some aquatic insects like diving beetles \citep{Chen:2014} or midge larva \citep{Kang:2020} use suction cups to adhere to surfaces \citep{DITSCHEKURU2012379,RN123}.
 However, underwater adhesion mediated by secreted liquids requires the displacement of the water at the interface first and a spreading of the fluid on the substrate.
-One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}.
-This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble.
+One approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \citep{Seymour:2013}.
+This has been shown in a recent study by \citet{RN87} that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach to surfaces underwater by using such an air bubble.
 Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact.
@@
 
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=6in]{Figure1-Setup_schematic}%
+\caption[]{Adhesion test setup (see text for details).
+Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange).
+The recorded force data and
+contact area of a distal pad are shown in the bottom-right plot, in which, the shaded
+regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
+represent attraction and the minimum force peak during the final retraction
+step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the supplementary material (see Movie1).}
+\label{fig:Setup}
+\end{figure*}
+
 The goal of this paper is to clarify the current understanding of underwater adhesion seen in terrestrial insects which use hairy pads and secrete an oily fluid for attachment.
+Specifically, the significance of a trapped air bubble to promote underwater adhesion was resolved.
 We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion force of its individual pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces.
@@
 Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions.
-The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion.
+The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's contribution in the insect's adhesion.
 Finally, we discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.
@@
 Each leg of a male ladybug beetle has two hairy adhesive pads.
-For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one.
+For the test, we only allowed the distal pad to make a good contact with the substrate thus minimising partial or bad contact of the proximal pad.
 The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack.
 The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset).
-Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres.
+Care was taken to ensure the glue does not contaminate the rest of the tarsomeres.
 A small piece of non-sticky Teflon tape helped to keep the other legs tucked close to the body and avoided any interference during the adhesion test.
@@
 as well as observe the contact. The force sensor was mounted on a stage
-consisting of a X-piezo element (\emph{Physik Instrumente, Germany}), used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
+consisting of a X-piezo element, used for precise lateral movements. Additionally, a separate Z-piezo element (P-629.1CD, \emph{Physik Instrumente, Germany}, resolution = 3 nm), fixed upright,
 was used for vertical up-down motion, bringing the insect in contact
@@
 LABVIEW (\emph{National Instruments, USA}) program. Force data was acquired at a sample rate of 984 Hz,
-averaged to 512 points per motion step. Videos were recorded at 20
+averaged to 512 points per motion step for smoothing. Videos were recorded at 20
 frames per second.
@@
 A further 10 \textmu m compression step (approach) set all hairs in slight compression which helped maximize the hair contact
-with the surface. Next, a short pause (1 s) removed any
+with the surface. Next, a short pause (1 s) minimized any
 viscoelastic effects before finally retracting the leg away from the
@@
 For underwater experiments, 1 ml Milli-Q water was pipetted into the
-substrate holder (roughly 3 mm water level). The beetle was then partially 
+substrate holder (roughly 3 mm water level). The beetle (roughly 5 mm long) was then partially 
 submerged to allow underwater contact of the pad with the substrate (immersion time $\sim$ 15 mins). In order to achieve contact without
@@
 Before the experiments,
-the pad was brought into contact with the clean dry surface 10 times repeatedly 
+the pad was brought into contact with the clean dry surface 10 times repeatedly (same motion protocol as described above)
 to ensure the hairs are free of any contaminating particles.
@@
 Five force measurements were subsequently performed, each on a fresh spot of the substrate, and were averaged to avoid pseudo-replication during data analysis.
-Experiments were repeated with 30 distinct male beetles for all combinations of contact mode (``\emph{in air}'', ``\emph{underwater:
-bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic), 5 beetles for each  combination.
+Experiments were repeated with distinct male beetles for each combination of contact mode (``\emph{in air}'', ``\emph{underwater:
+bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic), using 5 beetles for each  combination.
+Thus, 30 distinct beetles were used in total.
 After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=6in]{Figure1-Setup_schematic}%
-\caption[]{Adhesion test setup (see text for details).
-Top-left inset shows a magnified cartoon of the beetle's leg constrained to a solder wire (grey) using Blu Tack (blue) and epoxy glue (orange).
-The recorded force data and
-contact area of a distal pad are shown in the bottom-right plot, in which, the shaded
-regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
-represent attraction and the minimum force peak during the final retraction
-step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the supplementary material (see Movie1).}
-\label{fig:Setup}
-\end{figure*}
 
@@
 For underwater measurements, an additional correction was necessary.
-When the beetle was partially submerged underwater, its contact line at the
-water surface shifted, which influenced the force readout due to surface
+When the beetle was partially submerged underwater, the water's contact with the beetle shifted, which influenced the force readout due to surface
 tension and buoyancy. This effect needed to be cancelled. Therefore, a ``background''
-force data was recorded, where the submerged beetle makes no contact
+force data was recorded, following the exact motion protocol as a typical adhesion test, but where the submerged beetle makes no contact
 with the substrate. This background data was then subtracted from
-a typical force curve with substrate contact to correct for the external
-surface tension effects. The pull-off force was subsequently calculated
+a typical force curve with substrate contact, by matching the time data, to correct for the external
+surface tension effects ($\sim$ 50 \textmu N) for each individual beetle. The pull-off force was subsequently calculated
 from the minima as before.
@@
  adhesion force measurements of ladybug beetle's (\emph{Coccinella
-septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
-conditions (n=5 per box). The two modes of contact during underwater experiments
+septempuctata}) distal pad on untreated hydrophilic glass (blue) and hydrophobic PFOTS coated glass (cream) substrates in air and underwater
+conditions (n=5 per box). The small black markers show the underlying data points. The two modes of contact during underwater experiments
 are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
-and \textquotedblleft\emph{no bubble}\textquotedblright . The small diamonds represent outlier points. Crosses
+and \textquotedblleft\emph{no bubble}\textquotedblright. Crosses
 represent theoretical predictions of adhesion force, while, circles
 represent the contribution of the bubble itself, calculated from the
-capillary bridge model (see text). In the model, hair diameter = 4 \textmu m,
-pad diameter = 200 \textmu m, hair length = 40 \textmu m,
-N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
-= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
-tension of the tarsal adhesive fluid in air and water were assumed to be
-24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
+capillary bridge model (see text and Table \ref{tab:Model-parameters}).}
 \end{figure}
@@
 Apart from the three depicted contact modes, we observed an additional
-fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
+fourth mode which occurred in roughly 25\% of our underwater experiments (excluded from above analysis) using degassed water.
 In this scenario, the ventral view recordings show that none of the hairs
@@
 
-We modelled the hairy pad as an array of $N$ cylindrical rods of length,
+The male ladybug beetles used in our experiments are known to possess mostly discoidal hairs on their distal pad.
+Contact images show that these hair tips are approximately circular (eccentricity $\sim$ 0.04), which could allow mechanical pinning of the secreted fluid around its perimeter.
+Based on this knowledge, we modelled the hairy pad as an array of $N$ cylindrical rods of length,
 $L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
@@
 respectively, to conveniently scale their volumes relative to the
-hair and pad diameters they are pinned to.
+hair and pad diameters they are pinned to. Larger values of $\phi_{f}$ ($\phi_{b}$) represents a smaller volume of liquid (bubble) relative to the hair (pad) that it is pinned to.
 
-The net force for cases 1 and 2 can be calculated as:
+The net force of the array, $F_{net}$, for cases 1 and 2 can be calculated as:
 
@@
 
+\begin{table}[!t]
+\processtable{Fixed parameters corresponding to the pad's geometry, 
+tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
+{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
+\hline
+\TCH{Property} & \TCH{Value} \\
+\hline
+Number of hairs, $N$ & 500\\
+Hair diameter, $D_{h}$ & 4 \textmu m\\
+Pad diameter, $D_{p}$ & 200 \textmu m\\
+Hair length, $L$ & 40 \textmu m\\
+Water surface tension, $\gamma_{wa}$ & 72 mN m\textsuperscript{-1}\\
+Tarsal fluid-air surface tension, $\gamma_{fw}$ & 27 mN m\textsuperscript{-1}\\
+Tarsal fluid-water interfacial tension, $\gamma_{fw}$ & 55 mN m\textsuperscript{-1}\\
+Tarsal fluid volume, $V_{f}$ & 4 fL\\
+Bubble volume, $V_{b}$ & 1 nL\\
+\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
+    & $\theta_{wa}=20\lyxmathsym{\textdegree}$\\
+\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=56\lyxmathsym{\textdegree}$\\
+    & $\theta_{wa}=93\lyxmathsym{\textdegree}$
+\end{tabular*}}{}
+\end{table}
+
 Geometric parameters and interfacial properties were kept fixed for
@@
 capillary bridge. Second, the effect of substrate on the force-distance
-curves of the hairy pad system was compared for each mode of contact.
-Third, we looked at the effect of changing the bubble
+curves of the hairy pad system was compared for each mode of contact. The volume of the bubble would
+influence it's capillary force as well as the proportion of hairs that are inside or outside the bubble.
+Thus, we also looked at the effect of changing the bubble
 volume, $\hat{V}_{b}$, on the net underwater adhesion.
-Finally, the influence of varying the hair diameter, $D_{h}$, on adhesion
-was studied for each case.
+Additionally, the influence of varying the hair diameter, $D_{h}$, on adhesion
+was studied for each case, to illustrate the ``contact splitting" effect \citep{RN24}.
 
@@
 
-\begin{table}[!t]
-\processtable{Fixed parameters corresponding to the pad's geometry, 
-tarsal fluid and substrate wetting properties used in the capillary bridge model \label{tab:Model-parameters}}
-{\begin{tabular*}{3.5in}{@{\extracolsep{\fill}}lllll@{}}
-\hline
-\TCH{Property} & \TCH{Value} \\
-\hline
-Number of hairs, $N$ & 500\\
-Hair diameter, $D_{h}$ & 4 \textmu m\\
-Pad diameter, $D_{p}$ & 200 \textmu m\\
-Hair length, $L_{h}$ & 40 \textmu m\\
-Water surface tension, $\gamma_{wa}$ & 72 mN m\textsuperscript{-1}\\
-Tarsal fluid-air surface tension, $\gamma_{fw}$ & 27 mN m\textsuperscript{-1}\\
-Tarsal fluid-water interfacial tension, $\gamma_{fw}$ & 55 mN m\textsuperscript{-1}\\
-Tarsal fluid volume, $V_{f}$ & 4 fL\\
-Bubble volume, $V_{b}$ & 1 nL\\
-\multirow{2}{*}{Hydrophilic substrate wetting} &  $\theta_{fa}=6\lyxmathsym{\textdegree}$\\
-    & $\theta_{wa}=20\lyxmathsym{\textdegree}$\\
-\multirow{2}{*}{Hydrophobic substrate wetting} &  $\theta_{fa}=56\lyxmathsym{\textdegree}$\\
-    & $\theta_{wa}=93\lyxmathsym{\textdegree}$
-\end{tabular*}}{}
-\end{table}
-
-\subsection{Capillary force of a single liquid bridge\label{subsec:Capillary-force-of}}
-
-Forces due to a single pinned capillary liquid bridge in contact with
-a substrate were obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
-We see that, generally, the shape of the liquid meniscus determines
-the strength of its adhesion force. High adhesion is seen for contact
-angles less than $\sim$ 70\textdegree{} due to a net negative (convex) curvature
-of the meniscus, while low adhesion is seen for contact angles greater
-than $\sim$ 150\textdegree{} due to its net curvature being close
-to zero. The Laplace pressure contribution to the net adhesion force
-dominates for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
-Interestingly, its contribution to the adhesion force is mostly non-repulsive
-for contact angles greater than 90\textdegree . This is because, the
-low volume of the liquid and its pinned contact line prevents the
-meniscus from having a high positive (concave) curvature due to geometric constraints.
-Only for a contact angle of 150\textdegree , the liquid's curvature
-becomes positive, manifested in its slightly repulsive Laplace contribution.
-Surface tension makes a significant contribution to the net force
-only for a small range of contact angles close to 90\textdegree .
-For contact angles greater than 150\textdegree , the net adhesion
-force approaches zero.
-
 \begin{figure*}[!t]
@@
 \end{figure*}
+
+\subsection{Capillary force of a single liquid bridge\label{subsec:Capillary-force-of}}
+
+Forces due to a single pinned capillary liquid bridge in contact with
+a substrate were obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
+We see that, generally, the shape of the liquid meniscus determines
+the strength of its adhesion force. High adhesion (> 60 \% of maximum) is seen for contact
+angles less than $\sim$ 70\textdegree{} due to a net negative (convex) curvature
+of the meniscus, while low adhesion (< 10 \% of maximum) is seen for contact angles greater
+than $\sim$ 150\textdegree{} due to its net curvature being close
+to zero. The Laplace pressure contribution to the net adhesion force
+dominates for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
+Interestingly, its contribution to the adhesion force is mostly non-repulsive
+for contact angles greater than 90\textdegree . This is because, the
+low volume of the liquid and its pinned contact line prevents the
+meniscus from having a high positive (concave) curvature due to geometric constraints.
+Only for a contact angle of 150\textdegree , the liquid's curvature
+becomes positive, manifested in its slightly repulsive Laplace contribution.
+Surface tension makes a significant contribution to the net force
+only for a small range of contact angles close to 90\textdegree .
+For contact angles greater than 150\textdegree , the net adhesion
+force approaches zero.
 
@@
 The force-distance curves show a general trend of repulsive forces
-at small distances (Figure \ref{fig:Single-bridge}a). This is a result
+at small distances, a minima at an intermediate distance corresponding to the adhesion force, and finally tending to zero force at large distances until the capillary bridge ruptures (Figure \ref{fig:Single-bridge}a).
+The repulsive force seen at small distances is a result
 of the pinned contact line on the top. A limited volume is available
@@
 pressure and thus repulsion. Without pinning, the capillary forces
-would have shown high attractive forces on a hydrophilic substrate\citep{RN93}. 
+would have shown high attractive forces on a hydrophilic substrate \citep{RN93}. 
 It is reasonable to expect the contact line to be mechanically pinned around the rim of the discoidal-shaped hair tip.
@@
 
-The normalised force-distance curves of a hairy pad system on a hydrophilic
+The force-distance curves of a hairy pad system on a hydrophilic
 and hydrophobic substrate are predicted based on the capillary bridge
@@
 
-On the hydrophilic substrate ($\theta_{wa}=24\lyxmathsym{\textdegree}$),
+On the hydrophilic substrate ($\theta_{wa}=20\lyxmathsym{\textdegree}$),
 highest adhesion is seen when the hairs contact in air, while lowest
@@
 of a bubble leads to intermediate force values. In contrast, on a
-hydrophobic substrate ($\theta_{wa}=120\lyxmathsym{\textdegree}$),
+hydrophobic substrate ($\theta_{wa}=93\lyxmathsym{\textdegree}$),
 highest adhesion is seen for the underwater case without a trapped
@@
 air and underwater conditions. A negative force value represents attraction.
-Normalised forces are calculated from the capillary bridge model,
+Forces are calculated from the capillary bridge model,
 with model parameters listed in Table \ref{tab:Model-parameters}.
@@
 bubble} contact is denoted by plus symbols. Insets represent the \emph{underwater:
-bubble }contact for each substrate.}
+bubble} contact for each substrate.}
 \end{figure*}
@@
 contact angle of the oily fluid is 6\textdegree , when surrounded
-by air (Table \ref{tab:Model-parameters}) and 150\textdegree , when
+by air (Table \ref{tab:Model-parameters}) and 138\textdegree , when
 surrounded by water (equation (\ref{eq:theta_fw})). This results
@@
 poor adhesion underwater. On a hydrophobic substrate however, the
-contact angles of the fluid in air and water are 50\textdegree{} and
-1\textdegree , respectively. In both cases, the contact angles are
+contact angles of the fluid in air and water are 56\textdegree{} and
+70\textdegree , respectively. In both cases, the contact angles are
 low, resulting in strong adhesion in both media. Additionally, the
@@
 adhesion for the \emph{underwater: no bubble} case when compared to
-\emph{in air} (Figure \ref{fig:Oil-contact-images}). Note that the
-contact area is fixed in all cases by keeping the area fraction and
-$D_{p}/D_{h}$ constant. Thus the observed effects is not a result
-of changing contact area, but rather on the nature of capillary forces.
+\emph{in air} (Figure \ref{fig:Oil-contact-images}). Note that since the hair diameter is kept fixed, the observed effects are not a result
+of changing contact area, but rather of the nature of capillary forces.
 
@@
 (\ref{eq:f_bubble})). For the given bubble volume, only part of the
-hairs make contact with the surface inside the bubble for the hydrophilic case, while,
-all the hairs contact the surface inside the bubble for the hydrophobic case.
+hairs make contact with the surface inside the bubble.
 Therefore, the force curve lies between \emph{in air} and \emph{underwater:
-no bubble} cases for a hydrophilic substrate, and closely follows
-the \emph{in air} case for a hydrophobic substrate.
+no bubble} cases for both substrates.
 
@@
 as well as change the relative proportion of hairs inside and outside
-it. To investigate this, we varied the bubble volume, $\hat{V}_{b}$,
+it. To investigate this, we varied the bubble volume, $V_{b}$,
 and compared the maximum adhesion force on both hydrophilic and hydrophobic
@@
 of the bubble to the net adhesion force is small regardless of its
-volume, when compared to the whole pad. Further, opposite trends of
-adhesion are seen on the two substrates with changing $\hat{V}_{b}$.
+volume, when compared to the whole pad (less than 3 \%). Further, opposite trends of
+adhesion are seen on the two substrates with changing $V_{b}$.
 
@@
 fluid bridges outside the bubble show poor adhesion due to the positive
-curvature of their meniscus. Thus, decreasing $\hat{V}_{b}$ decreases
+curvature of their meniscus. Thus, decreasing $V_{b}$ decreases
 the adhesion force due to a larger proportion of tarsal hairs being outside
@@
 
-A smaller $\hat{V}_{b}$ resulted in increased, but small, attraction
-by the bubble on both types of substrates. For larger values of $\hat{V}_{b}$
+A smaller $V_{b}$ resulted in increased, but small, attraction
+by the bubble on both types of substrates. For larger values of $V_{b}$
 however, the force trend for the whole pad mostly follows that of
 the bubble. This is because the bubble gets big enough to entrap all
-the hairs inside it. Thus, the force contribution due to the fluid
+the hairs inside it (Figure \ref{fig:Effect-of-bubble} inset). Thus, the force contribution due to the fluid
 bridges remain unchanged, and only the bubble's contribution drives
-the slight variation in the pad's adhesion at high $\hat{V}_{b}$.
+the slight variation in the pad's adhesion at high $V_{b}$.
 Once the bubble is small enough such that part of the fluid bridges
@@
 decrease (increase) in adhesion force on hydrophilic (hydrophobic)
-substrate as the volume decreases.
+substrate with decreasing bubble volume.
 
 \begin{figure}
-\includegraphics[width=3.5in]{Figure7-Model_effect_of_bubble_volume}\caption{\label{fig:Effect-of-bubble}Normalised adhesion force of a hairy
-pad as a function of bubble volume, $\hat{V}_{b}$, for the
+\includegraphics[width=3.5in]{Figure7-Model_effect_of_bubble_volume}\caption{\label{fig:Effect-of-bubble} Adhesion force of a hairy
+pad as a function of bubble volume, $V_{b}$, for the
 \emph{underwater: bubble} contact mode. Adhesion forces are calculated
 from the minima of the respective force-distance curves. Negative
-force value represents attraction. Pad to hair diameter ratio ($D_{p}/D_{h}$)
-is kept fixed. Highlighted regions represent entrapment of all hairs
-within the bubble.}
+force value represents attraction. The inset plot shows the corresponding fraction of hairs, $N_{in}/N$, making contact inside the bubble. Highlighted regions represent entrapment of all hairs
+within the bubble. Remaining model parameters are kept fixed, as listed in Table \ref{tab:Model-parameters}}
 \end{figure}
@@
 \includegraphics[width=3.5in]{Figure6-Model_effect_of_hair_size}
-\caption{\label{fig:Effect-of-hair}Normalised adhesion force of a hairy pad on a hydrophilic and hydrophobic substrate as a function of
+\caption{\label{fig:Effect-of-hair}Adhesion force of a hairy pad on a hydrophilic and hydrophobic substrate as a function of
 hair tip diameter, $D_{h}$. Volume of each fluid bridge, $V_{f}$, scales
-relative to $D_{h}$ based on the parameter $\phi_{f}=2$. Adhesion
+relative to $D_{h}$ based on the parameter $\phi_{f}=2$.
+Total contact area is kept fixed to 6283 \textmu m\textsuperscript{2} throughout.
+The number of hairs, $N$, varies with $D_h$, as shown in the inset plot.
+Adhesion
 forces are calculated from the minima of the respective force-distance
 curves, based on the capillary bridge model. A negative value represents
-attraction. The air bubble's contribution to the net force for an \emph{underwater:
-bubble} contact is denoted by plus symbols. Pad diameter and bubble
-volume are kept fixed. All lengths are scaled relative to $D_{p}$.}
+attraction. Remaining model parameters are kept fixed, as listed in Table \ref{tab:Model-parameters}}
 \end{figure}
@@
 changing the hair tip diameter, $D_{h}$ (Figure \ref{fig:Effect-of-hair}).
-Here, the pad diameter, total hair contact area and bubble volume
-are constant since $D_{p}$, $\alpha$ and $\hat{V}_{b}$ are kept
-fixed. The tarsal adhesive fluid volume is again assumed to scale relative
-to the hair diameter ($\phi_{f}=2$).
+Here, we fix the total contact area to 6283 \textmu m\textsuperscript{2} (corresponding to Figure \ref{fig:Effect-of-substrate}) and vary the number of hairs with $D_h$ to illustrate the ``contact splitting" effect.
+The tarsal adhesive fluid volume is assumed to scale relative
+to the hair diameter ($\phi_{f}=2$). The pad diameter, hair length and bubble volume
+are kept fixed as per Table \ref{tab:Model-parameters}.
 
@@
 with the ``contact splitting'' theory, which predicts higher adhesion
-when the contact is split into many small contact points\citep{RN24}.
+when the contact is split into many small contact points \citep{RN24}.
 Reducing the hair diameter results in two competing effects: 1) capillary
@@
 
-The bubble's contribution gets repulsive as hair diameter decreases
-for both substrates (Figure \ref{fig:Effect-of-hair}). Since the
-aspect ratio $L/D_{h}$ is fixed (Table \ref{tab:Model-parameters}),
-decreasing the hair diameter also decreases its length. Since the
-bubble's volume is kept constant, it will then have a lesser space
-available to occupy between the pad and the substrate. This results
-in it bulging outwards near the pinned contact line on the top, causing
-repulsion.
+%The bubble's contribution gets repulsive as hair diameter decreases
+%for both substrates (Figure \ref{fig:Effect-of-hair}). Since the
+%aspect ratio $L/D_{h}$ is fixed (Table \ref{tab:Model-parameters}),
+%decreasing the hair diameter also decreases its length. Since the
+%bubble's volume is kept constant, it will then have a lesser space
+%available to occupy between the pad and the substrate. This results
+%in it bulging outwards near the pinned contact line on the top, causing
+%repulsion.
 
@@
 Predictions of the ladybug's adhesion from the capillary bridge model
-agree with our experimental results (Figure \ref{fig:Effect-of-contact}).
+agree qualitatively with our experimental results (Figure \ref{fig:Effect-of-contact}).
 In underwater conditions without a trapped air bubble, adhesion to a hydrophobic
@@
 the capillary adhesive force in each case (Figure \ref{fig:Oil-contact-images}).
-However, the experiments do not show the predicted $\sim$ 2.6 times
+However, the experiments do not show the predicted $\sim$ 1.7 times
 increase in underwater adhesion relative to that in air on the hydrophobic
 PFOTS-coated surface. This discrepancy could be due to our assumptions of
-the oily fluid's interfacial properties. If we choose $\gamma_{fa}$=30
-mN m\protect\textsuperscript{-1} and $\gamma_{fw}$=40 mN m\protect\textsuperscript{-1}, the corresponding increase in adhesion
-will be $\sim$ 1.7, closer to our experimental value of $\sim$ 1.
-The resulting change in $\theta_{fa}$ and $\theta_{fw}$ will further
-decrease this number. Direct measurement of the fluid's interfacial
+the oily fluid's interfacial properties, which are not known for the ladybug beetle.
+Sensitivity analysis of the model does in fact show that the relative adhesion underwater when compared to that in air is sensitive to the fluid's interfacial tension values in air and water (see supplementary section S5).
+Direct measurement of the fluid's interfacial
 properties is thus essential to better predict the insect's adhesion,
@@
 trend is consistent for both hydrophilic and hydrophobic substrates
-in air and underwater.
+in air and underwater. Further, sensitivity analysis of the model showed that 
+the relative underwater adhesion when compared to that in air was insensitive to the hair or pad geometrical parameters, which validates the applicability of the model for our choice of parameters (see supplementary section S5).
+Interfacial tension influenced the relative adhesion for \emph{underwater: no bubble} case, while, contact area and bubble volume influenced the relative adhesion for \emph{underwater: bubble} case, as expected.
 
@@
 This suggests the possible role of interfacial water drainage dynamics on adhesion.
-The experimental adhesion values lie close the theoretical predictions, which suggests that the interfacial water is drained out within the time-scale of contact ($\sim$ 4 s).
+The experimental adhesion values lie close to the theoretical predictions, which suggests that the interfacial water is drained out within the time-scale of contact ($\sim$ 4 s).
 The tarsal fluid would then form capillary bridges in direct contact with the surface and enable adhesion.
@@
 It has been reported that some ants show similar adhesion on hydrophobic substrates under wet and dry conditions \citep{RN213},
-similar to what we see in a ladybug. This observation can again be explained by a capillary model as before. Recent experiments on
+similar to what we see in a ladybug.
+This observation can again be explained by a capillary model as before, where, the wetting and interfacial tension of the ants' secretion could mediate their underwater adhesion to hydrophobic substrates.
+Previous experiments on
 geckos revealed that they can attach well to fluoropolymer substrates (such as PTFE) 
-underwater while they show little adhesion to the same substrate in
-air\citep{RN199,RN15}. Geckos are thought to rely on van der Waals
-forces via dry contact with the substrate \citep{RN202}, although
-recent observations of phospholipid footprints left behind walking
-geckos \citep{RN205} could change that picture. Since geckos adhere
-poorly to PTFE (surface energy $\sim$ 20 mN m\protect\textsuperscript{-1}) one can
+when underwater, while they show little adhesion to the same substrate in
+air \citep{RN15,RN199}. Geckos are thought to rely on van der Waals
+forces via dry contact with the substrate \citep{RN202}, although observations of phospholipid footprints left behind walking
+geckos \citep{RN205} could change that picture.
+A recent study has in fact presented evidence for the importance of polar interactions in gecko adhesion mediated by this phospholipid layer \citep{RN301}.
+This calls for a reinterpretation of previously reported gecko adhesion data by considering the influence of the phospholipid layer.
+In principle, a capillary model could be used to describe the adhesion mediated by this layer, by assuming that the phospholipid compound is mobile with liquid-like properties.
+Since geckos adhere
+poorly to PTFE (surface energy $\sim$ 20 mN m\protect\textsuperscript{-1}), one can
 speculate that the phospholipid material has a higher surface energy,
@@
 Previous studies on gecko adhesion have attributed capillary effects to be a result of water monolayers adsorbed from ambient humid air onto the spatuale hair tips \citep{RN197, RN203, RN218}.
-We however emphasize that capillary contribution in gecko adhesion could rather be a result of its setal phospholipid layer rather than water.
+We however emphasize that the capillary contribution in gecko adhesion could instead be a result of its setal phospholipid layer rather than water.
 The previously reported influence of humidity on gecko adhesion \citep{RN197} could possibly be an effect of change in surface tension of the oily phospholipid layer at different humidity, which will in-turn influence the capillary adhesion force.
-We suggest performing single seta adhesion force tests similar to \citet{RN202}
-using a hydrophilic and fluorinated probe in air and underwater conditions. 
-If the fluorinated probe shows higher adhesion underwater than in air on a single seta, this
-would confirm the role of capillary contributions due to an oil-like phospholipid layer to gecko adhesion.
-Further work is also necessary to validate if the phospholipid layer in geckos' toes indeed has fluid-like properties.
+Further work is however necessary to understand the details of the mechanism by which the phospholipid layer mediates gecko adhesion.
 

### 2021-08-05 source/jeb_tex/supplementary.tex
responded to Reviewer 2 comments.
updated MS and figures and supplementary based on his elaborate comments.

@@
 
-\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information}
+\title{Wetting of the tarsal adhesive fluid determines underwater adhesion in ladybug beetles: Supplementary information}
 
@@
 the bottom. All lengths were normalised relative to length $s=\left(3V/4\pi\right)^{1/3}$.
-An appropriate geometry refinement routine was chosen to evolve the
-capillary bridge shape to its minimum energy state. The normalised
+An appropriate refinement and iteration routine was chosen by trial-and-error to get a stable converged solution corresponding to the minimum energy state of the capillary bridge surface.
+The normalised
 total capillary force, $\hat{f}=f/\gamma s$, is the sum of the Laplace
@@
 The surface chemistry of untreated glass (hydrophilic) and PFOTS-coated glass (hydrophobic) was characterized using dynamic contact angle measurements (Table \ref{tab:Contact-Angles}).
+De-gassed water showed similar contact angle values as normal water.
 \begin{table}[H]
@@
 to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
-pad should be negligible. Example measurement video is included in the supplementary data (Movie3).
+pad should be negligible (< 10 \%). Example measurement video is included in the supplementary data (Movie3).
 

### 2021-09-16 source/jeb_tex/manuscript.tex
reviewer responses edited based on thomas and michael's comments
revised MS sent to JEB

@@
 
-\corres{(\email{endlein01@mpip-mainz.mpg.de})}
+\corres{(\email{endlein@gmail.com})}
 
-\date{Received 11 May 2021; revised 11 May 2021} %CHECK DATE
+\date{Received 11 May 2021; revised 16 September 2021} %CHECK DATE
 
@@
 as well as observe the contact. The force sensor was mounted on a stage
-consisting of a X-piezo element, used for precise lateral movements. Additionally, a separate Z-piezo element (P-629.1CD, \emph{Physik Instrumente, Germany}, resolution = 3 nm), fixed upright,
+consisting of a X-piezo element, used for precise lateral movements (step size = 75 nm).
+Additionally, a separate Z-piezo element (P-629.1CD, \emph{Physik Instrumente, Germany}, resolution = 3 nm), fixed upright,
 was used for vertical up-down motion, bringing the insect in contact
@@
 at a speed of 62.5 \textmu m s\protect\textsuperscript{-1}. Ventral view video recordings
-were used for contact area extraction while the side view imaging
-was used to visually aid orienting the pad with the substrate before
-a test.
+were used for contact area extraction while the side view imaging was used to aid in orienting the pad
+with the substrate before a test.
 
@@
 represent the contribution of the bubble itself, calculated from the
-capillary bridge model (see text and Table \ref{tab:Model-parameters}).}
+capillary bridge model (see text and Table \ref{tab:Model-parameters}).
+Two-way ANOVA test showed a significant effect of the \emph{contact mode} (p=0.001, F=9.596, degrees of freedom=2) and \emph{substrate} (p<0.001, F=36.231, degrees of freedom=1).
+Significant interaction between the above two categories was seen (p=0.001, F=10.551, degrees of freedom=2).
+Post-hoc t-test analysis and linear mixed-effect model results are reported in supplementary material (section S3).
+}
 \end{figure}
@@
 bubble of volume, $V_{b}$, is trapped between the hairs and pinned
-to the pad circumference.
+to the pad circumference (``Cassie state").
 
@@
 with or without a trapped bubble. Our theoretical calculations further
-show that the bubble by itself has a negligible capillary contribution
+show that the bubble by itself has a negligible capillary contribution (less than 3\%)
 to the net underwater adhesion of the pad. Direct force measurement
@@
 and underwater conditions. Further, the bubble itself has a negligible
-capillary contribution to the total force. The trapped bubble can
+capillary contribution (less than 3\%) to the total force. The trapped bubble can
 promote adhesion only on a hydrophilic substrate by providing an air
@@
 
-\ack{We are grateful to Prof. Dr. Eduard Arzt and Dr. Ren\' {e} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for fruitful discussions.}
+\ack{We are grateful to Prof.
+Dr.
+Eduard Arzt and Dr.
+Ren\' {e} Hensel (Leibniz Institute for New Materials, Saarbr\"{u}cken, Germany)  for fruitful discussions.
+We further thank the referees for their valuable suggestions in improving the text.}
 
